\section{M. Russell Ballard}

\subsection{Marvelous Are the Revelations of the Lord, April 1998}

These were incredible times, as the spirit of revelation moved powerfully upon the Prophet Joseph Smith. Often others were present with him when revelations were received, and they bore witness of the Spirit and the outward manifestations that were present on these occasions. Typically, they spoke of a whiteness or a brightness that surrounded Joseph. For example, as the 76th section of the Doctrine and Covenants was given, Philo Dibble wrote that Joseph ``seemed to be dressed in an element of glorious white, and his face shone as if it were transparent." (``Early Scenes in Church History," in Four Faith Promoting Classics, (1968), 81) And Brigham Young testified that ``those who were acquainted with [Joseph] knew when the Spirit of revelation was upon him, for his countenance wore an expression peculiar to himself while under that influence. He preached by the Spirit of revelation, and taught in his council by it, and those who were acquainted with him could discover it at once, for at such times there was a peculiar clearness and transparency in his face." (Journal of Discourses, 9:89)

\subsection{Teaching—No Greater Call, April 1983}

President Brigham Young used the following story to illustrate the potential influence of teachers: ``A traveller in the Eastern country overtook an old gentleman walking towards a town, and asked him, `Who is the great man of that little town? Who is your leading man? Who is the governor and controlling spirit of that little place?' The old gentleman replied, `I am the king of that little town.' `Really,' says the traveller, `are you the leading man?' `Yes, sir, I am king in that place, and reign as king.' `How do you make this to appear? Are you in affluent circumstances?' `No, I am poor; but in that little village there are so many children. All those children go to my school; I rule the children, and they rule their parents, and that makes me king.'" (Journal of Discourses, 9:39.)