\section{J. Richard Clarke}

\subsection{To Honor the Priesthood, April 1991}

Those who rationalize acceptance of immoral material on grounds of maturity or sophistication are deceived. Those who excuse transgression by saying ``Well, I'm not perfect" may be reminded that conscious sin is a long way from perfection. We would do best to consider this counsel of President Brigham Young:```Be ...\footnote{ye} as perfect as [you] can,' for that is all we can do. ...\footnote{though it is written, be ye perfect as your Father who is in heaven is perfect. To be as perfect as we possibly can, according to our knowledge, is to be just as perfect as our Father in heaven is. He cannot be any more perfect than He knows how, any more than we. When we are doing as well as we know how in the sphere and station which we occupy here, we are justified in the justice, righteousness, mercy, and judgment that go before the Lord of heaven and earth. We are as justified as the angels who are before the throne of God.} The sin ...\footnote{that will cleave to all the posterity of Adam and Eve} is [not doing] as well as [you know] how." (In Journal of Discourses, 2:129–30.)

\subsection{To Honor the Priesthood, April 1991}

Those who rationalize acceptance of immoral material on grounds of maturity or sophistication are deceived. Those who excuse transgression by saying ``Well, I'm not perfect" may be reminded that conscious sin is a long way from perfection. We would do best to consider this counsel of President Brigham Young: ```Be ... as perfect as [you] can,' for that is all we can do. ... The sin ... is [not doing] as well as [you know] how." (In Journal of Discourses, 2:129–30.)\footnote{It may appear strange to some of you, and it certainly does to the world, to say it is possible for a man or woman to become perfect on this earth. It is written “Be ye therefore perfect, even as your Father which is in heaven is perfect.” Again, “If any man offend not in word, the same is a perfect man, and able also to bridle the whole body.” This is perfectly consistent to the person who understands what perfection really is. If the first passage I have quoted is not worded to our understanding, we can alter the phraseology of the sentence, and say, “Be ye as perfect as ye can,” for that is all we can do, though it is written, be ye perfect as your Father who is in heaven is perfect. To be as perfect as we possibly can, according to our knowledge, is to be just as perfect as our Father in heaven is. He cannot be any more perfect than He knows how, any more than we. When we are doing as well as we know how in the sphere and station which we occupy here, we are justified in the justice, righteousness, mercy, and judgment that go before the Lord of heaven and earth. We are as justified as the angels who are before the throne of God. The sin that will cleave to all the posterity of Adam and Eve is, that they have not done as well as they knew how.}