\section{Loren C. Dunn}

\subsection{Witnesses, October 1995}

Orson Pratt said: ``A person can not be a witness to that which he merely believes. God requires mankind, or certain individuals among mankind, to be witnesses for him—witnesses of his existence—so that they can bear testimony to others" (in Journal of Discourses, 16:209–10).

Said Wilford Woodruff from this Tabernacle: ``Joseph Smith was what he professed to be, a prophet of God, a seer and revelator. He ...\footnote{laid the foundation of this Church and kingdom, and} lived long enough to deliver the keys of the kingdom ...\footnote{to the Elders of Israel,} unto the Twelve Apostles. ...\footnote{He spent the last winter of his life, some three or four months, with the Quorum of the Twelve, teaching them. It was not merely a few hours ministering to them the ordinances of the Gospel; but he spent day after day, week after week and month after month, teaching them and a few others the things of the kingdom of God. Said he, during that period, “I now rejoice. I have lived until I have seen this burden, which has rested on my shoulders, rolled on to the shoulders of other men; now the keys of the kingdom are planted on the earth to be taken away no more forever.” But until he had done this, they remained with him; and had he been taken away they would have had to be restored by messengers out of heaven. But he lived until every key, power and principle of the holy Priesthood was sealed on the Twelve and on President Young, as their President. He told us that he was going away to leave us, going away to rest. Said he, “You have to round up your shoulders to bear up the kingdom. No matter what becomes of me. I have desired to see that Temple built, but I shall not live to see it. You will; you are called upon to bear off this kingdom.” This language was plain enough, but we did not understand it any more than the disciples of Jesus when he told them he was going away, and that if he went not the Comforter would not come. It was just so with Joseph. He said this time after time to the Twelve and to the Female Relief Societies and in his public discourses; but none of us seemed to understand that he was going to seal his testimony with his blood, but so it was. What he said to us and the Church we have had to perform. Joseph Smith was a good man, a prophet of God. His works are before the world; they are before the eyes of the nation; they are before the heavens and the earth.} The foundation that he laid we have built upon\footnote{until the present day; and that foundation no power on earth or in hell will ever be able to remove. That Church and kingdom of God that is planted here in these valleys of the mountains will remain on the earth until the little stone Daniel saw will become a mountain and fill the earth—until the reign of Jesus is supreme and universal.}" (in Journal of Discourses, 13:164).