\section{Lloyd P. George}

\subsection{Gratitude, April 1994}

I believe one of the greatest sins that we, the children of our Heavenly Father, are guilty of is the sin of ingratitude. President Joseph F. Smith said in one of his talks that when we see a man who has been blessed with additional gifts or greater intellect, and he rises to the acclaim and success of his fellowmen, ofttimes he will attribute his success to his own energies, labors, and mental capabilities. Rather than acknowledge the hand of God in anything connected with his success, he ignores Him altogether and takes the honor to himself (see Journal of Discourses, 25:53).\footnote{We see a man raised up with extraordinary gifts, or with great intelligence, and he is instrumental in developing some great principle. He and the world ascribe his great genius and wisdom to himself. He attributes his success to his own energies, labor and mental capacity. He does not acknowledge the hand of God in anything connected with his success, but ignores Him altogether, and takes the honor to himself; this will apply to almost all the world.}

In all the great modern discoveries in science, in the arts, and in all the material advancements of the age, the world says, ``We've done it!" The individual says, ``I've done it!" and gives no honor or credit to God. President Smith continues by saying, ``One of the greatest sins of which the inhabitants of the earth are guilty to-day, is the sin of ingratitude\footnote{the want of acknowledgment, on their part, of God, and His right to govern and control.}" (in Journal of Discourses, 25:52).