\section{David B. Haight}

\subsection{Come to the House of the Lord, April 1992}

``Your endowment is, to receive all those ordinances in the House of the Lord, which are necessary for you, after you have departed this life, to enable you to walk back to the presence of the Father, passing the angels who stand as sentinels, ..\footnote{being enabled to give them the key words, the signs and tokens, pertaining to the Holy Priesthood,} and gain your eternal exaltation in spite of earth and hell." (in Journal of Discourses, 2:31.)

Through the exercise of the sealing power of the holy priesthood, generations are bound together in patriarchal chains from the newborn baby ``as far back as the Lord shall reveal." (Brigham Young, in Journal of Discourses, 3:372.)

\subsection{Solemn Assemblies, October 1994}

In later years another Apostle, Elder George Q. Cannon, reaffirmed that principle to the Church. Quoting Brother Cannon:

``God, having once bestowed the keys of the holy Priesthood on man here on the earth for the up-building of His Church, will never take them from the man or men who hold them [who lead the Church] and \textit{authorize others to bestow them}\footnote{If you will read the history of the Church from the beginning, you will find that Joseph was visited by various angelic beings, but not one of them professed to give him the keys until John the Baptist came to him. Moroni, who held the keys of the record of the stick of Ephraim, visited Joseph; he had doubtless, also, visits from Nephi and it may be from Alma and others, but though they came and had authority, holding the authority of the Priesthood, we have no account of their ordaining him, neither did Joseph ever profess, because of the ministration of these angels, to have authority to administer in any of the ordinances of the Kingdom of God. He never baptized anybody, nor attempted to lay on hands for the reception of the Holy Ghost; and, in fact, he never attempted, that we have any account of, to exercise any of the functions of the holy Priesthood. He was a prophet, it is true, but a man may be a prophet and yet not have authority to administer in the Priesthood. The prophetic gift, to some extent, is distinct from the Priesthood. Joseph had received the prophetic gift and he exercised it and he acted as such prior to his ordination. But when the time came for him to be baptized, then a man who held the keys of that Priesthood came to him and laid his hands upon Joseph's head, and upon Oliver Cowdery, and set them apart, and gave them authority to officiate in the Aaronic Priesthood, which Priesthood held the keys of baptism and so forth.}" (Journal of Discourses, 13:47; emphasis added).

\subsection{Planting Gospel Seeds of Spirituality, October 1972}

God bless our missionary homes. May he also bless our missionaries, as promised by President John Taylor, who said of missionaries, ``...\footnote{Talking of the Elder, why he is a herald of salvation; he is a legate of the skies;} he is commissioned of the great Jehovah to bear a message ...\footnote{to the nations of the earth} and God has promised to sustain him. He has always sustained His faithful Elders, and He always will." (Journal of Discourses, vol. 24, p. 35.)

\subsection{Sustaining a New Prophet, April 1995}

As an early Apostle, Elder Orson Hyde, said: ``It is invariably the case, that when an individual is ordained and appointed to lead the people, he has passed through tribulations and trials, and has proven himself before God, and before His people, that he is worthy of the [position]\footnote{situation} which he holds. ...\footnote{And let this be the motto and safeguard in all future time, that when a person that has not been tried, that has not proved himself before God, and before His people, and before the councils of the Most High, to be worthy, he is not going to step in to lead the Church and people of God. It never has been so, but from the beginning} Some one that understands the Spirit and counsel of the Almighty \footnote{that knows the Church, and is known of her} is the [one]\footnote{character} that will lead the Church" (in Journal of Discourses, 1:123).
