\section{Spencer W. Kimball}

\subsection{Our Great Potential, April 1977}

President Brigham Young, the second president of this dispensation, said: ``It is supposed by this people that we have all the ordinances in our possession for life and salvation, and exaltation, and that we are administering in those ordinances. This is not the case. We are in possession of all the ordinances that can be administered in the flesh; but there are other ordinances and administrations that must be administered beyond this world. I know you would like to ask what they are. I will mention one. We have not, neither can we receive here, the ordinance and the keys of resurrection." (Journal of Discourses, 15:137.)

\subsection{To Bear the Priesthood Worthily, April 1975}

I read further from George Q. Cannon, who was also in the First Presidency:

``\footnote{Now, we can best do this in childhood; we can teach our children in childhood and in youth, and as they grow to manhood and to womanhood we can fortify them against those evils. It has been necessary, apparently—for the Spirit has seemed to indicate the necessity of this—that there should be greater strictness enforced among our people. There has been a growth of wrongdoing in many quarters that has been most painful to all those who have the welfare of the Saints of God at heart, and who desire the prosperity of Zion. Many cases have come to the knowledge of the First Presidency and of the Twelve and of other leading men wherein people have been compelled, in order to conceal their wrongdoing, to marry, and even then have failed to cover it up. Now, such a condition of things, if permitted to continue in our midst, unchecked, would be productive of the most terrible consequences.}The Spirit of God would undoubtedly be so grieved that it would forsake not only those who are guilty of these acts, but it would withdraw itself from those who would suffer them to be done in our midst unchecked and unrebuked; and from the President of the Church down, throughout the entire ranks of the Priesthood, there would be a loss of the Spirit of God, a withdrawal of His gifts and blessing and His power, because of their not taking the proper measures to check and to expose their iniquity." (Journal of Discourses, 26:139.)