\section{Franklin D. Richards}

\subsection{The Continuing Power of the Holy Ghost, April 1973}

President Brigham Young stated: ``The Holy Ghost ...\footnote{takes of the Father, and of the Son, and shows it to the disciples. It shows them things past, present, and to come. It} opens the vision of the mind, unlocks the treasures of wisdom, and they begin to understand the things of God. ...\footnote{their minds are exalted on high; their conceptions of God and His creations are dignified, and ``Hallelujah to God and the Lamb in the highest," is the constant language of their hearts.}

They comprehend themselves and the great object of their existence.\footnote{They also comprehend the designs of the wicked one, and the designs of those who serve him; they comprehend the designs of the Almighty in forming the earth, and mankind upon it, and the ultimate purpose of all His creations. It leads them to drink at the fountain of eternal wisdom, justice, and truth; they grow in grace, and in the knowledge of the truth as it is in Jesus Christ, until they see as they are seen, and know as they are known. }" (Journal of Discourses, vol. 1, p. 241.)

\subsection{The Law of Abundance, April 1971}

President Brigham Young, in referring to making our life a gift to God, had this to say: ``Our religion is worth everything to us and for it we should be willing to employ our time, our talent, our means, our energies, our lives." (Journal of Discourses, vol. 11, p. 119.)

\subsection{The Importance of Prayer, April 1972}

Brigham Young, in his realistic manner, stated: ``You know that it is one peculiarity of our faith and religion never to ask the Lord to do a thing without being willing to help him all that we are able; and then the Lord will do the rest." (Journal of Discourses, vol. 5, p. 293.)

It should be noted, the above quote cannot be found in the Journal of Discourses at this present time. (Jul 15, 2018)

\subsection{Personal and Family Financial Preparedness, April 1979}

\textit{The third point of the formula is to use your surplus funds wisely.} In many respects, the real test of a man is his attitude towards his earthly possessions. A person who places earthly possessions in the scales against the things of God evidences little understanding of eternal values.

President Brigham Young had this to say about this matter:

``When this people are prepared to properly use the riches of this world for the building up of the kingdom of God, He is ready and willing to bestow them upon us. ...\footnote{If the Latter-day Saints will walk up to their privileges, and exercise faith in the name of Jesus Christ, and live in the enjoyment of the fullness of the Holy Ghost constantly day by day, there is nothing on the face of the earth that they could ask for, that would not be given to them. The Lord is waiting to be very gracious unto this people, and to pour out upon them riches, honor, glory, and power, even that they may possess all things according to the promises He has made through His apostles and prophets.}

``I like to see men get rich by their industry, prudence, management and economy, and then devote it to the building up of the kingdom of God upon the earth" (Journal of Discourses, 11:114–15).

\subsection{Testimony, April 1984}

President Brigham Young said, ``You cannot find a compass on the earth, that points, so directly, as the Gospel plan of salvation. It has a place for every thing, and puts everything in its place." (Journal of Discourses, vol. 3, p. 96.)