\section{N. Eldon Tanner}

\subsection{Integrity, April 1977}

One of those who made that first long trek across the plains from the Mississippi River to the Salt Lake Valley was Heber C. Kimball, grandfather of our present-day prophet and leader, President Spencer W. Kimball. On one occasion he said:

``God ...\footnote{is much more merciful than we are. He} is determined to save those who will take a course to secure their election and heirship to eternal life. All such people will prevail. If they fail in their integrity and firmness to the cause of righteousness, and repent not, they will lose all they have already gained, all they have expected, and all that has ever been promised to them that overcome." (Journal of Discourses, 8:89.)

\subsection{Where Art Thou?, October 1971}

One reason is to help us develop and grow through the schooling we receive in the experiences we encounter in mortal life. Brigham Young said: ``I am happy ... for the privilege of having temptations." (Journal of Discourses, vol. 3, p. 195.) Temptations are necessary for our advancement and our development. ``When temptations come to you, be humble and prayerful, and determined that you will overcome, and you will receive a deliverance and continue faithful, having the promise of receiving blessings." (JD, vol. 16, p. 164.)

\subsection{Ye Shall Know the Truth, April 1978}

Brigham Young made this statement:

``There is not a man of us but what is willing to acknowledge at once that God demands strict obedience to his requirements. But in rendering that strict obedience, are we made slaves? No, it is the only way on the face of the earth for you and me to become free, and we shall become slaves of our own passions, and of the wicked one, and servants to the devil, if we take any other course.\footnote{and we shall be eventually cast into hell with the devils.}" (Journal of Discourses, 18:246.)