\section{Tue, Oct 2, 2018}

Life can be tricky at times. There are so many advancments in a life that a person can
see out there, yet not understand or grasp. That's okay though. At least we know from
experience that it can and does get better as life moves on. If we are but to
understand and think for ourselves, would it not be beneficial to actually do some
thinking at times? There doesn't appear to be any reason not to enjoy a thought here
and there. There's no reason not to try to understand something as simple as that.
But what is simple exactly? Is there anything which can or cannot be proven because
it is simply there? Because it exists? What does any of that mean anymore? If a
person really does have agency, if agency is a thing and not something a person
created for the benefit of their own welfare, then we should be allowed to choose
which religion to believe in. We should be allowed to decide what happens in our life
and continue on that path as we see fit.

That thinking crosses over into quite a rabbit hole. It is said that Jesus died for
our sins, that he knows us personally. That He knew which sins we would commit or
possibly commit and He suffered for those sins. So, let's say as an example a person
has the ability to steal something. Jesus suffered for that sin for that speciifc
person. What happens if that person decides never to steal something ever in their
life? Does that mean Jesus suffered for nothing?

If that is the case, that Jesus suffered for nothing, then that would mean the
atonment is for naught. It covered sins that didn't exist for a person. However, if a
person does commit the sin of stealing doesn't that mean Jesus and God know exactly
what course our lives will take? Thus we don't have agency in the matter? We are
doomed to make that mistake no matter which road we took, simply because Jesus saw
the sin and atoned for it. It's an interesting thought process for sure. I just wish
I had an answer for it.

\begin{displayquote}
For Christ also hath once suffered for sins, the just for the unjust, that he might 
bring us to God, being put to death in the flesh, but quickened by the
Spirit:\footnote{1 Peter 3:18}
\end{displayquote}

\begin{displayquote}
Now Aaron began to open the scriptures unto them concerning the coming of Christ, 
and also concerning the resurrection of the dead, and that there could be no 
redemption for mankind save it were through the death and sufferings of Christ, 
and the atonement of his blood.\footnote{Alma 21:9}
\end{displayquote}

\begin{displayquote}
Therefore I command you to repent-repent, lest I smite you by the rod of my mouth, 
and by my wrath, and by my anger, and your sufferings be sore-how sore you know not, 
how exquisite you know not, yea, how hard to bear you know not.

For behold, I, God, have suffered these things for all, that they might not suffer 
if they would repent;

But if they would not repent they must suffer even as I;

Which suffering caused myself, even God, the greatest of all, to tremble because of 
pain, and to bleed at every pore, and to suffer both body and spirit-and would that 
I might not drink the bitter cup, and shrink-

Nevertheless, glory be to the Father, and I partook and finished my preparations 
unto the children of men.\footnote{D\&C 19:15-19}
\end{displayquote}
