\section{Plural Marriage in Kirtland and Nauvoo}

\subsection{Essay Text}

Polygamy had been permitted for millennia in many cultures and religions, but, with few exceptions, was rejected in Western cultures. In Joseph Smith’s time, monogamy was the only legal form of marriage in the United States. Joseph knew the practice of plural marriage would stir up public ire. After receiving the commandment, he taught a few associates about it, but he did not spread this teaching widely in the 1830s.

\subsection{Journal of Discourses 13:193-194}

In the early rise of this Church, February, 1831, God gave a commandment to its members, recorded in the Book of Covenants, wherein He says, ``Thou shalt love thy wife with all thy heart, and shalt cleave unto her and to none else;" and then He gives a strict law against adultery. This you have, no doubt, all read; but let me ask whether the Lord had the privilege and the right to vary from this law. It was given in 1831, when the one-wife system alone prevailed among this people. I will tell you what the Prophet Joseph said in relation to this matter in 1831, also in 1832, the year in which the law commanding the members of this Church to cleave to one wife only was given. Joseph was then living in Portage County, in the town of Hiram, at the house of Father John Johnson. Joseph was very intimate with that family, and they were good people at that time, and enjoyed much of the Spirit of the Lord. In the forepart of the year 1832, Joseph told individuals, then in the Church, that he had inquired of the Lord concerning the principle of plurality of wives, and he received for answer that the principle of taking more wives than one is a true principle, but the time had not yet come for it to be practiced. That was before the Church was two years old. The Lord has His own time to do all things pertaining to His purposes in the last dispensation; His own time for restoring all things that have been predicted by the ancient prophets. If they have predicted that the day would come when seven women would take hold of one man, saying, ``We will eat our own bread and wear our own apparel, only let us be called by thy name to take away our reproach;" and that, in that day the branch of the Lord should be beautiful and glorious and the fruits of the earth should be excellent and comely, the Lord has the right to say when that time shall be.

Now supposing the members of this Church had undertaken to vary from that law given in 1831, to love their one wife with all their hearts and to cleave to none other, they would have come under the curse and condemnation of God's holy law. Some twelve years after that time the revelation on Celestial Marriage was revealed. This is just republished at the Deseret News office, in a pamphlet entitled, ``Answers to Questions," by President George A. Smith, and heretofore has been published in pamphlet form and in the Millennial Star, and sent throughout the length and breadth of our country, being included in our works and published in the works of our enemies. Then came the Lord's time for this holy and ennobling principle to be practiced again among His people.

We have not time to read the revelation this afternoon; suffice it to say that God revealed the principle through His servant Joseph in 1843. It was known by many individuals while the Church was yet in Illinois; and though it was not then printed, it was a familiar thing through all the streets of Nauvoo, and indeed throughout all Hancock County. Did I hear about it? I verily did. Did my brethren of the Twelve know about it? They certainly did. Were there any females who knew about it? There certainly were, for some received the revelation and entered into the practice of the principle. Some may say, ``Why was it not printed, and made known to the people generally, if it was of such importance?" I reply by asking another question. Why did not the revelations in the Book of Doctrine and Covenants come to us in print years before they did? Why were they shut up in Joseph's cupboard years and years without being suffered to be printed and sent broadcast throughout the land? Because the Lord had His own time again to accomplish His purposes, and He suffered the revelations to be printed just when He saw proper. He did not suffer the revelation on the great American war to be published until some time after it was given. So in regard to the revelation on plurality; it was only a short time after Joseph's death that we published it, having a copy thereof. But what became of the original? An apostate destroyed it; you have heard her name. That same woman, in destroying the original, thought she had destroyed the revelation from the face of the earth. She was embittered against Joseph, her husband, and at times fought against him with all her heart; and then again she would break down in her feelings, and humble herself before God and call upon His holy name, and would then lead forth ladies and place their hands in the hands of Joseph, and they were married to him according to the law of God. That same woman has brought up her children to believe that no such thing as plurality of wives existed in the days of Joseph, and has instilled the bitterest principles of apostasy into their minds, to fight against the Church that has come to these mountains according to the predictions of Joseph.