\section{Wed, Aug 15, 2018}

My my my how time tends to fly. I remember this day like it was yesterday. Many years
ago. Seriously, time tends to fly now that we're older. I kind of miss the days of
youth when I didn't have so many things to worry about and think about. Yet here I am
that many years later, and what have I learned from it?

Oh I hope I've gotten wiser and perhaps smarter over the years. I'm not sure. Who's
ever fully sure about any of it? It's life right? Isn't that what this whole things
is about? Living to an extent upon which you cannot fully understand or grasp?

Yeah, something like that.

\st{It would be nice to be able to forget some of the past. I mean who wouldn't want 
to forget something that happened years ago. Isn't a person meant to move on from
such thoughts? They should be able to forget something happened eventually... right?}

Whatever this life brings, it can be good or bad. There are no other ways of looking
at it all. Some experiences are meant to teach us and we learn from them. Other
experiences are just down right bad, and we wish we could forget them.

Life can be like a record caught on repeat. We can learn from past mistakes and move
forward, but those mistakes can have a way of sticking around in our minds not
allowing us them to leave us alone. If that makes sense? \st{Seriously, what even 
makes sense these days???} But if we aren't willing to try to move beyond that which
comes along, I don't know what to do about any of it. This is life.
