\section{Wed, Apr 24, 2019}

There's a problem with not believing anymore. When you say you don't believe, 
your friends and family leave you. It's that simple. People don't believe that 
happens, but it does. Because there have been countless leaders telling those 
who no longer believe to keep those people at arms length. It doesn't seem very 
Christlike. Christ went to those people who would seperate themselves from an 
organization. He went to the one lost sheep and brought them back to him. Not to 
an organization. The church in Christ's time was the furthest from the truth. He 
didn't bring people to the church, He brought people to believe in Him. See the 
difference? Not many people do.

God chose to restore His One and Only True Church in these last days, and it 
only accounts for what, .002\% of the population? Is that really how God works? Is that 
really how it's meant to work? I'm not sure I fully understand it. Now let's 
check other numbers, 70\% of mormons are inactive, that leaves 30\%, which comes 
to 4.5 million? Yeah something like that. Either way, it's a low number compared 
to the rest of the world.

The mellinium is supposed to wrap up all the loose ends. Everyone will be 
baptized and have all of their works done for them so they can get into Heaven, 
if they choose to become Mormon that is. Yet prophets and apostles have stated 
that non Mormons will make it into heaven. I guess they'll eventually be 
converted into Mormon? There's an interesting thought.

We don't care what you believed in all your life. It was wrong. Now, become 
Mormon and you can have eternal life. For this is the only way to get into 
heaven. You can pick up your wives at the gate.

Yeah, no thanks.
