\section{Thu, Jun 7, 2018}

Another day is here. There are some days which just don't make sense. I believe
today is one of those days. Why would it make sense? There's no reason for it to
make any sense at all. Yet here we are, trying to make sense of all and
everything which doesn't matter. It's life right? Such a life which doesn't want
to make sense will never make any sense. Yet, we expect it to do something and
have some kind of purpose that has reason to it. It's not a clear and cut dry
solution. That's what this life is all about. Nothing makes 100\% sense all of
the time.\footnote{Imagine for a second, a moment if you will, that life had
the ability to make perfect sense. There would be no confusion about how 
anything is meant to play out. Think about that for a moment. No fear of anyone,
no hatred, no grief, everything in perfect peace. I doubt we'll ever see that
in this life...perhaps in the next life to come. Who's to say exactly how any
of it will work.}

It would be nice for everything to have some kind of order to it. I wonder how
that would be exactly. If everything was in order, there wouldn't be much of a
problem would there? People would get in line. They wouldn't fight each other?
If there is order to a chaotic world, where does that leave the chaos? Where
would such chaos exist or go? Is it possible for an entire civilization, an
entire world to live in complete harmony?

We're told in the Book of Mormon after Christ's visitation to the America's,
there was a long period of peace between the Nephies and the Lamenites, that
there were no manner of ites.\footnote{4th Nephi 1:17} They were all one in 
purpose...finally they had achieved harmony. Eventually it went away, as does 
all kind of harmony as evil crept back in and destroyed civilization after 
civilization. But to have such a peace? How wonderful would that be!

We live in a world where destruction can come at any moment. There's no reason
to necessiarly fear it, but to be aware of such things. We are to be prepared in
all things that might come our way.

Naturally it would be good to find peace and harmony among all people. To not
worry about anything that might be of destruction to us, but life doesn't always
work out that way. It has a tendency to destroy us from within. That is, it can
destroy us from inside of an organization. There is always that one wolf in
sheeps clothing. Someone always has the intent on destroying a structure from 
the inside. Where is the justice in such an action? I cannot say for certain,
but it would appear such things would be bad.
