\section{Fri, Jun 8, 2018}

40 Years ago today. The Priesthood and Temple Ban on the Negro race was lifted.

There is in this life truths which cannot be denied. There are times when men
speak for God without asking God if they should say such things. It can be
rather embarrassing later on down the road when they have to change their speak,
claiming it to be from God or that God never instructed them to say such things.

As a body, we are expected to listen to their explaination of it all and simply
accept it. Moving forward as though none of it ever happened. This is not how
life works though. It is not in human nature to simply forget something happened
when in fact it did. There is no denying what was taught.

Yes we can move forward from such an act. But we cannot forget what happened in
order to not repeat the past. I hope that makes some kind of sense. It is better
to move forward into the future without repeating past mistakes than it is to
create those mistakes all oever again.

Naturally it is better to have not made such foolish statements to begin with,
but I fear that is human nature. I would say more on this topic, but I fear I
might get too heated. I do not wish that.\footnote{I of course am speaking about
blacks finally receiving the blessings of the priesthood and the temple after
so many years of prophets and aposltes having anti feelings towards them as a 
race. In my opinion, it should never have happened. They should have always
had the blessings allowed them, because God is not that author of confusion,
and God is not a respector of men.}

It is a good thing to be able to enjoy a coming up weekend. There is not much to
be said about it, aside from that which can be said. Work is a necessity of
life. There is no other thing possible than the need to do work. That is okay
for work brings in money, money brings about the ability to survive and live.

It is a wonder, do we become a slave to money? I do not know. There could be
times when it is a needed thing, but to become a slave to it? As though it were
your god? I would hope that is not the case. God is not made out of money, for
He is not an idol.\footnote{Acts 17}

There are so many confused people in this life. Some belong to a religion,
others do not admit to doing such. Either way, people will live their lives
according to their own dictates. However, there are some who are brainwashed in
such thinking. There is nothing wrong with belonging to a religion, that is fine
and well. It becomes an issue when that religion dictates everything you do.
Laws regarding your life should not be up to a religion, they need to be up to
God and His Son Jesus Christ.

Man's ways are not God's ways. We know this truth from a number of sources over
the years.\footnote{Isaiah 55:8-9} They aren't only from the bible. But from
other articles, prophets, etc.

So we continue onward in this life. There's nothing wrong with that thought
process. Life simply continues to move forward, whether we like it or not. Is
that not the reason people have difficulties in this life? You would think life
would be some kind of wonderful thing...that it would be understood by most.
Well, that's not the case. Not in the slightest bit. Life doesn't have a full
meaning to everyone. Life cannot always have a full meaning to everyone. I
believe if it did, people would lose balance in what they believed in. That
would be a tragedy.\footnote{Tragedy: An event causing great suffering, 
destruction, and distress, such as a serious accident, crime, or natural 
catastrophe.}

Instead, we would rather have a travesty run about us.\footnote{Travesty: A 
false, absurd, or distorted representation of something.} We are able to deal
with falsehoods prentending to be truth. There's no problem with that at all.
Why bother with the truth when a lie will do?

You can fool an entire group of people with simple lies, when they try to figure
out the truth is when shelfs begin to break. There's no opposition to this
statement for that much is the truth of the matter. Some will say you were
looking for faults in this, that, and the other. Others will sympathize with you
regarding your findings. There is simply no middle ground to any of it.

Benjamin Franklin's inoic text of Poor Richard's Almanack, had the following to
say about truth:

\begin{displayquote}
Half the Truth is often a great Lie

A Lie stands on 1 leg, Truth on 2.

When Knaves fall out, honest Men get their goods: When Priests dispute, we 
come at the Truth.

The Sting of a Reproach, is the Truth of it.

Craft must be at charge for clothes, but Truth can go naked.

When the Wine enters, out goes the Truth.\cite{franklin}
\end{displayquote}

It is an interesting thought process about lies. We are told in the Bible as a
commandment not to lie,\footnote{Exodus 20:16} in the Book of Morming we are 
told that liars go down to Hell.\footnote{2 Nephi 9:34}

Then there are lies of omission. ``A life of omission is still a 
lie,"\footnote{Star Trek: The Next Generation - The First Duty} said the great 
\textit{Enterprise} Starship Captain Picard.

But let us not mince words with those of men. For God knows our hearts. He knows
our souls and the desires of all matters that we attend to. If we have wicked
within us, we are that. If we have righteous desires, we are that. Either way,
we are what we are. There is no disputing any of it as this life is a challenge
to all \st{who come our way} those things which come our way.

It would be easier if this life was full of truth and duty as it were. There
cannot be such a thing if you constantly wish to undermine that which you have
been taught all those years of life. So many things are out there which cannot
be determined simply by astetics alone. \st{I might be rambling now... or 
something,} I cannot tell what is happening at the moment. I speak that which 
comes from my mind, my heart; my soul. Whatever the case, we are here in a life
doing our thing. Each of us has a way of working through our problems. Issues
which come about because of other thought processes. Sometimes those thoughts
occur because we cannot behold everything which they are at one given time.
Other times, those thoughts are simply there to meddle with our 
affairs.\footnote{Meddle: Interfere in or busy oneself unduly with something
that is not one's concern.}
