\section{Thu, Jun 14, 2018}

Today is another day. Just keep telling yourself that. You'll be fine. Is there
really anything anyone else can say about that? Aside from you'll be fine? It's
a thoughtful thought...no, no it's not. It's not even thoughtful at all. There's
no reason to wish someone they'll be fine. Honestly, is there really a reason to
tell someone they'll be fine and not to worry about anything? So many people get
told that they'll just be fine and not to worry about anything. Do you hear what
you're saying to people? Does anyone really grasp what they are telling people
when they say you'll be fine?

No one will simply be fine because \st{YOU} \textit{you} wish them to be fine. 
It doesn't work that way at all. It would be nice if life actually listened to
that kind of thinking and good wishes, but it doesn't.

Try telling someone who has anxiety ``I don't understand why you have anxiety,
why can't you simply let it go?" Yeah, that doesn't go over well either. It
never works out. The mind will do what the mind will do and there's nothing you
can say about it. Have we actually googled ``Anxiety" yet? Let's do
it!\footnote{Oh! it's a noun! 1. A feeling of worry, nervousness, or unease, 
typically about an imminent event or something with an uncertain outcome. 2.
Desire to do something, typically accompanied by unease. 3. A nervous disorder 
characterized by a state of excessive uneasiness and apprehension, 
typically with compulsive behavior or panic attacks.}

Yeah... those are some amazing descriptions there. (Psst, you have to check in
  the footnotes for them!) So yeah, there's that. I didn't ask for anxiety. It's
how God made me.
