\section{Tue, Jun 19, 2018}

Oh what a wonderful day today is. It is another day, it is one of those days
where you can just breathe. Breathing is good. It feels good ot breathe. There's
nothing wrong with that. Talk about a good feeling to have. Naturally it is the
beginning of the day, so things could happen...but for now it's going good.

There are so many things in this world that stress people out. So many darn
things that don't make sense, and so many other things that make you want to
pull your hair out like a mad man. Whatever the case, this life continues to
move forward. There's no reason for it not to. Life happens as it comes to us.
We just have to go with the flow somedays. Other times, we need to fight against
the current. Those days are difficult and hard, but they can be worth it.

Then come the questions. There are so many questions in this life. Why does x,
y, and z happen? Who lets it happen? What's going on with any of it? There
doesn't seem to be a rhyme or reason to any of it. It's life right? That's just
simply how everything works. To say it's not worth the risk? I dare say it is
worth the risk. What risk? Oh, every choice has a risk to it. Some risks are
easier to manage and accept than others. Then there are risks where if you don't
do it, things don't fall into place and you're just plain screwed. That's how
life also works at times. It can be a mess to clean up, a mess to work with, a
mess to overcome. But, remember this...anything can be \st{overcomed} 
overcome.\footnote{
Heh, overcomed isn't a word! Who knew! I sure do now. Thanks Google! Oh talk
about the various things in life which are good to know. The words we use? Very
good to know the correct spelling and meaning to them as we take them and use
them. Reminds me of the time I tried using a word I didn't know how to use at
all. Oh that was funny..well I was actually embarrassed about the whole ordeal.
But when I explained myself, it made better sense. I think? Yes, yes it sure
did. Perhaps life was meant to be this way? To run across words you don't
understand in order to find a way to make it \st{understandable} have sense? 
Well after you look it up I mean. Nothing can be fully understood without study. 
Yeah, something like that. Either way, it's life and we're here to grasp and
understand as much as we possibly can.
}

So here we are in a life which doesn't always makes sense, and we're supposed to
try and make some kind of sense out of it all. Yep, that's a work in progress if
I ever heard of one! I feel like a work in progress at times. Is there anything
wrong with that thought? I sure hope not. I mean, who isn't a work in progress
as we get through this life? Isn't that what this life is all about? Go through
the steps, try and figure out who you are and what you're doing here, and be on
your way? Yeah...something like that.

Dreams about life can be misunderstood. This life can be grasped through words
and verse, yet here we are trying to best understand everything which happens
while here on the land. Yet here we are, all grasping at straws. Thinking and
praying to a great sky God. Who sees from above, his children in distress. I
wonder what he thinks about all of this mess. We live and we go along a crooked
path, always but learning to see what we lack. Oh what a day, these days they do
come. Yet here we are ever learning, hoping for a better life.

It would be nice to be able to figure out everything there is to figure out in
this life, once and for all. To have all of the answers. But we are again told
to live by faith. That answers will eventually come. That we cannot have all of
the answers at this current moment because we are not ready for such answers to
come. Is it all a bunch of brainwashing which is happening? To keep people at
bay? To say to them, hey you don't need to worry about this...because if you
do...you'll freak out and we can't handle the aftermath of such a thing. It
could be something like that...I think? Maybe? Who's to say!

We live here...for a purpose. That purpose has been determined by different
people of different faiths. Some say they have the actual truth though...and we
are expected to live by that alone. But if we are expected to believe in the
words of others without knowing for ourselves...that doesn't feel right. It
feels like deception at times.

Life has many ways of messing with a person. Some say it's not life messing with
you but other people. Fine, if it's other people...then whos responsible for all
of it? If there is a higher being who watches over all? Then why does He allow
for everything to come up a mess of a life? It doesn't quite make sense now does
it? No, I didn't think so. Such an odd life to live in. Such a weird sight to
behold. Talk about annoying, a thought process which we cannot fully fathom
right now. We have to believe in something, have faith in something better than
we alone can behold and create. Where does that leave us exactly? Why does that
make people run for cover and hide from the world? If it's meant to be open and
uplifting to all...why do so many people suffer because of it?\footnote{
Suffering people has been around since...forever. There hasn't been a day where
the people of the world haven't suffered. It goes all the way back to Adam and
Eve after they were cast out of the Garden of Eden. They suffered because of
their lack of spirituality. Their lack of self governing. Man had to work by the
sweat of his brow to survive. Woman was now able to produce children, and suffer
through childbirth etc. Suffering is part of the great plan of our Eternal God?
Okay then...I suppose that's possible. But we shouldn't look upon rewards in
heaven for to do so would be foolish. We have to focus on our current status in
life, and the suffering which we cause to come upon ourselves as it were. Do we
really cause the suffering to come upon ourselves? Are we alone in the universe
to make our own lives a living hell? I'll let you hem and haw over that one for
a bit...I honestly don't have a clue.
}
