\section{Wed, Jun 20, 2018}

Wednesday. What is there to say about wednesday aside from it's the middle of
the week? It's a day, that much is true. What more do you want from it? I'm not
sure. It comes and goes every week. Never sticks around, and yet here we are
looking at it down the line.\footnote{
That might not have made much sense. Down the line. What does that even mean? I
haven't the faintest idea! Such an odd phrase to come up with. I'm assuming it's
been used before? Let's find out... Oh Google... ``At a further, later, or 
unspecified point." Yeah... I don't believe I used it correctly. Oh well. You
get the gist of it right? I sure hope you do! If not? Then we're in for a world
of hurt. Possibly even worse. But what could be worse than a case of mistaken
identity when it comes to a word? I'm sure there are many more things worse than
that!
}

So here we sit, waiting for something good to come along in life. There's no
reason for it. There's no reason for any of it is there? I mean, what good can
come from something which you basically have no control over? There doesn't seem
to be a reason for any of it. Reasons come a dime a dozen at times. There's
nothing worth a reason most of the time...unless there is? No, I don't think
there is.

Waiting around for a miracle as it were, well that feels like a bunch of nothing
to me. Why can't we all just do that which is right and get along with each
other? There doesn't seem to be any reasons for it. Aside from the typical
problems we all run into from time to time. Yes, that would be cause enough to
stand up for something better than we are currently standing for.

Some would have you believe there is truth in this life. A truth which cannot be
taken lightly. A truth which you cannot simply set aside from the rest of
anything. There are so many inconsistancies in this life, so many problems.
There are issues which not everyone has an answer to. There doesn't seem to
matter what's going on, yet here we are. Here we are indeed. There should be
needs to understand and gain an understanding of something. Anything. yet there
doesn't always appear to be reasons enough for any of it.

Where exactly does that leave us? I have to wonder at times if we are not all
damned and sent to hell as it were. Life doesn't have an on/off switch. We are
but a single vehicle moving forward and backwards without a driver, and without
a steering wheel. That's what it feels like at times. Who am I to confuse what
my mind says about this life to me? It's what it interprets and how everything
comes together at the end of the day. Talk about a crazy amount of crazy which
might never be able to be understood.\footnote{
When it comes to this life though, what exactly is to be understood? Is there
anything that can readily be grabbed and realized as truth? What is truth? Where
does it come from? If there is a great being in the universe, He has decided to
be quiet on certain matters and wants us all to simply figure it out without any
kind of direction. Yet if we do badly at it, we are punished because of our
decisions. That makes a lot of sense now doesn't it. Yeah, that's what I
thought.
}
