\section{Wed, Jun 27, 2018}

Headaches. What are you going to do with them? They come, they go, they stick
around and they are evil! Evil I say! What exactly are you supposed to do with a
headache that doesn't leave? It moves around but doesn't leave. Grrr I say, Grrr
to them all!

Whatever the case, there is nothing wrong with thinking. Overthinking can be a
problem, but thinking in general can be good. To think about something is to try
and grasp and understand what is being taught. There's nothing wrong with that.
One has to be able to research and try to understand that which they are
learning. If they do not? There is no purpose in learning and no purpose in
understanding. To think for your own self without relying on other people's
thoughts and wishes is to own your beliefs.

Feelings are something else which can betray you. Feelings can often be
misinterpreted and misrepresented. There are those who would base their faith on
their feelings, but those feelings cannot always be valid. Any kind of feeling
can cause your demise. There is nothing you can do about it. Faith cannot be
based on a fallacy such as feelings. It is not logical.\footnote{
Ah there's that word again, logical. What is logic though? I know I've 
\st{talked} wrote about it before. But that was just a quote now wasn't it?
Yeah, something like that. If someone understands logic, then they are far
better off than I am.
}

To feel okay with yourself is a must. There are days where no one ever fully
feels okay with themselves. They don't grasp the concept of self worth or self
love. It is a sad thought that people have such feelings and thoughts. It occurs
to more people than you would think.

Self acceptance can come. It will come. Yes it might take patience and a lot of
ressaurance, but people are able to come to accepting themselves as they are.
People who press down on them, and try to dictate what is right and wrong in
their lives are not those who should be around you.

There are times when writing out your feelings are helpful. There are other
times when doing such things can cause your mind more stress than it needs to
handle from day to day. Either way, this life will find a way to cause you to
forget that which you cannot possibly describe. Something which you must find
out for yourself. For if we do not find out for ourselves what is best for us,
we will always be a slave to that which would want control over us. I don't know
about you, but I don't plan on being a slave.

\lstinputlisting[language=Java]{2018/Meh.java}\footnote{
Oh what a silly thing to even try and comprehend. The life which will always
throw you down and toss you around before you can understand it. It will always
have no meaning to you. A way to find you guilty no matter what. Life will
always find a way to try and keep you down, dragging you to a pit of doom and
dispair. This is not living. This is not life. It will always find a way though.
Sometimes it is not a good feeling or a good thought which will keep you going.
But fear. Fear can be a great motivator. It can be quite an evil companion to
have. Do not fear that which you do not understand. Embrace it and attempt to
move forward with life. If it is bad for you? Then you may decide for yourself
if you need to toss it aside. But for now, live.
}
