\chapter{The Apostles}

According to the Encylopedia of Mormonism:

\begin{displayquote}
An `apostle' is an ordained leader in the Melchizedek Priesthood in The Church of 
Jesus Christ of Latter-day Saints. Apostles are chosen through inspiration by the 
President of the Church, sustained by the general membership of the Church, and 
ordained by the First Presidency and Quorum of the Twelve Apostles by the laying 
on of hands. They serve as general authorities-as distinguished from local and 
regional officers-holding their office as apostle for the duration of their lives. 
The senior apostle is the President of the Church. In addition to serving as 
witnesses of Jesus Christ to all the world (D\&C 107:23), as Jesus' apostles did, 
members of the current Quorum of the Twelve Apostles hold the keys of the 
priesthood—that is, the rights of presidency (D\&C 107:35; cf. 
124:128)\footnote{Encyclopedia of Mormonism [1992], 1:59–60}
\end{displayquote}

In Jesus' time, the apostles were actual witnesses of Christ. That is, they saw Him
and could testify of seeing Him. The apostles in these latter-days, don't appear to
have had that blessing of seeing the Savior. They are a witness of Him in name only.

During a youth event in WA, Elder Oaks at the time responded to the following
question:

\begin{displayquote}
\textbf{Youth Asks:}

\textit{What should we pray for to receive the same testimony and/or conversion that 
Alma the Younger experienced, for our friend who are not members?}

\textbf{Elder Oaks answers:}

I've never had an experience like that and I don't know anyone among the 1st 
Presidency or Quorum of the 12 who've had that kind of experience. Yet everyone of 
us knows of a certainty the things that Alma knew. But it's just that unless the Lord 
chooses to do it another way, as he sometimes does; for millions and millions of His 
children the testimony settles upon us gradually. Like so much dust on the windowsill 
or so much dew on the grass. One day you didn't have it and another day you did and 
you don't know which day it happened. That's the way I got my testimony. And then I 
knew it was true when it continued to grow.\footnote{Multi-Stake Youth Fireside 
Bellevue, WA, 1/23/2016}
\end{displayquote}

Some say that is talking only about an Alma the Younger experience, even though Oaks
says he didn't have a miraculous experience, that his testimony grew over time.

Okay, how about the Prophet Joseph Fielding Smith?

\begin{displayquote}
The question frequently arises: ``Is it necessary for a member of the Council of the
Twelve to see the Savior in order to be an apostle?" It is their privilege to see him
if occasion requires, but the Lord has taught that there is a stronger witness than
seeing a personage, even of seeing the Son of God in a vision. Impressions on the
soul that come from the Holy Ghost are far more significant than a vision. When
Spirit speaks to spirit, the imprint upon the soul is far more difficult to erase.
Every member of the Church should have impressions that Jesus is the Son of God
indelibly pictured on his soul through the witness of the Holy Ghost.

It is the calling of the First Presidency and the Council of the Twelve to be
directed by the Savior and the Holy Ghost in guiding this Church and its members.
Their labors in the service of our Savior are an inspiration to all mankind.

The Lord has blessed us with choice and vailant leadership.\footnote{Improvment Era, 
November 1966, Page 979}
\end{displayquote}