\chapter{Lilith}
\label{chap:lilith}

With all of the possible changes in the narrative throughout the years, there is
mention of a woman named Lilith. She was supposed to be Adam's first wife. But
she didn't want to follow what he said and she ran.

I include it here for a twofold purpose.

1. Do we know this isn't true for certain? It could have been removed from the
texts of the bible for all we know.

2. There is some confusion regarding Genesis 1:27 where it stats that God
created male and female. Then in the next chapter he creates them again.

Some have said there are two versions of the creation. Some have tried to state
(falsely based on the book of Moses) that this was the pre-existence creation of
Adam and Eve.

The pre existence had already been created.

The follow text is quoted from Hebrew Myths\cite{myth}:

Chapter 10: Adam's Helpmeets

(a) Having decided to give Adam a helpmeet lest he should be alone
of his kind, God put him into a deep sleep, removed one of his
ribs, formed it into a woman, and closed up the wound, Adam awoke
and said: `This being shall be named ``Woman", because she has been
taken out o f man. A man and a woman shall be one flesh.' The
title he gave her was Eve, `the Mother of 
All Living''.\footnote{Genesis II. 18-25; III. 20.}

(b) Some say that God created man and woman in His own image on
the Sixth Day, giving them charge over the 
world;\footnote{Genesis I. 26-28.} but that Eve
did not yet exist. Now, God had set Adam to name every beast, bird
and other living thing. When they passed before him in pairs, male
and female, Adam-being already like a twenty-year-old man-felt
jealous of their loves, and though he tried coupling with each
female in turn, found no satisfaction in the act. He therefore
cried: `Every creature but I has a proper matel', and prayed God
would remedy this injustice.\footnote{Gen. Rab. 17.4; B. Yebamot 632.}

(c) God then formed Lilith, the first woman, just as He had
formed Adam, except that He used filth and sediment instead of
pure dust. From Adam's union with this demoness, and with another
like her named Naamah, Tubal Cain's sister, sprang Asmodeus and
innumerable demons that still plague mankind. Many generations
later, Lilith and Naamah came to Solomon's judgement seat,
disguised as harlots of 
Jerusalem'.\footnote{Yalqut Reubeni ad. Gen. II. 21; IV. 8.}

(d) Adam and Lilith never found peace together; for when he
wished to lie with her, she took offence at the recumbent posture
he demanded. `Why must I lie beneath you?' she asked. `I also was
made from dust, and am therefore your equal.' Because Adam tried
to compel her obedience by force, Lilith, in a rage, uttered the
magic name of God, rose into the air and left him.

Adam complained to God: `I have been deserted by my helpmeet' God
at once sent the angels Senoy, Sansenoy and Semangelof to fetch
Lilith back. They found her beside the Red Sea, a region abounding
in lascivious demons, to whom she bore lilim at the rate of more
than one hundred a day. `Return to Adam without delay,' the angels
said, `or we will drown you!' Lilith asked: `How can I return to
Adam and live like an honest housewife, after my stay beside the
Red Sea?? `It will be death to refuse!' they answered. `How can I
die,' Lilith asked again, `when God has ordered me to take charge
of all newborn children: boys up to the eighth day of life, that
of circumcision; girls up to the twentieth day. None the less, if
ever I see your three names or likenesses displayed in an amulet
above a newborn child, I promise to spare it.' To this they
agreed; but God punished Lilith by making one hundred of her demon
children perish 
daily;\footnote{Alpha Beta diBen Sira, 47; Gaster, MGWJ, 29 (1880), 553 ff.}
and if she could not destroy a human
infant, because of the angelic amulet, she would spitefully turn
against her own.\footnote{Num. Rab. 16.25.}

(e) Some say that Lilith ruled as queen in Zmargad, and again in
Sheba; and was the demoness who destroyed job's 
sons.\footnote{Targum ad job 1. 15.} Yet she escaped the curse of death which 
overtook Adam, since they had parted long before the Fall. Lilith and 
Naamah not only strangle infants but also seduce dreaming men, any one of 
whom, sleeping alone, may become their 
victim.\footnote{B. Shabbat 151b; Ginzberg, LJ, V. 147-48.}

(f) Undismayed by His failure to give Adam a suitable helpmeet,
God tried again, and let him watch while he built up a woman's
anatomy: using bones, tissues, muscles, blood and glandular
secretions, then covering the whole with skin and adding tufts of
hair in places. The sight caused Adam such disgust that even when
this woman, the First Eve, stood there in her full beauty, he felt
an invincible repugnance. God knew that He had failed once more,
and took the First Eve away. Where she went, nobody knows for
certain.\footnote{Gen. Rab. 158, 163-64; Mid. Abkir 133, 135; 
Abot diR. Nathan 24; B. Sanhedrin 39a.}

(g) God tried a third time, and acted more circumspectly. Having
taken a rib from Adam's side in his sleep, He formed it into a
woman; then plaited her hair and adorned her, like a bride, with
twenty-four pieces of jewellery, before waking him. Adam was
entranced.\footnote{Gen. II. 21-22; Gen. Rab. 161.}

(h) Some say that God created Eve not from Adam's rib, but from a
tail ending in a sting which had been part of his body. God cut
this off, and the stump-now a useless coccyx-is still carried by
Adam's descendants.\footnote{Gen. Rab. 134; B. Erubin 18a.}

(i) Others say that God's original thought had been to create two
human beings, male and female; but instead He designed a single
one with a male face looking forward, and a female face looking
back. Again He changed His mind, removed Adam's backward-looking
face, and built a woman's body for it.\footnote{B. Erubin 18a.}

 (j) Still others hold that Adam was originally created as an
androgyne of male and female bodies joined back to back. Since
this posture made locomotion difficult, and conversation awkward,
God divided the androgyne and gave each half a new rear. These
separate beings He placed in Eden, forbidding them to 
couple.\footnote{Gen. Rab. 55; Lev. Rab. 14.1: Abot diR. Nathan 1.8; B.
Berakhot 61a; B. Erubin 18a; Tanhuma Tazri'a 1; Yalchut Gen. 20;
Tanh. Buber iii.33; Mid. Tehillim 139, 529.}

There is no way of knowing if these thoughts are true or if they are of fable.
The truth will eventually come forth in time naturally, but with all of the
changes of the Bible that have taken place, who is to know for sure exactly if
what is in the Bible can be taken as truth.

Either way, this is an interesting insight into human thought on the matter.
Changes come and go, there will always be changes it would seem.