\chapter{The Changing Bible}

\begin{displayquote}
We believe the Bible to be the word of God as far as it is translated correctly; 
we also believe the Book of Mormon to be the word of 
God.\footnote{8th Article Of Faith}
\end{displayquote}

Presently, members of the LDS Church believe the King James Version of the Bible to
be translated correctly. Well, perhaps as correct as it can be. Yet Joseph Smith made
revisions to the bible and produced the Joseph Smith Translation. So, how correct
exactly is the KJV Bible?

What exactly does it mean for the Bible to be translated correctly? If there are
inconsistencies in the Bible, does that mean it's not been translated correctly and
one shouldn't believe in it? At which point does one simply no longer believe in the
Bible and believe in more modern scripture?

It's been said that questions cannot be answered by the Bible alone, but by the Book
of Mormon as well. Missionaries are taught to basically push the Book of Mormon first
and foremost. Where does that leave the Bible?

There are scriptures that have been placed from the Bible into the Book of Mormon
that don't match up with the Joseph Smith Translation. If Lehi gathered the plates
before translators could create the Bible and put it together, shouldn't the verses
in the Book of Mormon be closer to that of the Joseph Smith Translation? If not, then
the books Lehi gathered had already been corrupted long before translaters even got
hold of the records.

An interesting change from the KJV Bible to Joseph Smith's Bible is this:

\begin{displayquote}
All things are delivered unto me of my Father: and no man knoweth the Son, but the 
Father; neither knoweth any man the Father, save the Son, and he to whomsoever the 
Son will reveal him.\footnote{Matthew 11:27}
\end{displayquote}

But, if we were to look at the Joseph Smith Translation of this verse, we would get:

\begin{displayquote}
All things are delivered unto me of my Father: and no man knoweth the Son, but the 
Father; neither knoweth any man the Father, save the Son, and they to whom the 
Son will reveal himself; they shall see the Father also.\footnote{JST Matthew 11:28}
\end{displayquote}

Is this not saying that Jesus is the Father, the Eternal God? Sounds like it. A
similar statement is found on the title page of the Book of Mormon:

\begin{displayquote}
And also to the convincing of the Jew and Gentile that Jesus is the Christ, 
the Eternal God, manifesting himself unto all nations\footnote{Book of Mormon 
Title Page}
\end{displayquote}

Sounds like a trinitarian view now doesn't it?

Then in Luke, we find the following:

\begin{displayquote}
All things are delivered to me of my Father: and no man knoweth who the Son is, but 
the Father; and who the Father is, but the Son, and he to whom the Son will reveal 
him.\footnote{Luke 10:22}
\end{displayquote}

Again, we find a little bit of a difference in the JST:

\begin{displayquote}
All things are delivered to me of my Father: and no man knoweth that the Son is the 
Father, and the Father is the Son, but him to whom the Son will reveal 
it.\footnote{JST Luke 10:23}
\end{displayquote}

Another interesting change, and another insight into Joseph's thought that Christ and
God were the same being?

The Bible itself seems to uphold this single thought:

\begin{displayquote}
Jesus saith unto him, I am the way, the truth, and the life: no man cometh unto the 
Father, but by me.

If ye had known me, ye should have known my Father also: and from henceforth ye 
know him, and have seen him.

Philip saith unto him, Lord, shew us the Father, and it sufficeth us.

Jesus saith unto him, Have I been so long time with you, and yet hast thou not 
known me, Philip? he that hath seen me hath seen the Father; and how sayest thou 
then, Shew us the Father?

Believest thou not that I am in the Father, and the Father in me? the words that I 
speak unto you I speak not of myself: but the Father that dwelleth in me, he doeth 
the works.

Believe me that I am in the Father, and the Father in me: or else believe me for 
the very works’ sake.

Verily, verily, I say unto you, He that believeth on me, the works that I do shall 
he do also; and greater works than these shall he do; because I go unto my Father.

And whatsoever ye shall ask in my name, that will I do, that the Father may be 
glorified in the Son.

If ye shall ask any thing in my name, I will do it.\footnote{John 14:6-14}
\end{displayquote}