\chapter{Condemnation}

The Book of Mormon was published in 1830. Exact date was 26 March 1830.\footnote{
Larry C. Porter, "From a Book Coming Forth," Ensign (July 1988), 42.} Though there
were parts of the book published in a newspaper in January of that same year.

However, two years later in September 1832 Joseph Smith received a revelation that 
the church was under condemantion for forgetting the ``new covenant, even the Book of
Mormon." Two years? That seems pretty quick to place an entire church under
condemnation for not following scripture.

Here's the scripture in full:

\begin{displayquote}
And your minds in times past have been darkened because of unbelief, and because you 
have treated lightly the things you have received-

Which vanity and unbelief have brought the whole church under condemnation.

And this condemnation resteth upon the children of Zion, even all.

And they shall remain under this condemnation until they repent and remember the new 
covenant, even the Book of Mormon and the former commandments which I have given 
them, not only to say, but to do according to that which I have written.\footnote{
D\&C 84:54-57
}
\end{displayquote}

Ezra Taft Benson as stated the following:

\begin{displayquote}
``Unless we read the Book of Mormon and give heed to its teachings, the Lord has stated 
in section 84 of the Doctrine and Covenants that the whole Church is under 
condemnation" and ``In our day, the Lord has revealed the need to reemphasize the 
Book of Mormon to get the Church and all the children of Zion out from under 
condemnation—the scourge and judgment."\footnote{Ensign, May 1986, pp. 5, 78.}
\end{displayquote}

The article from which those two quotes are taken, specify some possible explaination
of the condemnation,\footnote{What is the condemnation we are under that President 
Benson speaks of regarding the Book of Mormon?, Ensign, February 1991} which I don't
want to go into here as the emphasis is on the Book of Mormon.