\chapter{Grace of Christ}

Not much is talked about in The Church of Jesus Christ of Latter-day Saints regarding
grace. We are taught to work our way into heaven. John A. Widtsoe said the following:

\begin{displayquote}
Once the final judgment has been uttered and our place assigned, we remain there,
through we may progress forever, and everlastingly increase in power. Meanwhile, in
all such matters, and with respect to all such questions, we can safely rest
ourselves upon the mercy and justice of the Lord. Our only concern need be so to live
as to win a place in the celestial glory.\footnote{Evidences and Reconciliations, 
John A. Widtsoe, p. 283}
\end{displayquote}

So one must win their entrance into heaven. Scriptures teach that we are saved by
works, only the works we do matters most.\footnote{James 2:17-26}

Personally, it is through grace that we are saved. We cannot buy or win our way into
heaven anymore than will Satan change his mind and repent. It simply cannot be done.
It truly is through the grace of Jesus Christ that we are saved. I wish more people
would see that in the church. It's not taught often, it's not mentiond much. The
church claims to not have a checklist in order to get into heaven, but there is a
checklist.

\begin{enumerate}
\item Have faith
\item Repent of sin
\item Be baptized
\item Receive the Holy Ghost
\item Get your endowment
\item Be married in the Celestial Covenant
\item Pay your tithing
\item Be worthy to attend the temple
\item Obey the Word of Wisdom
\item Support the brethren
\item Do your calling within the church
\item Do ministering (formerly home and visiting teaching)
\item Endure to the end
\end{enumerate}

Naturally that is not a complete list of what needs to be done, but it is a good
starting place. It can be downright overwhelming at times. All of these things to do
in order to please God and to come back into His presence. It's enough to drive a
person mad at times. Yet we endure and continue to endure no matter what. But at what
cost? What good does it do if a person is to live all their days hoping to someday be
good enough knowing they will never be good enough to be with God based on their own
actions?

I think there's a scripture that not a lot of people take time to actually think
about and consider. It's possibly the most quoted scripture around. It's found in
John Chapter 3 verse 16. I would, however like to cite from that chapter verses
15 to 18:

\begin{displayquote}
That whosoever believeth in him should not perish, but have eternal life.

For God so loved the world, that he gave his only begotten Son, that whosoever 
believeth in him should not perish, but have everlasting life.

For God sent not his Son into the world to condemn the world; but that the 
world through him might be saved.

He that believeth on him is not condemned: but he that believeth not is 
condemned already, because he hath not believed in the name of the only begotten 
Son of God.\footnote{John 3:15-18}
\end{displayquote}

Here we are taught that if we beleive in Jesus Christ we have eternal and everlasting
life. We are not condemned because of belief, no we would be condemend because of a
darkness within us. In order to be saved, we must believe in Christ, causing no
malice towards others. I believe that's the main point there. It is true our works do
not matter, we cannot earn our way into heaven. Through our actions, if they be evil
and wrong we can prohibit the light of Christ to dwell within us and will show God
that we do not want heaven.

People tend to take that as saying we have control over if we go to heaven or not. To
the highest level of the Celestial Kingdom as it were. We don't have control, we
cannot buy or earn our way into heaven. It's not done. Only through the grace of
Christ are we saved, are our stripes healed. We must accept Him and allow His
salvation to work within us. Without that? We are damned.

We find the Gospel of Christ Jesus in 1 Corinthians 15.

\begin{displayquote}
Moreover, brethren, I declare unto you the gospel which I preached unto you, 
which also ye have received, and wherein ye stand;

By which also ye are saved, if ye keep in memory what I preached unto you, 
unless ye have believed in vain.

For I delivered unto you first of all that which I also received, how that 
Christ died for our sins according to the scriptures;

And that he was buried, and that he rose again the third day according to the 
scriptures:\footnote{1 Corinthians 15:1-4}
\end{displayquote}

That, my friends, is the gospel of Jesus Christ.

Compare that to to the Book of Mormon, which states:

\begin{displayquote}
Behold I have given unto you my gospel, and this is the gospel which I have 
given unto you-that I came into the world to do the will of my Father, because 
my Father sent me.

And my Father sent me that I might be lifted up upon the cross; and after that I 
have been lifted up upon the cross, that I might draw all men unto me, that as I 
have been lifted up by men even so should men be lifted up by the Father, to 
stand before me, to be judged of their works, whether they be good or whether 
they be evil-

And for this cause have I been lifted up; therefore, according to the power of 
the Father I will draw all men unto me, that they may be judged according to 
their works.

And it shall come to pass, that whoso repenteth and is baptized in my name shall 
be filled; and if he endureth to the end, behold, him will I hold guiltless 
before my Father at that day when I shall stand to judge the world.

And he that endureth not unto the end, the same is he that is also hewn down and 
cast into the fire, from whence they can no more return, because of the justice 
of the Father.\footnote{3 Nephi 27:13-17}
\end{displayquote}

One gospel speaks about grace, the other speaks of justice. One about a gift the 
other regarding works. Which is it?
