\chapter{Introduction}

Ah what is a life that cannot be lived? Who is to say it will come and go as you
please? No one has the ability to say such things. It is but a false narrative
from which you can easily fall down a shaft and die. Did not the poet say:

\begin{displayquote}
Prick us do we not bleed.\footnote{Shakespeare - The Merchant of Venice}
\end{displayquote}

Yes, that is what happens in life when you haven't the faintest idea of where
you are headed. Perhaps it is more easily meant if one were to understand that
which we cannot easily see for we look through a mirror 
darkly.\footnote{1 Corinthians 13:12}

To say that we have the full truth, as it were, is to feign ignorance on 
whatever there is other people are able to bring to us as a whole. We are not to 
push them away but embrace them, accept them and what they have to bring to the
table. yet we get caught up in our own ways that we do not know where to begin
and where to end. We are at a loss in this time in life, and it is a pity.

Not everyone wants to believe in the same ideals as you do. Not everyone wants
to have the same thoughts as you do. Not everyone is the same. Yes we can be 
\textit{one} as it were, but not everyone comes from the same background. We 
are all different in our own ways. Should that alone not be celebrated?
Diversity in numbers and types of people? Different cultures and backgrounds? We
can each learn something from one another.

Life has always had a problem with it. There were thoughts that just wanted to
come forth no matter what. Sometimes those thougths got me in trouble. That was
usually the case actually. Then there were times where thoughts didn't matter.
Words were said and life continued onward without problems. This life is but a
life in which we live. There is no other reason for it than for us to experience
joy and pain. Sometimes those experiences occur at the same time. Other times,
they are few and far apart. Either way, this life is what we make of it.

It should be noted text cited from the Bible is from the King James Version.
