\section{Polygamy and Polyandry}

First off, let's get some definitions out of the way:

\begin{displayquote}
Polygamy: The practice or custom of having more than one wife or husband at the same 
time.
\end{displayquote}

\begin{displayquote}
Polyandry: Polygamy in which a woman has more than one husband.
\end{displayquote}

Eveyone knew Brigham Young practiced polygamy. It was thought for the longest time 
that it all began with him. Well, that's not the case. According to the LDS Church
Essay, ``Plural Marriage in Kirtland and Nauvoo"\footnote{
https://www.lds.org/topics/plural-marriage-in-kirtland-and-nauvoo?lang=eng
} we learn that Joseph Smith practed polygamy.

From the book of Jacob, we read:

\begin{displayquote}
For if I will, saith the Lord of Hosts, raise up seed unto me, 
I will command my people; otherwise they shall hearken unto these 
things.\footnote{Jacob 21:30}
\end{displayquote}

Polygamy is meant to bring up seed unto the Lord. It's a means of populating the
Earth so those people will become members of the Lord's church and continue on with
the traditions of their fathers.\footnote{Not to be confused with the vain traditions
of the wicked Lamenites.}

If that's ``one" of the reasons for practicing polygamy, why are there no offspring
of Joseph Smith from those polygmous relationships? People in the church will tell
you he married them spiritually only, but that goes against what the Book of Mormon
teaches.

Can't have it both ways, so which is it?

There are also reports of Joseph Smith marrying girls as young as 15.\footnote{
From the essay: ``he youngest was Helen Mar Kimball, daughter of Joseph’s close 
friends Heber C. and Vilate Murray Kimball, who was sealed to Joseph several 
months before her 15th birthday."
} Again, the apologetics will tell you this was normal for the time. Normal or not,
it goes against any kind of morality a person should have. I don't care the time
period in which it was normal.

Joseph was also sealed to women who were already married to other men. According to
the essay, an angel rebuked Joseph for practicing Polyandry and went back to marrying
single women.

Another moment where God forgot to specifcially announce His intentions of how
polygamy should be practiced? Again, one would think that God would have instructed
Joseph exactly in how things should be worked out. The Bible is full of examples
of the Lord telling the people exactly how to build something, why would other
principles of the gospel be any different?

Is it possible, the polygamy command didn't come from God at all? Joseph made it up
and he decided what he wanted to do and how to go about it? If that's the case,
that's not how God is meant to work. One would hope that certain commandments given
from God would have a strict understanding and expectation to be followed. A prophet
is speaking for God afterall, is he not?

Again from the same essay ``Plural Marriage in Kirtland and Nauvoo" stated above,
there is a troubling line:

\begin{displayquote}
But Emma likely did not know about all of Joseph’s sealings.
\end{displayquote}

This goes against D\&C 132.\footnote{
D\&C 132:52 And let mine handmaid, Emma Smith, receive all those that have been 
given unto my servant Joseph, and who are virtuous and pure before me; and those 
who are not pure, and have said they were pure, shall be destroyed, saith the 
Lord God.
} She was to receive all those who the Lord gave unto Joseph. if she did not know
about them, how was she to receive them? Apparently this revelation was directed
directly to Emma because she did not apporve of Joseph's polygamy practices.

Polygamy came to an end in 1890 with the manifesto. Official Declaration 1 in the
LDS Scriptures. Well kinda. They had to put out a second manifesto in 1904 warning
people they would be excommunicated if they entered into plural marriage. So I guess
the first one was to say the church didn't believe in the practice, and the second
was to actually enforce the rule? I'm not quite sure.

There were mixed feelings on the first manifesto to begin with, I've no idea how
people felt about the second manifesto. Not much is talked about the second manifesto
in today's church meetings. Only the first. There's a bit of things people aren't
taught about in the church, a lot of history gets glossed over; this is one of them.