\section{Quotes}

\begin{displayquote}
Say nothing of my religion. It is known to my God and myself alone. Its evidence 
before the world is to be sought in my life; if that has been honest and dutiful 
to society, the religion which has regulated it cannot be a bad one.\footnote{
Thomas Jefferson
}
\end{displayquote}

Quotes abound in the world of religion. There are so many religious quotes out 
there, some days I do not know where some begin and others end. They are that 
which bring forth the breath of life into people. Allowing them to try and see 
all that is out there.

Granted, not all quotes are faith promoting. There are quotes out there which 
people would rather be buried never to see the light of day. But still those 
quotes exist for a reason. Sometimes those reasons are more than we can grasp 
at the current moment in time.

\begin{displayquote}
If we have the truth, it cannot be harmed by investigation. 
If we have not the truth, it ought to be harmed.\footnote{
President J. Reuben Clark}
\end{displayquote}

The truth is out there. One just has to want to look for it. It isn't hiding. 
In most instances the truth is there, in plain sight. If we do not actually 
look for the truth or seek it out, we cannot find the truth. It will seldom 
come to find us.

\begin{displayquote}
The man who cannot listen to an argument which opposes his views either has a 
weak position or is a weak defender of it. No opinion that cannot stand 
discussion or criticism is worth holding. And it has been wisely said that 
the man who knows only half of any question is worse off than the man who 
knows nothing of it. He is not only one sided, but his partisanship soon 
turns him into an intolerant and a fanatic. In general it is true that nothing 
which cannot stand up under discussion and criticism is worth
defending.\footnote{James E. Talmage}
\end{displayquote}

\begin{displayquote}
We desire that the brethren and sisters will all feel the responsibility of 
expressing their feelings in relation to the propositions that may be put 
before you. We do not want any man or woman who is a member of the Church to 
violate their conscience. We would like all to vote as they feel, whether for 
or against.\footnote{President Joseph F. Smith}
\end{displayquote}

Men and Women are free to choose according to their own thoughts. That is the 
will and mind of the Lord. For we were all given agency th at we might choose 
good from evil. Without having such a choice, we wouldn't learn or grow from 
that which comes across our path in this life.

There are other quotes by church leaders which are not quite in tune with that 
which we have today. Some quotes have been disavowed, others have been simply 
said the person speaking was saying such things as a man.

\begin{displayquote}
Live a good life. If there are gods and they are just, then they will not care 
how devout you have been, but will welcome you based on the virtues you have 
lived by. If there are gods, but unjust, then you should not want to worship 
them. If there are no gods, then you will be gone, but will have lived a noble 
life that will live on in the memories of your loved ones.\footnote{
Marcus Aurelius}
\end{displayquote}

Isn't that what this life is all about? Living a good life? Shouldn't that be
what this life is all about? Do unto others as you would have them do unto you?
Come on now, it can't be this difficult.