\section{Revelation}

We live in a time of continuous revelation as it were. When the church was
being organized and during the time Joseph Smith was the prophet of the church,
he continued to receive revelations. The Doctrine and Covenants of the church
is full of revelations.

After Joseph's death, there doesn't appear to be many revelations coming forth
from the church. Some point to the end of polygamy, or the end of the ban 
against the blacks. There are those also who say there were other reasons
to end those things.

From a publication by David Whitmer, we find the following quote:

\begin{displayquote}
Some revelations are of God: 
some revelations are of man: 
and some revelations are of the devil.\footnote{David Whitmer, 
An Address to All Believers in Christ, in EMD 5: 198.}
\end{displayquote}

This is in regards to the failiure of the church to sell the copyright in
Canada. (See Appendix C: An Address to All Believers in Christ)

Ahem, say what now? Revelations coming from the devil? As revelation? What?

How is that possible? It's been said that the devil can show himself as an 
angel, but an entire revelation from the devil? Wow, what kind of hot water
must you be in to get one of those?

Either way? How does one know if the revelation is from man, God, or the devil?
In what ways are we supposed to actually fully know that these things are
true and to do as they direct, or if we are to set them aside for they are evil?

Makes things rather complicated right?

After Joseph Smith's death, there weren't many additions to the Doctrine and
Covenants. No new revelations added. The Official Declarations 1 and 2 don't
appear to be revelations as they do not say ``Thus saith the Lord" in them,
which was known to be had in other revelations throughout the book.

So what are they exactly?

There's a revelation by Joseph F. Smith which became section 138 of the D\&C,
but nothing since then. Why is that? If we are a church that believes in
continuous revelations, why is that book not being updated? Why are there
not more revelations coming and recored?

Time has changed things. Are people not as revelatory since the times of
Joseph Smith, Jr. when he led the church? Do we have all we need and God doesn't
see fit to speak to us in this day and age?

You might be thinking I'm being rude. But these are honest questions. I'm not
bashing the prophets who have come since Joseph Smith, Jr. I am just not aware
of actual revelations which have come along the way is all.

\newpage

\section{Temple Changes}

Now the temple is a very sacred part of the LDS faith. People don't talk about
it openly due to covenants they have made inside the temple. It is supposedly
restored from the time of Adam when he walked the earth. Some say Joseph Smith
crated the Endowment based off of Freemasonry. Whatever the case, there have
been changes to the temple ritiual over the years.

\subsection{Oath to Avenge Joseph Smith}

After the death of Joseph Smith, Brigham Young added a vengence oath to the
endowment. It was to avenge the death of the Prophet Joseph Smith. If the temple
ordinance was restored and hadn't changed. I doubt this was actually intended to
be part of it. I doubt Adam went around swearing to an oath to avenge the death
of a man who wouldn't be born for centuries to come.

\subsection{Adam God Doctrine}

For a time the Adam God Doctrine was taught at the veil. This was instituted by
Brigham Young. What is the Adam God Doctrine? Here it is in short. Adam is God.
No seriously. Here it is in the long form:

\begin{displayquote}
Now hear it, O inhabitants of the earth, Jew and Gentile, Saint and sinner! 
When our father Adam came into the garden of Eden, he came into it with a 
celestial body, and brought Eve, one of his wives, with him. He helped to 
make and organize this world. He is MICHAEL, the Archangel, the ANCIENT OF 
DAYS! about whom holy men have written and spoken – He is our FATHER and our 
GOD, and the only God with whom WE have to do. Every man upon the earth, 
professing Christians or non-professing, must hear it, and will know it 
sooner or later!\footnote{Prophet Brigham Young, Journal of Discourses, v. 1, 
p. 51}
\end{displayquote}

This was all taught in the temple for a time before it was pulled from the
ceremony. If the temple ceremony was restored, per the Prophet Joseph Smith, why
was the Adam God Doctrine not there to begin with? Why was it added later to the
temple ceremony at the veil? Then, if it was taught as doctrine and was true,
why was it removed?

\subsection{Penalties}

Up until 1990, there were Penalties in the temple. People would symbolically cut
their throats as a sign for what would come if they were to give away the sacred
ordinances of the temple. These were in there from the start, and were removed
as I said in 1990. Is God changing His mind about what is to be taught? Why were
these removed from the temple ordinance? If it's no longer in there, were the
people who took the blood oaths still under requirement to live by those oaths
that if they talk of the temple they will be required to take their own lives?

Again something else that has changed from what was restored. If it is restored
is it not perfect? If it wsa perfect, the doctrine that is, then why was it
removed?

Perhaps it too closely resembled Cain's oath with Satan?

\begin{displayquote}
And Satan said unto Cain: Swear unto me by thy throat, and if thou tell it thou 
shalt die; and swear thy brethren by their heads, and by the living God, that 
they tell it not; for if they tell it, they shall surely die; and this that thy 
father may not know it; and this day I will deliver thy brother Abel into thine 
hands.\footnote{Moses 5:29}
\end{displayquote}

Was it a type of secret combination? We're told to avoid such things.

It should be interesting to note the following quote:

\begin{displayquote}
The Prophet Joseph Smith taught, `Ordinances instituted in the heavens before 
the foundation of the world, in the priesthood, for the salvation of men, 
are not to be altered or changed.'\footnote{Ensign Magazine, August 2002, p 22}
\end{displayquote}

\subsection{Other Changes}

There are other changes to the temple ceremony. At one point there was a
preacher who was a follower of Satan. An entire choir that would sing christian
hymns etc.