\chapter{Seer Stones}

Richard Bushman in Joseph Smith, Rough Stone Rolling explains:

\begin{displayquote}
Joseph had discovered two stones, one in 1822 while digging a well with Willard Chase 
a half mile from the Smith farm. (called the Chase seer stone) The source of the 
other stone is uncertain. These stones were the keys that enable Joseph to see 
things, as Lucy said, ``invisible to the natural eye." Emma Smith described one of 
them as ``a small stone, not exactly black, but was rather a dark color."

In 1841, Joseph showed his other, whitish stone to the Council of the Twelve in 
Nauvoo and told them, Brigham Young reported, ``that every man who lived on the 
earth was entitled to a seer stone and should have one, but they are kept from them 
in consequence of their wickedness."

Alva Hale...said Joseph Smith Jr. told him that the ``gift of seeing with a stone" 
was ``a gift from God" but that ``peeping" was all d\_\_d nonsense.\footnote{
Bushman, p. 48-52
} 
\end{displayquote}

We learn in D\&C 28, that a man by the name of Hiram Page claimed to have a seer
stone in his posession. But it was telling him things from the devil. So Satan has
power over seer stones. Yet, we are to believe that Joseph's seer stone never told
him anything from Satan?

\begin{displayquote}
And again, thou shalt take thy brother, Hiram Page, between him and thee alone, 
and tell him that those things which he hath written from that stone are not of me 
and that Satan deceiveth him;

For, behold, these things have not been appointed unto him, neither shall anything 
be appointed unto any of this church contrary to the church covenants.

For all things must be done in order, and by common consent in the church, by 
the prayer of faith.

And thou shalt assist to settle all these things, according to the covenants of 
the church, before thou shalt take thy journey among the Lamanites.

And it shall be given thee from the time thou shalt go, until the time thou shalt 
return, what thou shalt do.

And thou must open thy mouth at all times, declaring my gospel with the sound of 
rejoicing. Amen.\footnote{D\&C 28:11-16}
\end{displayquote}

So, Joseph was able to have a seer stone, but another man was not and it was due to
being controlled by the devil. A simple outside observation could indicate that
Joseph might have wanted the spotlight to be on himself and not another person who
could see things in a stone? Not sure what to make of that thought at all.

We're also told that Joseph didn't need the seer stone when translating the bible
because he had learn the power of revelation since then. He didn't need an object
upon which to translate.

Seer Stones were used in magical thing like looking for money and hidden treasure in
Joseph's day. It doesn't seem to be something worthy of a prophet of God who had been
prepared since before the world was formed. It feels off and odd at times to think
about.

There was another time when Martin Harris was known to switch out the seer stone in 
the hat,\footnote{Millenial Star 44:87} and when Joseph went to translate again he 
couldn't. Martin was testing Joseph in this act because he wanted to know if Joseph 
truely saw things through the stone. Martin expalins he had found a similar looking 
stone. Wouldn't Joseph know which stone was his and what wasn't? He would have 
quickly known that wasn't his stone in the hat right?

Another thought about it, if the object didn't matter. Wouldn't God have given Joseph
the revelation anyways? He didn't need a stone to translate. It was like a security
blanket really. God can do anything without the power of an object.

I could see the story going either way.