\section{Temple Changes}

Now the temple is a very sacred part of the LDS faith. People don't talk about
it openly due to covenants they have made inside the temple. It is supposedly
restored from the time of Adam when he walked the earth. Some say Joseph Smith
crated the Endowment based off of Freemasonry. Whatever the case, there have
been changes to the temple ritiual over the years.

\subsection{Oath to Avenge Joseph Smith}

After the death of Joseph Smith, Brigham Young added a vengence oath to the
endowment. It was to avenge the death of the Prophet Joseph Smith. If the temple
ordinance was restored and hadn't changed. I doubt this was actually intended to
be part of it. I doubt Adam went around swearing to an oath to avenge the death
of a man who wouldn't be born for centuries to come.

\subsection{Adam God Doctrine}

For a time the Adam God Doctrine was taught at the veil. This was instituted by
Brigham Young. What is the Adam God Doctrine? Here it is in short. Adam is God.
No seriously. Here it is in the long form:

\begin{displayquote}
Now hear it, O inhabitants of the earth, Jew and Gentile, Saint and sinner! 
When our father Adam came into the garden of Eden, he came into it with a 
celestial body, and brought Eve, one of his wives, with him. He helped to 
make and organize this world. He is MICHAEL, the Archangel, the ANCIENT OF 
DAYS! about whom holy men have written and spoken – He is our FATHER and our 
GOD, and the only God with whom WE have to do. Every man upon the earth, 
professing Christians or non-professing, must hear it, and will know it 
sooner or later!\footnote{Prophet Brigham Young, Journal of Discourses, v. 1, 
p. 51}
\end{displayquote}

This was all taught in the temple for a time before it was pulled from the
ceremony. If the temple ceremony was restored, per the Prophet Joseph Smith, why
was the Adam God Doctrine not there to begin with? Why was it added later to the
temple ceremony at the veil? Then, if it was taught as doctrine and was true,
why was it removed?

\subsection{Penalties}

Up until 1990, there were Penalties in the temple. People would symbolically cut
their throats as a sign for what would come if they were to give away the sacred
ordinances of the temple. These were in there from the start, and were removed
as I said in 1990. Is God changing His mind about what is to be taught? Why were
these removed from the temple ordinance? If it's no longer in there, were the
people who took the blood oaths still under requirement to live by those oaths
that if they talk of the temple they will be required to take their own lives?

Again something else that has changed from what was restored. If it is restored
is it not perfect? If it wsa perfect, the doctrine that is, then why was it
removed?

Perhaps it too closely resembled Cain's oath with Satan?

\begin{displayquote}
And Satan said unto Cain: Swear unto me by thy throat, and if thou tell it thou 
shalt die; and swear thy brethren by their heads, and by the living God, that 
they tell it not; for if they tell it, they shall surely die; and this that thy 
father may not know it; and this day I will deliver thy brother Abel into thine 
hands.\footnote{Moses 5:29}
\end{displayquote}

Was it a type of secret combination? We're told to avoid such things.

It should be interesting to note the following quote:

\begin{displayquote}
The Prophet Joseph Smith taught, `Ordinances instituted in the heavens before 
the foundation of the world, in the priesthood, for the salvation of men, 
are not to be altered or changed.'\footnote{Ensign Magazine, August 2002, p 22}
\end{displayquote}

\subsection{Other Changes}

There are other changes to the temple ceremony. At one point there was a
preacher who was a follower of Satan. An entire choir that would sing christian
hymns etc.

\subsection{Thou Shalt Not}

An interesting change is when God placed Adam in the Garden of Eden, he gave a
commandment:

\begin{displayquote}
But of the tree of the knowledge of good and evil, thou shalt not eat of it: 
for in the day that thou eatest thereof thou shalt surely 
die.\footnote{Genesis 2:17}
\end{displayquote}

Eve was not found on the Earth at that time.

In the temple we see that Adam and Eve were together in the Garden of Eden when
God gave such a commandment.

So which is correct? This isn't just what happened in Genesis, but it also
happened in the Book of Moses as well. God commands Adam to not eat of the
fruit, He then creates Eve later after pulling a rib from Adam's side. It is
again the same timeline in the Book of Abraham. So there are three sources from
which it is put forth, yet the temple contradicts that timeline. Again, which
one is correct?

Don't believe me? Here are the scriptures to research:

\begin{displayquote}
Genesis 2:15 - 22

Moses 3:15 - 22

Abraham 5: 11 - 16
\end{displayquote}