\chapter{Book of Mormon Translation}

For years members of the Church of Jesus Christ of Latter-day Saints were told that
Joseph Smith translated the Book of Mormon. It is said he translated it by the ``gift
and power of God." When people think of translation, they think he looked at the
plates and translated letter for letter, word for word the words of ancient prophets.

This was not the case. Joseph would place a seer stone in a hat, and put his face
into the hat. He would then read off the words as they appeared to him. The words on
the stone wouldn't change until his scribe confirmed back to him what was said.

The actual gold plates weren't used in the translation process at all.

People have brought up the question about how Bible passages, complete with changes
known to have been made by men, made it into the Book of Mormon. We have a possible
explaination for that. Joseph Smith copied the passages from the Bible into the 
Book of Mormon:

\begin{displayquote}
When Joseph Smith saw that the Nephite record was quoting the prophecies of Isaiah, 
of Malachi, and the words of the Savior, he took the English Bible and compared these 
passages as far as they paralleled each other, and finding that in substance in 
thought, they were alike, he adopted our English 
translation.\footnote{Young Men's Mutual Improvement Associations Manual, pp.
505-506, 1903-1904. New Witnesses for God. Volume II. The Book of Mormon Part I.
https://archive.org/stream/ymmia1903\#page/n699}
\end{displayquote}

So we're not even sure we have those passages copied word for word from the gold
plates. If that's the case? How are we to be sure that the rest of the book is really
the ``most correct book" out of them all?

There have been noted changes in the book throughout its history. The Eternal Father
being changed to Son of The Eternal Father for Christ etc. It seems to point towards
Joseph changing the words of the prophets. The idea of one god to three seperate
individuals.

But whenever someone questions the validity of the book, they are told to pray about
it. Taking Moroni's promise and seeing for themselves if it is true. Again, acting on
feelings alone and not evidence.

We were taught from the beginning, that the Book of Mormon is about the Native
Americans who came from Jerusalem. That is they were Jews. Science has determined
this not to be the case. The church had to make a change in the introduction of the
Book of Mormon, where it once said the Lamenite people ``are the principal ancestors 
of the American Indians", now it reads ``are among the ancestors of the American 
Indians."

If that change had to be made, what else about the book has been deemed wrong or
incorrect?

Some have come to believe that Joesph made the whole book up, that it was his
imagination which caused the Book of Mormon to come about. They claim the book is not
a historical document, but people should look on the principles taught within the
book which is more important than the origins.

The Book of Mormon stands as a keystone to the LDS Religion. If it is a fraud, then
the whole church is a fraud and Joseph Smith was not a prophet of God. Church leaders
have stated thusly, challenging those who would criticize the book.

President Gordon B. Hinckley had the following things to say:

\begin{displayquote}
There is no middle ground. Joseph Smith talked with the Father and the Son or 
he didn’t. If he didn’t, then we are embraced in a great fraud, a terrible 
fraud.\footnote{``Counsel from the Prophet," Church News, 4/27/96, 4}
\end{displayquote}

\begin{displayquote}
Our whole strength rests on the validity of that vision. It either occurred or 
it did not occur. If it did not, then this work is a fraud... upon that unique and 
wonderful experience stands the validity of this church.\footnote{
``The Marvelous Foundation of our Faith," Ensign [Conference Edition], 
November 2002, 80
}
\end{displayquote}

\begin{displayquote}
You and I are faced with the stark question of accepting the truth of the First 
Vision and that which followed it. On the question of its reality lies the very 
validity of this Church.\footnote{``The Stone Cut Out of the Mountain," Ensign 
[Conference Edition], November 2007, 86}
\end{displayquote}

\begin{displayquote}
That becomes the hinge pin on which this whole cause turns. If the First Vision 
was true, if it actually happened, then the Book of Mormon is true. Then we have 
the priesthood. Then we have the Church organization and all of the other keys 
and blessings of authority which we say we have. If the First Vision did not 
occur, then we are involved in a great sham. It is just that 
simple.\footnote{Teachings of Gordon B. Hinckley, 227}
\end{displayquote}

The book itself states that if there are mistakes in it, those are the mistakes of
men (possibly the translation) and not of God.\footnote{Book of Mormon Title Page}

Why was the manner of translating the book never taught in a primary or sunday school
class? Why did it have to come out through other means? Those teachings were thought
to be anti-mormon lies and false doctrine, only to be proven later on they were true.

In a recent face to face with Elder Cook of the Quorum of the Twelve Apostles, it was
mentioned that the seer stone has always been knowledge, it was even mentioned in an
article from 1974 Children's Friend.

It's nice that was in the Children's Friend back in 1974, but it wasn't actively
taught when I was growing up in the 80s and 90s etc. I did some digging, which we're
basically told not to do,\footnote{We're told to follow the words of the current 
prophet and apostles. If they aren't actively teaching it, how are we to know about 
it unless we go digging in the archives for it?} and found the article in question.

\begin{displayquote}
Because of his spiritual nature and his willingness to learn the truth, Joseph Smith 
was tested and found worthy to be the translator of the Book of Mormon. To help him 
with the translation, Joseph found with the gold plates ``a curious instrument which 
the ancients called Urim and Thummim, which consisted of two transparent stones set 
in a rim of a bow fastened to a breastplate."

Joseph also used an egg-shaped, brown rock for translating called a seer stone. The 
translating was done at Peter Whitmer's home, a friend of the Prophet's where Oliver 
Cowdery, Emma Smith (Joseph’s wife), one of the Whitmers, or Martin Harris wrote down 
the words spoken by the Prophet as soon as they were made known to him.

Martin Harris said that on the seer stone ``sentences would appear and were read by 
the Prophet and written by [the one writing them down] and when finished [that 
person] would say `written;' and if correctly written, the sentence would disappear 
and another take its place; but if not written correctly it remained until corrected, 
so that the translation was just as it was engraven on the 
plates."\footnote{A Peaceful Heart, Children's Friend September 1974}
\end{displayquote}

This quote brings about a question. Was the ``translation" a tight or a loose
translation? If it was tight, there shouldn't have been any changes in the book. If
it truely fell from the prophet's lips word for word, and wouldn't change until it
was written correctly then there shouldn't be any changes. If it is a loose
translation, that is by revelation only, then we don't know if we have the text as it
was written by prophets of old.

There is another interesting thought about the Book of Mormon. The final page, the
last leaf of the book, was a literal translation:

\begin{displayquote}
I wish to mention here, that the title-page of the Book of Mormon is a literal 
translation, taken from the very last leaf, on the left hand side of the collection 
or book of plates, which contained the record which has been translated, the language 
of the whole running the same as all Hebrew writing in general; and that said 
title-page is not by any means a modern composition, either of mine or of any other 
man who has lived or does live in this generation. Therefore, in order to correct an 
error which generally exists concerning it, I give below that part of the title-page 
of the English version of the Book of Mormon, which is a genuine and literal 
translation of the title-page of the original Book of Mormon, as recorded on the 
plates.-DHC 1:71. (1830.)\footnote{Teachings of the Prophet Joseph Smith}
\end{displayquote}

From this we learn the title page was written in Hebrew. Not Reformed Egyptian like
the rest of the plates. Where the rest of the book was translated using the Urim and
Thummim or a rock in a hat, the final page was translated by Joseph himself as a
literal translation. I suppose by this time, he could read and translate Hebrew?