\chapter{Teasure Seeking}

It is interesting to note, Joseph was told by an angel not to continue with treasure
seeking. From the novel, Saints.

\begin{displayquote}
In September 1826, Joseph returned to the hill for the plates, but Moroni said he was 
still not ready for them. ``Quit the company of the money diggers," the angel told 
him. There were wicked men among them.9 Moroni gave him one more year to align his 
will with God’s. If he did not, the plates would never be entrusted to 
him.\footnote{Saints, Chapter 4 Be Watchful, Page 34}
\end{displayquote}

But ten years later, in 1836, Joseph was told there would be a large amount of money
to be had? Isn't that a form of treasure? So he went to Salem to search for it:

\begin{displayquote}
Revelation given through Joseph Smith the Prophet, at Salem, Massachusetts, 
August 6, 1836. At this time the leaders of the Church were heavily in debt due to 
their labors in the ministry. Hearing that a large amount of money would be available 
to them in Salem, the Prophet, Sidney Rigdon, Hyrum Smith, and Oliver Cowdery 
traveled there from Kirtland, Ohio, to investigate this claim, along with preaching 
the gospel. The brethren transacted several items of Church business and did some 
preaching. When it became apparent that no money was to be forthcoming, they returned 
to Kirtland. Several of the factors prominent in the background are reflected in 
the wording of this revelation.\footnote{Header of D\&C Section 111}
\end{displayquote}

If he was told to stop in 1826, why was he still doing it in 1836?