\chapter{Seeing God or Jesus}

Is it possible that since the early days of the Church in the old world, that no man
has seen God or Jesus?

Think about it for a moment. In times past, when God wanted to communicate His word
to people He sent angels to talk with them. He didn't make an appearance Himself.

We know in the Garden of Eden, God appeared to Adam and Eve. But afterwards when He
sent further light and knowledge to them, it was done through His people. God didn't
appear to them.

The God of the Old Testament didn't appear to Moses face to face, but through a
burning bush.

So why was it necessary for God to appear to Joseph Smith when an angel could have
done exactly that. Doesn't God believe in sending messengers down to people? Isn't
that his modus operandi?

Even then, it was a vision. Did Joseph see it in his minds eye? And why did Satan
attempt to stop him from praying? If Satan truly doesn't know the mind of God, why
would he stop a fourteen year old boy from praying to God? Did Satan actually know
God and Jesus were about to visit? If so, then Satan knows somewhat the mind of God
does he not?

We know there are some instances in the New Testament where people have seen Jesus.
They weren't the most righteous people of their time, Saul was out persecuting the
church, yet he saw Jesus or heard Jesus, it depends on which account you read. Here
was by all accounts an evil man who was out trying to destroy the church of God and
Jesus made himself known unto this man.

Propehts and apostles in these latter days, aside from Joseph Smith, do not declare
to have seen God and Jesus. It isn't done anymore. Why is that? If they're God's
mouthpiece, wouldn't they be in contact with God and Jesus? Some say, yes but they
receive revelation. Is that enough? Wouldn't they at least need to have that personal
touch like Joseph Smith did?