\chapter{A Volcano and a Family}

In 1815, the Tambora volcano erupted in Indonesia. It killed 80,000 people.\footnote{
https://www.history.com/this-day-in-history/volcanic-eruption-kills-80000
}

Because of this eruption the climate was affected worldwide, even to North America
where Joseph Smith Sr. and his family lived. With their crops ruined, they were
forced to move from Vermont to Palmyra New York. Five years after that Joseph Smith
had his First Vision.

These facts can be found in the new church history book titled ``Saints". It's in the
first chapter titled ``Ask in Faith".\footnote{https://history.lds.org/saints?lang=eng}

So let me get this straight. God kills over 80,000 people. Not just the people killed
in the volcano. Becuase of it, more than 80,000 people died due to starvation etc,
and Joseph Smith's family moved closer to the gold plates? So Joseph Sith Jr. could
find them? Couldn't have God found another way than killing over 80,000 of his
children? The narrative makes it sound like this was the cause for Joseph Smith Jr.
to be near the golden plates when the time came.

In the article ``A Year Without Summer"\footnote{
https://www.lds.org/ensign/1983/01/a-year-without-a-summer?lang=eng}, it simply
states that this volcano eruption ``played a small role in the history of The Church
of jesus Christ of Latter-day Saints."

I have a feeling God could have found other ways for Joseph Smith Sr. to move his
family instead of killing over 80,000 people.

It is interesting, a few chapter later in ``Saints", it speaks of Joseph trying to
get the gold plates. The angel warned him that if he had any evil thought in his mind
to use the plates to get gain, he could not obtain them.

When Joseph went to the hill to obtain the plates, upon seeing the other items in the
box which were valuable he placed the plates aside for a second. They disappeared.
The angel hid them from Joseph telling him he wasn't ready to take the plates.

If the angel could simply move them like that? Why was the volcano necessary?