\section{The Desk}

It was afternoon in the office. The phone lines had quieted down a bit from the morning rush. Susan sat in her office working on a proposal for the next day. Her legs were crossed under her chair as she swayed along with music playing in her office.

Tom looked up from his computer across the hall. He smiled as he saw Susan dancing in her chair. Tom shook his head as he continued working. He had a crush on Susan for a while now. It was something he hadn’t told anyone of course. One doesn’t just hit on the daughter of the president of the company. He had seen many guys try and ask her out but she had turned them all down one after another. The men weren’t fired because of it, but they couldn’t handle the stares of other co workers, so they left on their own.

“Tom” Susan’s voice could be heard over his phone speaker. He looked up towards her office. She was looking at him. “Come in here please.”

Tom activated his speaker “Right away.” He stood and cross the office floor to Susan’s office.

As he approached her office, he saw that she was wearing a short black skirt with a white blouse. Her shoes were off. Tom knocked on the door.

“Oh come in Tom” Susan said. She watched as he walked in. Tom was wearing

dark pants and a button up shirt. She stood and walked over to him. Taking a deep breath, she smelled aftershave on Tom. He smelled good. Susan closed the door and then the blinds so no one could see in.

Tom smiled nervously. “What can I do for you?”

Susan sat on the desk and gestured to her chair. “Have a seat.”

Tom sat as ordered.

Susan placed her foot between Tom’s legs an inch from his crotch. She wondered if he was cut or if he still had a foreskin. She smirked. Susan would find out soon enough. “Thank you for coming.” She said. “I’ve been watching you Tom.”

Tom could feel his pulse quicken. She had been watching him? What did she mean by that?

Susan rubbed his crotch with her foot. She felt his cock with the tips of her toes. He was getting harder as she did so. She smiled at him. Tom looked afraid. She would have to fix that.

“I want you to fuck me Tom.” Susan said. “Take me right here and fuck me.”

Tom froze. His fantasies were coming true. He had wanted her for the longest time and now was his chance. He nodded. “Okay.”

Susan unbuttoned her blouse and let it fall to the floor. Her bra came off next. She threw it in Tom’s face. Tom pulled the bra off his face and looked at her. Her breasts stared back at him.

Tom stood from the chair and walked over to Susan. Taking a breast in his hand he sucked on it while massaging the other. Susan unbuttoned Tom’s shirt and took it off. She leaned her head back as Tom worked his way up to her neck. His pants were next to go.

Tom stood there in his boxers as he continued to caress and kiss Susan. He reached for her skirt and pulled it down her body as he continued to kiss her. She wasn’t wearing any panties. A shame, he had wanted to pull them down with his teeth.

Susan’s pussy was shaved. Tom started to lick her lips working his way to her clit. He massaged her vulva as he did so. Susan let out a slight gasp. She put her hands in Tom’s hair and grabbed hold. It was exactly like she imagined it.

Tom turned Susan around and bent her over the desk. Removing his boxers he rubbed his hard cock. Pre-cum was flowing down the side of his cock. He reached for Susan’s ass and spanked her. Susan jumped in surprise.

“Again?” She asked.

Tom spanked her again. This time leaving a light red handprint. Susan bit her lip so she wouldn’t scream. Tom put his tip on Susan’s pussy from behind and slowly worked his way into her. Susan grabbed onto the desk as she felt him enter. He filled her without any problems. She rubbed against him as she started to rock her hips back and forth.

Tom rocked with her each thrust a little harder than the last.

Susan reached to her clit and rubbed it with one hand as Tom reached around her and grabbed her left breast. He gently squeezed her nipple and rubbed her breast. Susan leaned her head back again. If he kept that up she would come soon. She continued to bit her lip as Tom continued to thrust into her.

As Susan came her legs started to shake. She held onto the desk for support. Tom continued to thrust into her. Her pussy was so sensitive now thanks to the orgasm. “Oh Tom” she said. “Give it to me.”

Tom continued to thrust. She was breathing hard now. After a few more thrusts, Tom withdrew his cock from her. he turned Susan around. Susan placed Tom’s cock in her mouth as she started blowing him. She massaged his smooth balls. In and out his cock went. Her mouth hungrily sucking on it. Tom grabbed hold of Susan’s head and held it.

“I”m coming.”

Susan moaned. Tom ejaculated. She swallowed all of his semen as she continued to suck on his cock. It was as far as she could take it.

Tom took a step back removing his cock from Susan’s mouth.

They smiled at each other as they got dressed.

Tom kissed Susan. “That was fun,.”

She nodded. “Mhhmm. We’ll have to do it again sometime.”

Tom exited her office. They both went back to work.
