\section{The Elevator}

Joe stepped into the elevator. A woman stood there holding the door open for him. He smiled to her as he entered. The elevator smelled of old mahogany and furniture polish. All things pointing to an old building.

“Thank you for holding the lift.” Joe said.

The woman nodded as she looked him over. Joe was wearing a dark grey suit with a bright colorful red tie. He was six feet tall of yummy goodness. She bit her lip as she thought about what he could do to her.

Joe pressed a button on the elevator console that would take him to his destination.

“I’m Sally” She said holding out a hand.

Joe shook her hand gently. Her skin was soft. “Joe” he replied.

Sally bit her lip. She imagined hitting the emergency button causing the elevator to stop. Imagined Joe taking her in his arms and kissing her gently, fully with tongue. Sally took a deep breath in. Her hand got closer to the emergency button. She glanced at Joe wondering if he had noticed her movement. He was too busy staring into her eyes.

Joe imagined taking Sally to his winter resort for a weekend and showing her a good time. Spreading her out on his bed, he would go down on her making her cum no less than three times before entering her. His hard cock was throbbing in his pants.

Sally had her hand on the emergency button now. She wanted to press it. She could feel her nipples tingling, her clit wanted to be licked. She wanted Joe to take her. Wanted him to tell her what a good girl she was.

Joe reached over to Sally’s hand and pressed the button.

Sally smiled.

Joe pushed Sally up against the elevator wall and pulled her panties to the floor. His cock was out and in hand.

As Joe thrust into her, Sally moaned. each thrust more forceful and deliberate than the last. Joe grabbed Sally’s ass hard as he fucked her. His cock rubbing against her clit fast and rough.

Sally grabbed onto Joe’s hair holding onto him for support. He continued to fuck her. She screamed and moaned.

A moment later, Sally came hard. Joe felt her juices rush over his penis. He smiled at her. Their hearts beating hard and fast.

Joe zipped his pants and reached for Sally’s panties that were laying on the floor. He pocketed them.

Sally raised an eyebrow and hit the emergency stop button to make the elevator start moving again.

They rode the lift in silence.

The doors opened, Joe stepped outside the elevator and turned to see Sally still smiling at him.

“Nice job counselor.” Sally said. “Let’s see how well you do before my bench in court.”

The doors closed.

Joe’s smile dropped. He had just fucked a judge.
