

\section{They Shared A Moment}

He awoke to the sound of movement... it wasn't near him, but at the other end of the house towards the guest bedroom. Where she was sleeping.

Climbing out of bed, he walked down the hallway and prepared himself for whatever struggle might be going on.

As he turned the corner, there was his guest. Nude on the bed pleasuring herself.

He smiled.

She was enjoying herself. Rubbing her wet pussy. Moaning as her other hand was rubbing her round tits. The bed gently rocked against the wall. As she rubbed her clit her pussy got wetter and wetter. She thrust a few fingers inside and then brought them up to her mouth where she tasted herself. She grinned in delight as she continued to rub her vulva.

His cock was hard as he had started rubbing it. Hoping and wishing that he would be the one that was pleasing her. His precum light at first got thicker and thicker as he stroked. Rubbing the precum up and down his shaft then around his balls. The veins on his penis pulsed with each rub. Wrapping his right hand around his cock, he squeezed and jerked his penis as he continued rubbed his balls. He could feel himself on the verge of coming. He continued to stroke until he climaxed. His cum exploding all over his hands inside of his boxers.

He must have let out a moan for her eyes were watching him now.

His face flushed as they made eye contact. She smiled at the visitor. Kicking a sheet off the bed she made sure he had a full view of the show. Her throbbing clit needed more attention, it demanded it. She rubbed her clit more and more. Biting her lip as it became more sensitive with each stroke of her fingers.

She continued to masturbate, not taking her eyes off him. Her left hand rubbing her clit, as her right hand squeezed and rubbed her perky nipples. Pulling her left breast to her mouth, she sucked on her nipple and then softly blew on it. The air hitting her nipple became cool. Goosebumps formed as she started to rub her breasts.

He watched as she arched her back, she kept watching him; kept the eye contact until she came as well.

They shared a smile as he exited the room and headed back to his own bed.

In the morning he would fuck her for sure.

