\section{The Encounter}

Steve walked up to Lilly. Looked her up and down. He could only imagine the hell she had been through. "I'll pay for this. Don't you worry."

Lilly shook her head "No, I have a check..."

Steve smiled. "Do not worry. I have it taken care of." Walking up to the front of the restaurant he paid for her meal. As Steve made it back, his bright blue eyes made contact with hers. He sat down across from her.

Lilly smiled, "That was kind of you. I can't believe that jerk stood me up like that."

Steve placed his hand on the table playing with a napkin. "Well jerks do exist in the world. I'm sorry you had to run into that guy."

Lilly nodded. She couldn't stop staring at him. it was as though she had met him before.

"Well, I'd better let you go." Steve said standing up.

Lilly smiled. "Thank you again." Taking a sip of wine, she watched as he left the restaurant.

Looking down at the table, something caught her eye. A business card? She picked it up... sure enough it was the man's business card. That sly devil wanted her to contact him. Putting the card in a safe location, she finished her meal and headed home.

The next day at work, all Lilly could think of was the stranger that helped her out from the night before. There was something in his eyes that screamed "take me now". Was she imagining it?

Lilly stared at the business card sitting on her desk. As she picked up the phone, she felt warm. Blushing as she dialed the number.

"Hello?" Steve's voice answered.

Lilly paused, almost wanting to hang up the phone.

"Hello?" Again the warm voice of the man spoke.

"Hi." Lilly finally said. "I wanted to thank you again for last night. This is Lilly." Her legs were shaking... the voice of a sexy man. She wanted him.

She could hear Steve smile. "Well hey there. Glad I could help." He hadn't expected to hear from her so quickly. He imagined what she was wearing and what he wanted her to be wearing. Or rather what he hoped she wouldn't be wearing... for the clothes, he imagined, would look better on the floor.

Lilly bit her lip. "I want to see you again."

Steve couldn't help but smiling. "Me too. What are you doing for lunch?"

Before Lilly could think, she said what was on her mind. "Sucking your cock." She froze.

Steve equally froze. Did she just say what he thought she said? "Well... that can be arranged." He said as he could feel his member perk up.

Lilly grinned. After agreeing on a place to meet, she picked up her purse and left her office.

Twenty minutes later, Steve arrived at the hotel. Room 4007 was his destination. As he made his way across the lobby he wanted to run. But he walked... quickly.

The elevator ride felt like an eternity. 1... 2... 3... finally the 4th floor. As he stepped off the elevator he could feel his heart beat faster. As he reached the door, he found it slightly open.

Steve opened the door. There was Lilly sitting on the bed. Her chocolate coffee colored skin glowed in the afternoon light. She was wearing a white blouse with a green skirt. The blouse was lightly falling off her shoulder.

As Lilly saw him, she smiled. Standing up she walked towards him.

Steve was wearing business casual. Slacks and a button up long sleeved shirt. As Lilly came near him, he held her. Placing his left hand under her skirt, he felt her thigh. His right hand at her back he pulled her in close. Feeling her back, Steve found her panty line, placing two fingers beneath her panties right on her ass he rubbed her lightly and leaned in for a kiss.

It was a deep kiss. His tongue explored her mouth, her tongue explored his. She put her right hand near his swelling cock... teasing it.

Steve continued to rub her thigh.

Pulling apart for a second, he lifted the blouse off of her and lowered her skirt down

to the floor. Lilly unbuttoned Steve's shirt and removed it. Steve kicked off his shoes and socks. He loosened his belt and unbuttoned his pants. Lilly helped him unzip them and slid them down to the ground. Steve stepped out of them.

Lilly rubbed his cock through his underwear. As his members stiffened harder, he started to precum.

"Mmmm... tiger, getting excited are you?" Lily said as she kissed him more.

Steve smiled. "Maybe..." He placed his hand inside her bra feeling her large Double D breasts. He kissed her neck again and played with her hair.

Lilly went down to her knees... and looked at Steve's cock face to... cock. Taking his underwear band in her teeth, she pulled them down. Coming back up to his cock. she licked his head then made her way down his shaft.

Steve put his hand on Lilly's head lightly.

As she reached his balls, she focused on one ball at a time. Licking, and sucking. Lightly taking a ball in her mouth... she sucked on it. mmm clean shaven... she enjoyed it. Lilly started to stroke Steve's cock up and down with her hand while tickling his balls with her other hand.

Steve moaned. "Oh baby." He said. He took a fistful of her long black hair in his hand and tugged slightly.

Taking the clue, Lilly stood up.

"Turn around." Steve said. Lilly did so. Steve held her again... putting his hard cock into her back, she could feel the mixture of

precum and saliva through her panties. Steve moved Lilly's hair to one side and kissed her neck. He cupped her breasts with both hands. Taking her bra off, it fell to the floor. Steve felt her full breasts. Massaging them. Rubbing her nipples lightly... with a little pinch to both of them. Lilly moaned.

She wanted his hard cock in her pussy which was starting to get moist with her juices.

Steve put his fingers in her panties... went to her front and ran his fingers over her smooth vulva. Soon her panties were on the floor.

Lilly led him over to the bed.

"Lay down." Steve said. Lilly laid on the bed, spreading her legs open for him.

Steve laid next to her, on her left. He traced the outline of her body. Teasing her... traced her right breast down her tummy to her thigh. Working his way across her thigh and back up the other side, tracing her breast up to her neck. Steve moved his fingers down her middle between her breasts, down back to her tummy and down to her pussy.

He gently rubbed the area right above her clit.

Lilly's breathing increased. Steve watched her chest rise up and down. It made his cock harder.

Lilly rubbed his cock... using his precum as lubricant. Steve moaned.

Lilly bit her lip.

Steve positioned himself between her legs. Kissing her inner thighs while he

placed his left hand up and played with her right breast. Lilly guided his hand as she played with her left breast. Every once in a while, she sucked on his fingers.

Steve looked up at her... her nipples were hard and erect. He lightly licked her inner thighs. Lilly started to squirm.

Taking his tongue, Steve kissed her pussy lips. Lightly parting them with his tongue. She was extremely wet. Dripping her juices. He lapped them up with his tongue. "mmm" he moaned. "So yummy."

"You like that big boy?" Lilly asked.

"Mhmm hmmm." Steve responded. Parting her pussy lips, he started to suck on her clit while humming. "hmmmmmm"

Steve then licked Lilly's clit over and over again.

Lilly's back arched in pleasure. Steve continued to lick. Every lick causing more pleasure.

"I want you in me." Lilly said.

Steve smiled. Looking up again into her eyes... they were so inviting.

Moving up, and taking his hard cock. he teased Lilly's pussy. Inserting barely, he massaged her clit with the top of his cock head. Lilly moaned. She moved her legs up in the air and wrapped them around Steve's back.

Steve moved up a little more and put his hard erect member into Lilly's wet juicy pussy. His six inches fitting perfectly into her. He started pumping.

Lilly felt his smooth balls hitting the bottom of her pussy. "Oh God!" She screamed.

Steve continued to pump her, getting harder with every stroke. Lilly grabbed the edges of the bed. Steve grabbed the headboard. He could feel her wet throbbing pussy clench around his hard cock.

They continued pumping and receiving. Sweat dripped down Lilly's back as Steve kept eye contact with her. They both were smiling.

"I'm gonna cum." Lilly shouted. "Oh God!"

Steve moaned... "mmm cum baby.... just cum."

She did. Her pussy clenched around his cock, hard. Steve moaned loudly. "Me too." Lilly grinned "Cum in me... I want it all."

Steve gladly complied. His cock started to pulse as cum released into her. He started to shake. "Oh... oh... God!" Steve screamed.

Their hearts were pounding hard. Breathing fast.

Steve removed his cock from Lilly's pussy and slid up next her. They spooned, cuddling. Lilly felt Steve's heart beating to her back. He wrapped his arm around her tummy. She held it.

Steve kissed her neck and nuzzled it as they fell asleep.

