\section{After Hours}

It was after closing hours. The lights were off. Joe walked around the building to make sure the doors were locked up tight. That’s when he noticed a light on in the conference room. Taking out a flashlight, Joe held it in case he needed to hit someone upside the head. Turning a corner into the room, he saw her.

Jessica was seated at the conference room table going over some notes. She smiled at Joe as he walked in.

“Oh, sorry ma’am.” Joe said as he saw her. “Thought everyone had gone for the night.” He put the flashlight away.

Jessica looked up from her work. “It’s okay.” She said. “I was just about finished here.

Joe looked at her their eyes locked. He smiled at her. “Very well. I’ll be out here if you need me.” He turned and exited the room.

Jessica looked down between her legs where her co worker was. His tongue was currently pressed against her pussy lips licking them. His finger was massaging her clit. Jessica put her hand on his head as he licked her. “That was a close one.” She said

The man kept licking. “Mmmhmmm” he managed to say as he licked. “Put your legs up.”

Jessica did as ordered. Leaning back in her chair she rested her legs on top of the table spreading them. Placing two fingers on her pussy she spread her lips for him. He continued to lick her, nibbling on her lips here and there. She came rather quickly. Her breathing was fast. She moaned as she came. The man continued to lick her. Taking two fingers, he put them in her vagina and stimulated her G-Spot. He continued to massage her as she was coming. Jessica came even harder.

“Don” Jessica said “Don, I can’t cum now...”

Don smiled. “Yes you can.” He continued to massage her. A moment later, he removed his fingers and pushed Jessica’s chair back. Don crawled out from under the conference table. He motioned onto the table, Jessica leaned against it. Her chest flat on the table. Don unzipped his pants and pushed her skirt up.

Don took his hard cock out from his pants and placed it against Jessica’s right ass cheek. He rubbed it there for a moment feeling his erection get harder. His balls tightened as he did so. Don spread Jessica’s legs a little farther, rubbing his cock as he did so.

Jessica bit her lip anxiously waiting to see what he would do next to her. She loved not knowing what was going on. Would he slip his engorged cock into her wet waiting pussy? Or would he force it into her ass. She wanted both to happen. She could feel her clit throbbing. Jessica wanted to reach down and massage her clit. But she knew that doing so would go against what Don had in store for her.

Don raised Jessica’s skirt up higher so he could see her perfect round ass. Licking his finger he spanked her on the right side. Then on the left. He continued this a few times. Jessica grinned as he did so. Her ass felt warm as he did so. She enjoyed it when he did that to her. Jessica loved being spanked. She loved having someone else in control of how the encounter was going.

Jessica looked back at Don. Their eyes locked. She smiled at him. He smiled back at her. “Good girl.” Don said praising her.

“Yes Daddy.” Jessica said. “Thank you Daddy.” She continued to smile as she looked forward.

Don rubbed his hard cock some more. He stroked the length of his cock starting at the balls and working his way up to the purple engorged tip. He gave his balls a slight squeeze. He was ready for her. Don picked up a condom off the table and sheathed his erect penis.

Slipping his penis into her wet vagina, Don felt her vaginal walls as he entered her. Her pussy clamped around his hard member welcoming him.

Jessica let out a gasp as Don’s cock brushed against her cervix. He was in deep. As deep as he could go.

Don grabbed hold of both of Jessica’s hips and started thrusting. In and out he went. Jessica's breasts rubbed against her blouse on the table. Her nipples were hard. She moaned as he thrust into her. Each thrust was harder than the last. Jessica loved it rough. She loved how he thrust into her knowing he wouldn’t hurt her. That trust was the best part of it all.

Don continued to thrust. As he did so, he reached down with his right hand and rubbed Jessica’s swollen clit. She moaned in pleasure.

Don came and ejaculated into the condom. He grabbed hold of Jessica’s waist as he did so.

Jessica came as well. Her pussy contracted around Don’s cock. Pleasure released throughout her body. As Don withdrew from her, she was limp against the conference room table. Don caught her as she was about to pass out.

“You okay baby?”

Jessica looked up into his eyes. “Oh yes Daddy. More than okay. You always know what to do.” She smiled at him.

Don smiled back at her. “Good girl.” He kissed her slowly as she melted into his arms.

Don smirked. After hours wasn’t a bad thing after all.

