\section{It Was All A Dream}

Night had come early. Winter was in full swing. Cold nights and winter snow storms seemed to fill the air.

Sandra didn’t mind the cold air in the house. At night she would simply bundle up with more blankets. Sandra preferred to sleep naked. She felt better that way. The blankets helped add warmth to her already warm body.

As Sandra fell asleep she began to dream. Her dreams were typical most of the time unless she had a nightmare. Tonight’s dream would be something...different.

Sandra had just gotten back from the bar where she met a guy. He was six foot tall, blue eyes and black hair. Think Superman but without the super powers. She gave him her number expecting him to call, he never did.

Oh well it was probably for the best. She didn’t want to give her hopes up on some fucker who didn’t care about her.

Sandra’s dreams would prove different though that night.

She was in the bar sitting there talking and flirting with the bartender. Most bartenders would give her a free drink if she did the right kind of flirting. It didn’t matter the gender, she had been able to flirt with both men and women equally.

Tonight Jenny was working. Sandra was pulling out all the stops, she wanted to get drunk fast.

“So, Jenny” Sandra said “what’s a nice girl like you doing in a dump like this?”

The bartender smiled at the lame attempt. This wasn’t her first rodeo. She had been hit on by patrons before all to get a drink. There was something different about this woman in the red dress though, Jenny wanted to see what made her tick, so she played along.

“Oh the usual, just paying bills. Getting by.” Jenny smiled back at Sandra as she filled a glass of beer for another customer. “You know the drill.”

Sandra did know the drill. Everyone had bills to pay. Somedays she felt as though she had more than most. But that was beside the point.

Jenny flashed Sandra a smile. They had been talking nonsense all evening. What she really wanted to know was if Sandra was interested in her. Not a relationship of course, she just wanted to fuck the girl and be done with her.

Biting her lip, Sandra watched as Jenny put a Martini down in front of her. “For me?”

Jenny nodded.

Taking a sip of the Martini, Sandra smiled. It was perfect, just as she had hoped.

Jenny continued to smile at Sandra. Soon this women would be putty in her hands, she could feel it. “Come by after work, I’ll fix you another.” She winked.

Sandra smiled. Taking her drink she left the bar and sat in a corner booth waiting for

Jenny’s shift to end. She listened to the music, watched a game here and there. Simply enjoyed herself.

A man approached Sandra’s booth. His red hair shined in the dim light. “This seat taken?”

Sandra looked him up and down. “It is now.” She patted the chair next to her.

“I’m Jake.” The man said.
“Sandra” she introduced herself. Without thinking, Sandra rubbed Jake’s

leg. He didn’t stop her. Before long, she had his hard cock out and was rubbing the shaft up and down.

Jake leaned back in his chair and moaned.

Jenny looked over towards Sandra’s direction and saw what was going on. She smiled, at least someone was having a good time in the bar.

Sandra went down on Jake. His precum tasted good. Rubbing his balls as she sucked him, Sandra could feel her pussy getting wet. She was horny and turned on.

She kept stroking until the point where Jake came in her mouth. Swallowing all of his seed, she licked her lips.

“Mmmm thanks for dessert.” Sandra said. “You may go now.”

Jake looked at Sandra as he zipped his pants up. Go? He wanted to fuck her bad. “Come on now, we can continue...”

Sandra shook her head. “No thanks, you’re not my type.”

Jenny watched as Jake left the table. Fuck. She thought. She couldn’t wait to feel

Sandra’s tongue on her clit as she ate her out. Reaching down, Jenny part her pussy lips with her finger and tasted herself. She loved the way her pussy tasted.

Sandra woke up. Her heart was beating fast. Noticing her sheets were soaked, Sandra gathered she had cum. She smiled at the fact.

Looking over to the clock she noted the time. Eleven PM. The bar was still open. Sandra hopped out of bed and got ready, Jenny would be getting laid that night. 

