\section{Christmas}
 
Looking out across the bed, I see her. She’s 
wearing a sexy santa outfit. Something from 
one of the catalogues I imagine. Whatever 
the case, I won her. She’s mine for the night. 
Fair and square I got her. (Every year the 
company auctions off willing participants 
for charity.) 

     Slipping out of her robe and stockings, 
she stands there naked before me. The 
woman didn’t even bother wearing a bra. 
What’s the use? She was going to be naked 
before she knew it anyway. Oh yes, this is 
quite the life I live. 

     She looks at me with a smile. Her hips 
swooshing back and forth. Her breasts, oh 
my her tits are amazing. She crawls onto the 
bed. Her tits are in my face now. I can’t wait 
to cum all over them. 

     Her name is Nancy, I think she works in 
account payables, but can’t be sure. It was 
her idea to fuck me, not mine. I would never 
take control over such a delicate thing like 
that. Especially since she gave herself to me 
for a good cause. 

     My cock is writhing as it waits to be 
sucked on. But first, Nancy puts her tits in 
my mouth. Well not together, they’re too big 
for that. One at a time. She moans as I rub 
my hard cock against her throbbing clit. She 
wants it. Oh how she wants it. 

     She’s moaning my name now. Over and 
over she says my name. I turn her around 
and place her on all fours. I want to fuck her 
from behind. She likes the thought of this as 
she continues to rub her juicy wet pussy 
against my cock. 

     I enter her pussy. She gasps at the size of 
my dick. I tried telling her she was going to 
get quite a treat, she had laughed at the 
thought. I think she was nervous. But oh 
well, that was in the past. 

     Fucking her feels like heaven. She moans 
and screams as my balls slap against her 
ass. I spank her. She begs for more. I 
continue to spank her until her ass is red 
with my handprint. 

     “Oh Nancy!” I yell. 

     She begs me to keep going, so I do. Now 
she’s on her back again, legs up in the air. I 
fuck her agains the headboard. She smiles 
as I do so. She’s biting her lip. Her eyes 
continue to beg me for more. I give her all I 
have. 

     I’m about to cum now. I ask her where 
she wants it. 

     “On my tits lover.” She says. “Cum all 
over my tits.” 

     Sliding out, I come up to her tits. She 
looks at my cock waiting for it. I can hear 
her rubbing her pussy. Her clit. She wants to 
cum at the same time. I don’t have a 
problem with that. 

     My balls are tight. I can feel them ready 
to explode all over her gorgeous tits. 

     I cum hard, it goes all over her tits. My 
warm juices. Some get in her mouth. She’s 
okay with that. Licking them up she smiles. 
Then her orgasm comes. It comes with a 
force. She can’t hold onto the bed. Oh my 
how she moans. 

     We’re glowing now. Climax has been 
achieved. 

     She smiles at me. I smile back. 

     “Merry Christmas” She says. I return the 
gesture and we fall asleep.

