\section{Couch Session}

Her appointment with her shrink was at 
2pm. As usual, she was prompt and ready 
for him a good ten minutes early. 

     Sitting in the waiting room, she could 
only imagine how his day was going, that 
and what she would talk to him about. Anna 
had been seeing the same doctor for the past 
seven years. He always knew what she 
needed to get her through the week. 

     "Anna?" She heard her name called out 
by the receptionist. "The doctor's ready to 
see you  now." 

     Anna stood and walked into the office. 

     As Anna entered the room, their eyes 
locked. Soon her skirt was on the floor and 
her blouse was off. Anna unclasped her bra 
and let it fall to the floor. She never wore 
panties to her appointments, they always 
got in the way. 

     "On the couch." He instructed. 

     "Yes sir." Anna responded. "Anything you 
say Daddy." The word Daddy rolled off her 
tongue. She needed to be spanked, fucked, 
and anything else he wanted to do to her. 
She wanted it all. 

     Anna kneeled on all fours on the couch. 

     Taking his hard throbbing cock out of his 
pants, the doctor gave her what she needed. 
Grabbing onto her hips, he licked his fingers 
and then rubbed his cock. Finally he slid 
deep into her. 

     Anna wanted to scream in pleasure, but 
knew people could hear outside the room. 
So she kept quiet. 

     Daddy could feel her tight pussy around 
his hard member... she was nice and wet. 
"Such a good girl." He said as he continued 
to thrust into her as deep as he could. 

     He spanked her ass, hard. Anna jerked 
forward and smiled. Biting her lip, she 
begged. “Please again Daddy? Again for 
your baby girl?” 

     The doctor kept thrusting and spanking 
her. He was sure people could hear the 
spanking, but that didn’t matter. He was 
having fun. Anna was having her fun as well. 

     He came almost immediately but kept 
thrusting until she came. 

     As she climaxed, Anna grabbed the 
couch. Her nails digging into it. "Oh yes 
Daddy, fuck me." She whispered. "You 
always know how to take care of me." 

     He kept going until he felt Anna had her 
medicine. Sliding out of her, he wrapped his 
hand around his dick and rubbed. Lifting 
his fingers up to his mouth he licked and 
sucked off her juices. “Mmmm” He said, 
“You taste good. Daddy likes the way you 
taste.” 

     Standing up, Anna got dressed and 
waited for instructions. 

     The doctor took out a prescription pad 
and started writing. "I need to see you next 
week. The usual time." He handed her the 
slip. 

     "Yes Daddy. Thank you Daddy." Anna 
said as she exited. 

     Sitting down at his desk, he pressed the 
intercom button. "Rose, please come in 
here. I have something that needs your 
immediate attention." 

     Daddy was horny that day, he needed 
someone else to fuck.

