\section{Baby Girl}

    It was late after work, a long day. I walked in the door ready for a night of relaxation. Babygirl stood at the stairs. Her pacifier in her mouth, sucking on it. I imagined she was sucking on my cock. The one she loved so much.

    “Hi baby.” I said as I walked up to her and kissed her.

    “Papa!” Baby replied as she hugged me. “I missed woo so much!”

    I missed her too. Hadn’t seen her since the morning. We walked into the kitchen, Baby sat down at the table. “I want to color!”

    We shared a smile. I loved it when she wanted to color. I got out her pencils and her coloring books so she could choose which one she wanted to color in. She had other things in mind. Tossing the coloring books to the floor, Baby cired. “No! None of thowse. I want different!”

    Unfortunately we didn’t have any different coloring books. I tried to explain it to her. That’s when the binkie came out of her mouth and landed on my shirt. I picked up the binkie and handed it back. “Here you go little one.”

    “No!” She tossed the binkie again.

    I wasn’t sure if she was being a brat on purpose, or what. Picking up the binkie, I placed it in her mouth. “Here you go baby.”

    Again the binkie came out. “No.” She said.

    Putting my hand under her chin I smiled gently. “I see.” Taking her by the hand I helped her stand up. Over my knee she went. *Spank*

    Baby’s bottom wiggled.

    *Spank*

    Again more wiggling.

    You like that do you? I thought. She grinned back at me.

    Taking her upstairs I motioned over to the bed and handed her the binkie again. “Take this.”

    She gladly took it in her mouth.

    I dropped my pants and let my cock breathe. She ran her fingers up and down my shaft caressing my balls. “Want! Want!”

    Turning her around, so her diapered ass was facing me, I rubbed her bottom and pulled the diaper to the side. Her cunt was dripping wet. She really was excited to see me. I licked her pussy and she moaned.

    Sliding in, I started to thrust in and out. Slow at first and gradually getting faster and harder. Babygirl held onto the bed hard as I fucked harder.

    “Oh fuck Papa!” She moaned.

    I spanked her. She was my slut, just like I was hers. Together we were one. I fucked her harder. Her pussy gripped onto my cock. I lurched forward, hitting something. Her cervix.

    Baby moaned. “Yes Papa! Moar Moar!”

    I continued to fuck her. “I’m almost there” I moaned.

   “Me too!”

    “No” I said. “No cumming.”

    Baby looked behind her at my smile. “Yes Papa.”

    Sliding out of her, she came around and sucked on my cock. Tasting herself, she moaned some more. “Mmmmmm” I fucked her face. What a good girl she was being for Papa.

    When I started cumming, babygirl sucked harder. My cum flowing down her throat. What a good girl she was. Taking my entire load in her mouth not missing a drop.

    She laid down after taking it all. “Mmmm thank you Papa.”

    I held her. Running my fingers through her hair. “Shhh, good girl. My baby girl.”

    We wrapped up in a blanket and cuddled talking about our days, and the night to cum.

