\section{Papa's Silly Cock}

Papa walked into the living room where babygirl was playing with blocks. Kneeling down next to her he ran his fingers through her hair. 

"Hi Papa" she smiled. 

"Hi baby" he kissed her forehead. "Having fun?"

"Oh yes Papa. I building and smooshing" she toppled the blocks over. 

Papa laughed. He loved when his baby played. 

"Uh oh" babygirl said. 

Papa looked up from the blocks. "What's wrong?"

Baby stood up and pulled Papas hand. "Dis way. I show woo."

Papa bear followed her to her bedroom. 

Babygirl kneeled before Papa and pulled at his pants. "Want it out" she said. "Gimme."

Papa unzipped his fly. His cock worked its way out of his boxers. "This?"

"Yes Papa" she rubbed Papas cock. "Uh oh" babygirl said again. 

"Lay down" Papa said. "Time for a changing."

"Yes Papa"

Babygirl laid down as instructed. It was exactly what she needed and wanted. 

Pulling back the diaper, Papa smiled. He loved baby girls cunt. Soft and delicious. Taking a wipe he rubbed her cunt gently. Then got the powder out and applied it. 

Babygirl soothed. "Yes Papa yummy. Thank woo Papa."

Papa smiled. He loved taking care of his babygirl. She deserved the best. 

Babygirl yawned. "Nap time Papa?"

Papa nodded. Yes. 

Babygirl grabbed her blankie. "Okay Papa let's go."

Snuggling into bed, Papa fell asleep. Babygirl looked at Papas naked Cock and giggled. She rubbed it. It would bounce up and down. Again she would giggle. 

"Papa silly. "

Taking his cock in her mouth, Babygirl sucked and sucked. Licking it, precum started to flow. "Oh yummy Papa" she said as she sucked more. 

Papa moaned in his sleep. 

Babygirl continued sucking harder. She kept sucking until Papa came. Swallowed his load, she giggled. Papa silly. 

Babygirl fell asleep next to Papa and they enjoyed a nap together. 

