\section{Shower Time}

Kitten stepped into the shower, it had been a long day. As the hot water hit her skin, she smiled. It felt good. Kitten scrubbed and washed her hair and her body. Focusing on her breasts and down her thighs. Wishing Papa had been there to help her out.

    Getting down to her cunt, Kitten moaned. She needed Papa’s special touch.

    Papa walked in the door. “Kitten?”

    “Papa!” Kitten said. “You came.”

    He smiled as he got undressed. “Thought I might help you out.”

    Kitten grinned. “Oh yes Papa. Oh yes.”

    Papa opened the door to the shower and stepped inside. Walking up behind Kitten, he pressed his cock against her ass and reached around to her tits.

    “Papa loves you Kitten.” He whispered into Kitten’s ear as he nibbled at her neck. “Papa is always here for you.”

    Kitten smiled and squirmed. “Thank you Papa.” She handed him the soap. “Wash my back?” Kitten rubbed her ass against Papa’s hard cock.

    Papa took the soap and rubbed Kitten’s back with it. She reached behind her and grabbed Papa’s cock.

    “Papa, it’s so hard.”

    “Only for you Kitten.”

    “Dawww Papa, you know what I like.”

    Papa nodded. “Yes I do, and Kitten knows what I like.”

    Kitten rubbed Papa’s cock and played with his balls. “Papa, hold me.”

    Papa returned the soap to its container and held Kitten close. “Always Kitten. Always.” He held her and whispered into her ear. They shared a soapy moment. A lovely moment. Papa reached down and played with Kitten’s cunt.

    “My cunt.” Papa said.

    Kitten nodded. “Yes Papa.”

    Papa reached for Kitten’s hand and placed it on his cock again.

    “Your cock.”

    Kitten smiled. “Yes Papa.”

    Papa nodded. “Good girl.”
