\section{Naughty Baby Girl Part 3}

     Stepping out of the shower, Kitten and Papa kissed all the way into the bedroom. They couldn’t keep their hands off each other.

     Papa led Kitten to the side of the bed where he sat down, she kneeled in front of him.

     Taking Papa’s cock into her mouth, Kitten stroked it with her tongue and caressed his balls. Papa moaned as she did so. He ran his fingers through Kitten’s hair. Such a good girl she was.

     Kitten moaned as precum flowed into her mouth. Papa tasted sweet, like honey. Kitten licked and licked around Papa’s cock head. She loved that taste.

     Papa pulled kitten up and kissed her starting with her neck, he worked his way down her body. Kitten squirmed. “Oh Papa!” She said.

     Kissing her stomach, Papa fingered her wet cunt. Kitten continued to squirm.

     Taking his fingers out of Kitten’s cunt, he put them up to her mouth. “Taste.”

     Kitten nodded “Yes Papa.” She moaned as she licked his fingers clean.

     Stroking Papa’s cock, Kitten continued to play. Faster and harder she stroked hoping Papa would cum for her.

     Papa leaned back and moaned, exposing his ass.

     Kitten placed a finger in his hole and probed a bit. Getting lube, she explored more.

     Papa squirmed. Kitten stroked and probed. Papa moaned.

     Papa started to cum, Kitten continued to stroke as she got a mouthful of cum. Swallowing it, she smiled. “Oh Papa.”

     Papa shook from the orgasm. She was hitting all the right spots in his bum.

     Looking up, Papa smiled. It would be Kitten’s turn next.


