\section{Conscent}

Kitten walked around her house in her nightie. It had been weeks since she and Papa had made the agreement. Every night, she waited hoping that night would be the night; and every night she would have to wait another night.

     Candles were lit in the bathroom as she slipped the nightie off. Her naked skin exposed to the fresh breeze coming in through the window. Her nipples perked up, the night felt nice. Slipping into the bathtub, Kitten smiled at the hot bath. She let the water flow over her. Kitten’s cunt felt good as the water surrounded it. She moaned as she felt her cunt. It needed Papa’s touch.

     A man entered the room. Kitten looked up and smiled. “Papa.”

     Papa grabbed Kitten by the arm and pulled her towards the bedroom. Kitten pretended to resist for a bit, but gave in.

     Tying her up to the bed, Papa ran his fingers along Kitten’s legs.

     “There’s my slut.” Papa said. “My good little cum bucket.”

     Kitten’s heart was racing. “Oh god.” She said.

     Papa took out a ball gag. “No talking.” He placed it over Kitten’s mouth.

     Now she couldn’t talk and could barely squirm. Papa dropped his pants. His cock was pulsing with excitement. He rubbed the tip, precum was nicely flowing down his shaft. Papa rubbed kitten’s thighs.

     “Now you’ll see what kind of whore Papa wants from you.” Papa said. He smirked.

     Kitten tired to arch her back but was unable to.

     Papa licked Kitten’s wet dripping cunt. He teased her with the tip of his cock until he thrusted it into her.

     Pleasure flowed through Kitten’s body. She moaned.

     Papa continued fucking Kitten. Raw. Hard. Fast. He rubbed her clit as he thrusted. Kitten was his toy for the night. His fuck toy.

     Kitten quivered. Papa could tell she was ready to cum, he spanked her clit with his hand and pinched lightly. Kitten shook.

     “Not yet.” Command Papa. “I’m not ready for you to cum.”

     Papa continued fucking Kitten. He thrusted into her, her hips wanted to thrust back. Her perky nipples wanted to be groped and touched. Papa did so. Biting her nipples, he moaned.

     A moment later, Papa untied Kitten and forced her onto all fours. Kitten complied.

     Entering from the rear, Papa eased his cock into Kitten’s ass. Fucking her and rubbing her clit, Papa continued to fuck her.

     Kitten grabbed onto the bed for support. She clenched her ass against Papa’s cock. Her cunt dripping wet.

     Papa smiled. “Kitten needs all holes filled.”

     Kitten nodded.

     Papa pulled her hair. “Good slut. My slut. My whore.”

     Kitten moaned.

     Papa reached for Kitten’s pink vibrating dildo and forced it into her waiting cunt. Kitten moaned as he started the vibrations.

     Kitten wanted to cum but knew she couldn’t, not until Papa said for her to.

     Papa continued thrusting into her ass.

     Kitten breathed heavily. “Oh God!” She thought. “Fuck me Papa!”

     Papa continued to fuck her hard.

     Coming out of her ass, Papa washed his cock off. He made kitten wait for what came next.

     Turning kitten around, Papa removed the ball gag and thrust his cock down Kitten’s throat. He fucked her face.

     Kitten’s cunt trembled.

     Papa continued fucking her face until he came inside her mouth. His cum dripping down Kitten’s throat.

     Kitten sucked Papa’s cock dry.

     Papa leaned back on the bed, Kitten was at the other end moaning.

     Papa smiled. “Cum for me.”

     Waves of ecstasy filled Kitten from her cunt to her tits down her ass. She trembled as her orgasm reached its peak.

     Papa smiled. “Good little slut.”

     Kitten nodded. “Thank you Papa.”

     Papa continued to smile. “Welcome my baby. Welcome.”
     He held her. Kitten’s fantasy had only begun.
