\section{The Breeder}

     It was date night. Papa and Baby Girl went out to dinner. She wore a black skirt with a light blue top. Underneath her skirt was a diaper, which only her and Papa knew about.

     The waitress came over to their table. “Hello folks, what can I get you?”

     Papa ordered, “I’ll have a whiskey, my girl will have a glass of milk.”

     The waitress nodded. “I’ll be right back.”

     Baby Girl looked to Papa. “Didn’t know you waz gonna have grown up drink.” She pouted.

     Papa smiled. “Did you want something Baby Girl?”

     Baby nodded. “Yes Papa. Me want Whiskey.”

     Papa pulled out a handkerchief and slid it over to Baby Girl. “Here, change into this and you can have a grown up drink.”

     Baby’s eyes lit up. “Okay Papa!” She stood from the table and went to the bathroom.

     The waitress came back with the drinks.

     Papa looked at the milk. He took it over on his side. “Actually I’ll take the milk as well. She will also have a whiskey.” Papa hated when his heartburn flared up. Milk had a way of calming it.

     The waitress nodded. “Understood.”

     In the bathroom, Baby Girl undid her diaper. She looked in the handkerchief. Her small plug was staring back at her. Angel moaned at the thought. Papa wanted her bad, she could tell it.

     Putting the plug in, Angel smiled. Felt just right. Filled her tight hole. Papa would fill the other one later for sure. She bit her lip. Tossing the diaper away, Angel left the bathroom.

     She joined Papa for a drink.

     “Comfortable?” Papa asked.

     “Yes, very comfortable.” Angel replied. “Thank you.”

     Papa kissed Angel’s hand. “Welcome darling.”

     Dinner went as expected, the couple wanted alone time. Lots of it. By the end of the meal, they couldn’t keep their eyes off each other, or their hands.

     Walking through the front door, Papa and Angel were kissing, groping each other, and couldn’t be contained.

     Papa smiled. “Feisty tonight.”

     Angel nodded. “I’m your whore Papa. Do with me as you please.” She knelt down in front of Papa. Her plug reminding her it was still in.

     “Strip.” Papa said.

     Angel did without hesitation. Down came the skirt, off came the blouse and the bra. Her shoes went flying against the door.

     Papa smiled. “Good Girl.”

     “Thank you.”

     “You’re welcome.”

     They made their way to the bedroom. Papa in the lead, Angel crawling on the floor. Papa had a leash out and was leading her. “I’m bringing you in here for one reason.”

     “Yes Sir.” Angel said.

     Papa took the leash off. “I am going to fill you with cum. You are my breeder.”

     Angel’s cunt quivered. She was wet. Hungry for Papa’s cock.

     “Position.” Papa said.

     Angel, without hesitation, laid down on the bed with her legs stretched.

     Papa walked around the bed as he striped his suit off. Taking his tie, Papa tied Angel’s hands to the bedpost.

     He walked back around to the front of the bed and inspected his property. Angel’s cunt was dripping wet. Papa licked her sweet cunt. Angel moaned. He smiled. Papa loved when Angel felt good. He was hoping she would feel real good by the time the night was over.

     Rubbing his hard cock against Angel’s cunt, he teased her. “Hungry for cock baby?”

     She nodded. “Yes Sir.”

     Papa nodded. “Good.”

     He thrust the cock into her wet, delicious cunt. Angel squirmed and moaned. It felt so good. She licked her lips.

     Papa continued to thrust. Each thrust getting harder than the last. Angel screamed. “Oh FUCK! Yes Papa, take me. I’m your whore!”

     Papa smiled. “Good Girl!” He said. “Mine.”

     Angel nodded. “Yes yours.”

     Papa continued fucking her. “Your cock.”

     Again, Angel nodded. “Yes, my cock.”

     “My cunt.” Papa said.

     “All yours.”

     Papa continued to thrust, he was hitting her cervix. His balls slapping against the plug. He came deep inside her. As far up as he could go.

     Angel came as well.

     They moaned together.

     Papa laid next to Angel. He watched her breasts rise up and down rapidly.

     “How are you feeling?”

     Angel nodded. “Good Papa. Your slut is good.”

     Papa nodded. “Good Girl.” He kissed her. “We’ll do it again in an hour.” Papa said. “I’m gonna fill you up so good.”

     Angel smiled. “Thank you Papa.”

     Untying her, Papa ran his fingers through Angel’s hair as she stroked his cock. She would let him know when her cunt was ready for more of Papa’s cum. He’d be ready for it.


