\section{Naughty Baby Girl Part 4}

     Baby was at the table as Papa was making lunch. Putting a bowl of smooshed peas in front of Baby, Papa told her to eat.

     She looked at the peas and turned her nose at it. “No Papa.” She pushed the bowl away from her.

     Pushing the bowl back, Papa shook his head. “No Baby, you must eat.”

     Baby picked up the spoon and flung a chunk of pea at Papa. She giggled.

     Taking a towel, Papa wiped his nose off. “That’s not nice.”

     “It funny” she said giggling.

     Papa tried again to feed her.

     Again, Baby flung food at Papa.

     Papa wiped his forehead off. This was getting silly.

     Taking Baby over his knee, Papa spanked her. “No throwing your food.”

     Baby looked down. “Hard.”

     Papa sighed. Yes he had an erection. His baby girl had noticed.

     “Milk.” Baby said.

     Papa unzipped his pants and let his cock out.

     Baby rubbed papa’s cock with her fingers. “Sticky.”

     Papa nodded. “Yes baby, it’s sticky.”

     Taking some precum up to her mouth, Baby moaned. “Good.”

     She got on her knees and sucked papa’s cock. She would stroke and suck and suck some more. “Give it to me papa.”

     Papa didn’t argue. He let her service him. He loved when she was eager. Such a good girl.

     “Papa’s gonna cum soon.”

     Baby nodded. “Mmmmhmmm.” She stroked faster and sucked harder. “Give it to me papa.”

     Papa’s cock came hard. All inside baby’s mouth. She sucked it down like a good slut. Papa moaned. Baby moaned.

     “Yum Papa.” Baby said. “Yum.”

     Papa nodded. “Good Girl.”

     Standing up, Papa helped Baby to her feet.

     “Now it’s baby’s turn.”

