\section{Naughty Baby Girl Part 6}

     “Road Trip!” Papa yelled from the bedroom.

     Baby’s ears popped up. Woad Trip? Woad Trip! She dropped her blocks and came running.

     “Papa?” Baby girl said as she entered the bedroom.

     Papa was packing clothes. “Yes baby?”

     “Where we goin?”

     Papa smiled as he placed a black dress in the suitcase. “We’re going to drive somewhere, and then we’ll stop for food and a night sleep and drive back.” It was a simple getaway. Just the two of them.

     Baby jumped up and down “Woad Trip! Yay! I go get my bear.”

     She left the room.

     Papa smiled. He loved when baby was happy.

     An hour later, they were on the road.

     Baby looked out the window with excitement. Not knowing where they were headed made it exciting, that and the fact they were just going somewhere. It was all the fun.

     “Papa?”

     “Yes baby.”

     “When did you get a stick shift?”

     Papa looked at baby. What was she talking about? “We don’t own a stick shift hon.”

     Baby unzipped Papa’s pants and pulled his cock out. “What’s this? Looks like a stick shift to meeeeee.” She rubbed Papa’s cock.

     Papa moaned. “Baby” he said “we’re driving. Here?”

     Baby nodded “Yes Papa. Baby wants to play!”

     Papa smiled. He wasn’t about to say no. “Okay baby, baby can play.”

     “Yay!” She continued to rub Papa’s hard cock. Using his precum as lube, she rubbed it up and down his shaft. Baby wished she could put it in her mouth, but that would happen later that night for sure.

     “Oh Papa.” She said. Papa moaned some more.

     “Baby girl like?”

     Baby nodded. “Yes Papa! Yes!”

     “Good.”

     As she continued rubbing, Papa was breathing fast. “Papa’s gonna cum baby.”

     Baby was focused on rubbing, she didn’t listen.

     As Papa came all over baby’s hands he chuckled. “Oh baby.”

     “Uh oh!” Baby said. “Papa spit.”

     Papa nodded. “Yes, yes he sure did.”

     “Sowwy Papa” Baby said.

     Papa shook his head. “It’s okay baby. Let’s get cleaned up shall we?”

     “Yes Papa.”


