\section{Shower Time}

Walking into the apartment I took off my jacket and tossed it on the couch. "Jen?" I called out.

There was no response.

Walking around, I heard the shower running. I slipped off my shoes and loosened my tie. I loved shower time, it was always a fun experience.

By the time I made it to the bedroom, my shirt was unbuttoned and my pants were on the floor. Kicking the pants aside, I tossed the shirt into the laundry hamper.

Opening the door to the bathroom, I took a peek in. There she was singing away. I removed my boxer briefs. They dropped to the floor as I stepped out of them. I stood there nude waiting for her to take notice.

She continued singing. "I'll give you something to sing about." I whispered.

I opened the shower door.

Startled, Jen turned around. Her nude body facing me, her tits staring me down. Her hips inviting me. "Mike." She said as she bit her lip between words.

I smiled. "Hi baby, thought you could use a pick me up."

She grinned. "Yes please."

Walking into the shower, I closed the door. Starting with her neck, I kissed her. My hands exploring her body. Her bare ass, her breasts, her hips. Oh my her hips. I rubbed her all over feeling her moan. I

worked my way down her body. My penis becoming erect as she stroked it.

Grinding my hard cock against her wet pussy, wet because of the shower and wet because of my teasing, I pressed against her. Taking her hands, I pushed them against the wall and ground against her more. She moaned and whimpered.

Jen wasn't ever a fan of the teasing, she wanted it all and wanted it now. I knew this and it was my plan to tease her for a bit longer.

"Mike, please." She said "Just fuck me, fuck me hard. Now."

Feeling down to her pussy, I slid a finger in, then another finger in. Teasing her clit with each stroke of my fingers. She grabbed the back of my neck and then reached down to my balls. She rubbed them, squeezed them, tickled my penis with her fingertips. My penis welcomed her touch. At that moment, I couldn't take the teasing myself anymore.

Picking her up, I leaned her against the shower wall and started to fuck her. She grabbed onto my back for support as I thrust harder and harder.

"Oh god!" She screamed. "Yes! More!"

I continued to fuck her harder until she came.

Winking, I kissed her again. "Time to go back to work."

She pouted. "Why?"
I simply grinned. "Lunch time is over...." "I don't recall you eating me out." She

said, covering her chest with her arms. Her

arms catching the water that was pouring down her breasts.

"That's tonight for dessert." I smirked as I left the room. I could only imagine what was going on through her mind. Hopefully it was anticipation for later that night. She was going to get it. She was going to get it good.

