\section{Water Park}

    Angel walked into the water park, she was going to have a blast of a time. Changing into her swimsuit, Angel went down a slide, there she caught the attention of a lifeguard. He was handsome and he was looking her up and down.

    She smiled and waved at him shyly.

    He waved back.

    Every side she went down, the lifeguard seemed to be there watching. Waiting if she or anyone else in the park needed rescuing.

    Angel imagined him giving her mouth to mouth...and then some.

    She played in the water and relaxed. It rushed over her body. Talk about a perfect day.

    Running around in the splash fountain, Angel found herself face to face with the lifeguard.

    “Hi.” He said.

    Angel smiled back. “Oh hi there.”

    He gestured to a door. “Wanna get out of here?”

    She nodded.

    Leading her to the door, the lifeguard led Angel to the employee hot tub.

    Angel stepped into the tub and sat down. It was relaxing.

    The lifeguard did as well.

    “Having fun?”

    Angel smiled. “Yeah, even better now that you’re here.”

    Placing a hand on her knee, the lifeguard leaned forward and kissed Angel. Their tongues met and danced with each other. Angel rubbed his leg, leading up to his cock.

    With her hands down his shorts, she jacked the lifeguad. He slipped her swimsuit off around her shoulders and down her legs.

    His cock was hard.

    Angel straddled the lifeguards cock. Up and down she went in the water fucking him. He moaned in delight and pleasure. She moaned as well.

    Cupping her tit, the lifeguard brought it to his mouth and sucked on it. It led to biting. Angel moaned more. “Oh yes.” She said. “You know just what I like.”

    He continued thrusting into her. Fucking her sweet cunt.

    Angel rode harder.

    “I’m cumming.” The lifeguard said.

    Slipping off his cock, Angel watched as he lifted himself out of the water and came all over her gorgeous tits.

    She licked her tits. He tasted sweet.

    “Mmmm” Angel said.

    The lifeguard smiled as he spread Angel’s legs and fingered her. Slipping in and out of her cunt, rubbing her clit. She moaned as she came.

    They held each other in the hot tub. Kissing each other.

    It was indeed a perfect day.

