\section{Naughty Baby Girl Part 14}

    Making a fire, Papa smiled. “That should do it.”

    Baby girl shivered in the cold. “Paaappaaa.”

    Papa sat down next to her and embraced her. Rubbing her back and arms, he nodded. “It will be warm soon enough.

    “Promise?”

    “I promise” Papa said.

    “Good” Baby girl replied.

    Sure enough, it started to warm up quickly.

    Baby girl bit her lip. There were things she wanted Papa to do to her. Oh how she wanted him to just take control and ravish her.

    Papa brought out marshmallows, he looked at baby girl. She didn’t seem to want them, she wanted something else.

    Walking over to baby girl, Papa nodded. “Strip, now.”

    Baby girl’s eyes lit up. “Yes Papa.”

    Dropping her skirt to the ground, baby girl removed her blouse next. Then off came her socks. She stood before Papa with a bra and panties on.

    Papa ran his fingers along baby girl’s hips as he adjust her panites down her legs, next her bra came off. He moaned.

    Leading baby girl over to the flat rock, Papa smiled. “Lay down.”

    Baby girl laid down and spread her legs for Papa to inspect her.

    Papa rubbed baby girls wet cunt. He was in charge, she knew this, she craved this. Licking his fingers, he smiled. “You taste good baby girl.”

    Baby girl moaned. “Thank you Papa.”

    “Welcome baby girl.”

    Papa stripped naked, his hard erection was waiting. Slowly rubbing his cock against baby girl’s clit, she squirmed.

    “What’s Papa going to do?”

    “Breed you.” Papa said.

    Baby girl arched her back. “Oh yes Papa.”

    Papa thrusted his hard cock into baby girl’s tight waiting cunt. Each thrust more deliberate than the last.

    Baby girl held onto the sleeping bag so she wouldn’t fall off the rock. “Oh god!” She squirmed.

    “You’re my cunt. Baby girl.”

    She nodded “Yes Papa.”

    “My whore.”

    “Yes Papa.”

    “My cum bucket.”

    “Oh yes Papa!” Baby girl screamed.

    Papa thrusted harder. “I’m going to fill your cunt with my seed baby girl.”

    “Mmmm yes Papa.”

    Papa fucked her. Raw. Hard. their raw emotions flowed back and forth to each other. She was his, he was hers. There was no one in the world but them.

    Baby girl rocked her hips with each thrust. “Oh fuck me Papa.”

    Papa continued to fuck her. Hard. He could feel her cunt tighten around his cock. He wanted her to cum hard. So hard.

    Baby girl moaned. “Can I cum Papa?”

    “Almost baby girl. Almost.” Papa said.

    Baby girl moaned. She loved when Papa told her when to cum.

    Papa held onto baby girl’s hips and continued to fuck her.

    “I’m almost there baby girl, I want us to cum together. Understand?”

    Baby girl nodded. “Yes Papa.” She was breathless.

    Papa shoved his cock in her hard, it rubbed her cervix. “I’m coming.”

    Baby girl allowed her own release.

    They trembled together on the rock as they came. Papa and baby girl. Locked in each others embrace as one.

    Nothing could be heard but their breathing. The only two people in the world.

    Laying down, Papa smiled at baby girl as he cuddled her.

    Baby girl smiled back.

    “Thank you Papa.”

    Bab nodded. “Welcome baby girl.”

