\section{Naughty Baby Girl Part 15}

     Baby and Papa woke up to the sun coming over the horizon. It had been a peaceful night. Their naked bodies still entwined from the pleasure they had.

     Laying her head on Papa’s chest, baby felt secure. Safe.

     Papa smiled as he ran his fingers through her hair. She was such a good baby girl. He kissed her forehead.

     “Papa” baby said “There’s one fantasy, we haven’t explored yet.”

     Papa nodded. “I know.”

     Baby girl teased Papa’s nipples with her fingertips. Her cold fingers caused his nipples to go erect.

     Papa looked at baby girl and smiled.

     Turning her on her back, Papa held down her arms. “This what you want?”

     Baby girl nodded. “Oh yes Papa.”

     Papa rubbed his cock against baby girl’s legs. He fingered her a little, feeling her wetness. “Baby girl’s wet.”

     Baby nodded again. “Yes Papa.”

     Papa entered her. His hard cock pulsing into her cunt. Fucking her hard. He held a hand over her mouth as she moaned in pleasure.

     “Good girl.” Papa said.

     Baby girl smiled.

     Placing his hand on her breast, Papa squeezed gently. His mouth soon found its way to her perky nipples. He sucked on her tits.

     Baby girl squirmed and moaned more. “Fuck me Papa.”

     Papa fucked her hard. Her legs in the air, he fucked her over and over again.

     It didn’t take long for baby girl to cum. She laid there pulsing as her orgasm took hold.

     Papa kept thrusting. “Good girl.” He said. “Good girl.”

     Baby girl let out a loud moan. “Oh Papa!”

     Papa smiled. He loved when baby girl felt good, and loved it even better when he was the one pleasuring her.


