\section{Naughty Baby Girl Part 16}

     Getting dressed, baby and Papa decided to go on a short hike. Mostly just walking through the forest to see all that was there. Trees. They found lots and lots of trees. Oh and rocks. Yep, rocks were to be found as well. It was a forest, what did one expect?

     Walking along, they talked and held hands. It was a wonderful get away.

     They came across a natural hot spring. There was a part that was not as hot as the others. Papa stripped his clothes off and sat down in what appeared to be a natural hot tub.

     Baby did as well.

     They made out, their tongues locking and dancing around each other. Papa licked his way down baby’s body. Feeling every inch of her. He guided her hand to his hard cock.

     Baby rubbed Papa’s cock. It was def hard. She rubbed his smooth balls and played with them in her hand. She continued to kiss Papa moaning.

     Papa continued to let his hands roam over baby’s body. Squeezing her ass. Her tits. He licked, sucked, and caressed her tits. Baby leaned back as Papa kissed down her neck.

     “Turn over.” Papa said.

     Baby did as told.

     Placing his hard cock in baby’s ass, Papa fucked her. Baby held onto the side of the rocks for balance as she was fucked.

     Papa kept fucking baby. She rubbed her clit with her fingers and then fingered herself. Papa kept thrusting.

     Baby came. She moaned. “Oh Papa!”

     Papa continued fucking her tight ass. He fucked her hard. They were one in rhythm.

     As Papa came, he grabbed baby girl’s hair and pulled. He moaned loudly.

     Baby girl too moaned.

     Settling down from their orgasms, Papa and baby cuddled each other in the pool of warm water.

     “Good girl.” Papa said.

     “Thank you Papa.” Responded baby.


