\section{Naughty Baby Girl Part 17}

     Papa and baby girl drove back home. The camping trip had been a success. Orgasms were had. Laughs were had. They enjoyed each other’s bodies. It was heaven.

     Entering home, Papa looked at baby girl. “I’m gonna grab a shower.”

     Baby followed him into the shower.

     Papa turned on the water, nice and hot.

     Baby girl stripped out of her clothes and held Papa from behind.

     She rubbed his crotch feeling as his cock got hard.

     Papa turned around, he too stripped out of his clothes and embraced baby girl.

     They kissed. Papa grabbed baby girl’s ass and gave it a squeeze.

     She squirmed.

     Stepping into the shower, they couldn’t keep their hands off each other. Papa massaged baby girl’s tits as she played with his balls. Soaping each other up, they cleaned the camping off of them.

     Papa washed baby girl’s hair. She giggled. “Yay.” It felt good.

     Baby girl sucked on Papa’s cock. She didn’t stop. His smooth balls pressed against her chin, which she gladly licked with her tongue. Papa held onto her head as he fucked her face. She moaned.

     Baby girl played with her clit as Papa face fucked her.

     As he came, his cum dripped down baby girl’s throat. She licked up all of it not missing a drop.

     Papa turned baby girl around and fucked her from behind. She held onto the shower wall for support.

     “Oh yes Papa.”

     Papa fucked her hard, rubbing her clit from behind as well. Making sure baby girl had three orgasms before the shower was over.

     “Mmmm thank you Papa.”

     Papa nodded. “Night’s not over yet kitten.” He grabbed the handcuffs.


