\section{Naughty Baby Girl Part 19}

     Papa sat at the table waiting for baby girl to come home from her shopping trip.

    As she entered the house, baby girl put down her bags and walked over to Papa. They kissed. Papa held baby girls hand. 

     She sat on Papas lap. Papa bounced her on his knee for a moment. She giggled. "Hi Papa"

    "Hi baby girl." Papa said. He kissed her neck. "Have a good time shopping?"

     Baby girl nodded "Oh yes Papa."

     "Good." Papa said. 

     Baby girl kept bouncing on Papas knee. She rubbed her belly. "Papa, I hungry."

     Papa reached over and picked up a bottle he had ready for her. Leaning baby girl back, he put the bottle in her mouth. Baby girl sucked on the bottle. 

     "Mmmmm, thank you Papa."

     "Welcome baby." Papa said.

     "Papa?"

     "Yes baby?"

     "I feel poke poke."

     Papa chuckled. Yes he was hard.

     Papa slid baby girls pants down. She was wearing her diaper. Unzipping his fly, he felt her wetness against his throbbing cock. He bounced her on his knee again and slid into her. 

     Baby girl gasped. "Ohhh Papa."

     Papa thrusted gently and kept thrusting. He pulled baby girls hair. She moaned. Baby loved when Papa took control.

     Papa groped baby girls tits. Her nipples were hard.

     "Oh Papa" baby girl said. "I have cummies?"

     Papa shook his head. "Not yet baby girl." He continued to rub her tits. Baby girl continued to moan.

     As Papa thrust, baby girls clit throbbed. She moaned louder. Papa smiled. His girl was enjoying it. He loved when she enjoyed it.

     Papa licked baby girls neck.

     He kept thrusting. "Cum for me baby girl."

     Baby came hard. Papa continued fucking her. She came again and again.

     Papa thrust again. He was about to cum  himself. He held on tight to baby girl. She moaned. 

    They came together. Her cunt clenched around Papas cock. His cock jumped inside baby girls cunt. His seed went into her. 

     Papa gasped as his orgasm filled him.

     Baby girl kept bouncing on Papas cock.  She moaned. 

     Taking baby girl in his arms, Papa took her to the next room where they laid down and snuggled together. It was a beautiful day.

     "Love you baby"

     "Love you Papa"

