\section{Naughty Baby Girl Part 20}

    Baby girl walked down the street, skipping as she walked. Papa walked beside her. It was Papa’s day off, and they decided to go out and have fun.

    Papa held baby girl’s hand and gave her a gentle squeeze. Reminding her what was in her cunt. Ben Wa Balls. She stopped skipping hoping they wouldn’t fall out. She wasn’t wearing any panties and only had a skirt on.

    Baby girl felt the balls having her fun as she kept them in.

    It had been Papa’s request. She happily complied.

    They went from store to store, finally coming across a boutique store.

    Walking inside, Papa looked around. He came across a rubber fist.

    Picking it up, he winked over at baby girl who’s eyes lit up.

    She loved being fisted. Papa had something naughty in store for her.

    They walked home.

    Entering the apartment, Papa pulled out the rubber fist.

    “Strip.”

    “Yes Sir.” Baby girl said.

    Her clothes dropped immediately.

    “Take out the balls.”

    They dropped to the floor.

    Papa led baby girl into the bedroom where he restrained her.

    Her heart was beating fast. Her cunt was flushed and wet. Baby girl waited patiently for what was to come.

    Papa rubbed baby girl’s clit gently at first and felt her wet cunt with his fingers.

    “Baby girl is wet.”

    “Yes Papa. For you Papa.”

    Papa nodded his approval. “Good girl.”

    “Thank you Papa.”

    He ran a finger up and down baby girl’s body outlining her. Teasing her. Tingling her. She moaned.

    Papa took out the rubber fist and lubed it up. He stuck the protruding fingers into her cunt and gauged her reaction. She took it well.

    “Want more?”

    Baby girl nodded. “Yes, please.”

    Papa laid next to her and licked her tits. Kissing them gently. NIbbling on her perfect nipples. He continued to trace her outline and then slid the fist a little further in her cunt. She gasped. It felt so good.

    “We still good?”

    “Yes Papa.” Baby girl said.

    “Good.” Papa kissed her forehead and continued to caress her and nibble at her tits. He loved baby girl’s tits. They were perfect.

    Papa slid the fist further in.

    Baby girl gasped. “Yellow.”

    Papa backed the fist out. “You okay?”

    She nodded. “Yes Papa, now I am.”

    Papa hugged her. “Sorry about that, didn’t meant to…”

    “It okay Papa. I use signal.”
    Papa nodded. “Yes.”

    Taking the fist out of her cunt, Papa replaced it with his own fingers. “Better?”

    “Yes Papa. Much.” Baby girl said.

    Papa smiled. “Good.” He finger fucked her to orgasm. Over and over. With each one, baby girl squirmed and bucked her hips. Her face was flushed, she moaned with each orgasm.

    Papa continued to smile. Baby girl was enjoying herself. He was happy.

    He continued to finger fuck her.

    “What about Papa?” Baby girl asked.

    “Today is your day baby girl.” Papa said. “All the orgasms you want are yours.”

    “Thank you Papa.” Baby girl said.

    Papa smiled and kissed her deeply. “Welcome baby girl. Happy Birthday.”

