\section{Naughty Baby Girl Part 21}

     Papa and baby girl laid in bed. It was Saturday. They had the day off and were simply enjoying each others company.

     Baby girl was dressed in a nighty without panties. Papa wore boxers.

     Papa smiled at baby girl. She smiled back.

     “What are we gonna do today Papa?”

     Papa continued to smile. “We’re gonna fuck.”

     Baby girl’s eyes lit up. “Yay!” She loved when they fucked.

     Papa reached down and rubbed baby girl’s cunt. “Mine.”

     “Yes Papa.” Baby girl said. “Always yours.”

     Placing her hand on his cock, Papa gestured.

     Baby girl nodded as she put Papa’s cock in her mouth and rubbed his balls. Papa moaned as she did this. “Good girl.”

     “Mmmmhmmm.” Papa massaged baby girl’s neck and shoulders. He played with her tits. Baby girl ran her tits against Papa’s balls.

     It felt amazing.

     Papa’s hands felt down baby girl’s body down to her ass. He fingered her ass gently. Playing with it.

     Baby girl moaned. “Mmmmm.”

     Papa felt baby’s tongue tickle his balls and his taint. He loved when she played with his balls. She rubbed them and stroked him.

     Papa held onto baby girl’s shoulders as she continued to go down on him. He fucked her face thoroughly.

     As Papa came, baby girl took it all and drank him.

     Papa moaned.

     Baby girl kissed Papa and rode him. Her wet tight cunt wrapped around his cock. Papa thrust into her. In and out. In and out. In and out. Her tits were in his face. He grabbed them and licked, sucked, and played with them.

     Papa moaned.

     Baby girl moaned as she came.

     Papa kept thrusting as she came again, and a third time.

     Out of breath, baby girl smiled. “Thank you Papa.”

     Papa grinned. “We’re only starting.”


