\section{Naughty Baby Girl Part 22}

     “We’re only starting?” Baby girl asked.

     Papa nodded. “Remember your words?”

     Baby girl nodded.

     “Good.”

     Papa brought out a collar and placed it around baby girl’s neck. It was decorated in penguins and had a lead which was in Papa’s hand.

     Baby girl leaned back on the bed.

     Papa pulled on the lead. “No. You will kneel.”

     Baby girl did as instructed. “Yes Sir.”

     She felt her cunt getting wet again. Getting on the floor, she kneeled in front of Papa.

     Papa’s cock was hard again. He placed it in baby’s mouth. She sucked at it eagerly. Remembering when he came into it earlier. She wanted his cum in her mouth. On her body. Deep inside her. Baby girl was hungry.

     Papa fucked her face. Pulling on the collar as he did so. He listened to baby girl’s moans making sure to know if it was getting too much. She was doing good.

     He continued fucking her face. Using her. Her body was his to do with as he pleased. He loved that thought. Deep in her throat, Papa’s cock went. Baby continued to moan.

     Pulling out a butt plug, Papa handed it to baby girl. “Put this in.”

     “Yes Sir.” Baby girl said. She lived to serve. Loved to please.

     Baby girl also loved her butt plug. How it made her feel. She slid it in easy. It felt amazing.

     Papa continued to fuck her face.

     She continued to moan.

     Pulling on the collar, Papa took his cock out of baby girl’s mouth and instructed her to go on all fours.

     Baby did as instructed.

     Papa rubbed his cock against baby girl’s pussy. It clenched. She wanted his cock inside her.

     Papa spanked baby girl.

     She moaned.

     Papa spanked her again then fingered her pussy.

     Baby girl continued to moan.

     Taking the butt plug out of her ass, Papa stuck his hard cock deep inside her and fucked her.

     Baby girl held onto the side of the bed as Papa fucked her ass. She continued to moan. “Yes Papa.”

     Papa fucked her hard and rough. He spanked her as he fucked her.

     Pulling out a dildo, Papa shoved it in baby girl’s cunt. It slid in as he fucked her. Both holes filled. Papa continued to fuck her ass.

     Baby girl wanted to cum. But knew Papa had to give permission. She held on best she could.

     “Baby girl, you’re so good.”

     “Thank you Papa.”

     Papa came hard in her ass. Filling her ass with his seed. Taking the butt plug, Papa placed it back in baby girl’s ass.

     Baby wanted to cum. Oh how she wanted to cum.

     Papa spanked her again.

     She moaned.

     “Cum.”

     Baby came. Hard. The orgasm flowed through her body. Her ass stung. Her cunt trembled.

     Papa removed the butt plug as she relaxed.

     Taking the collar off, Papa grabbed a blanket and wrapped her up in it.

     He cuddled her.

     Rubbed her hair.

     Papa comforted her.

     “Shhh” he said. “Good girl.”

     Papa reached into a fridge and took out some ice cream.

     They shared the ice cream. One spoonful at a time.

     “How are you?”

    Baby girl smiled. “Good Papa.”

    Papa kissed her forhead.


