\section{Naughty Baby Girl Part 23, The Chair}

    Papa walked in the door. Setting his briefcase down and loosening his tie, he looked around. “Baby girl?”

    Baby girl was nowhere to be found.

    Papa walked through the house. “Baby girl?”

    Still nothing.

    Walking into the kitchen, that’s when he saw her. Covered in flour.

    Baby girl turned around just as Papa walked in.

    “Uh oh.”

    Papa nodded. “Uh oh indeed.”

    She toed through the flour.

    “What happened here?”

    Baby girl shrugged. “Nothing.”

    Papa put his hands on his hips. “Baby girl, what happened?”

    “Nothing Papa, promise.”

    Papa walked towards her. “Then what’s this?” He ran a finger along baby girl’s face taking a bit of flour with it.

    She shrugged. “Nothing!”

    Baby girl put both hands on Papa’s shirt leaving flour marks and ran off.

    Papa chased baby girl through the house. “Baby, get back here.” He said. Papa was losing patience. Baby was up to some kind of game, but he wasn’t sure what it was. Maybe just having one of those days.

    When he finally caught up to her, baby girl had slipped into the shower. “If I wash it off, Papa won’t know.”

    Papa opened the shower door. “There you are.”

    Baby girl looked at Papa. She smiled. “Hi Papa! I do nothing.”

    Papa gestured towards him. “Come here.”

    Baby girl shrugged. “Okay.” She turned off the water.

    “You’re naked, good.” Papa said. He placed a collar around baby girl’s neck. “Come with me please.”

    “Yes Sir.” Baby girl said.

    Taking her to the next room, a chair was seated in the middle of the room. There were handcuffs at the back, and leg cuffs at the feet. A hitachi was situated through the seat and plugged into the wall.

    “Have a seat.”

    “Yes Sir.” Baby girl said.

    She sat down. Papa handed her a towel. “Let’s dry you off first.” He rubbed the towel over sexy body. Getting all of the water droplets till she was dry.

    “Thank you Papa.”

    Papa nodded. He cuffed her to the chair. Legs first then her hands.

    Papa fingered her a bit, sucking on her tits. Baby girl was wet.

    Turning on the hitachi, Papa smiled. “Don’t cum.”

    The hitachi sent waves of pleasure up baby girl’s spine. “Yes Papa… oh oh…”

    “Don’t cum.”

    Baby girl squirmed. “Yes Papa.”

    Papa flicked a switch on the chair, a hole opened in the back of it where a butt plug eased into baby girl’s ass. “Don’t move.”

    Baby girl curled her toes. “Yes Papa.” “Oh Oh Oh.” She wanted to cum. Wanted to cum bad.

    Papa storked baby girl’s hair. “Words?”

    Baby girl nodded. “Green.”

    Papa nodded. “Good.” He made sure she was okay. At anytime she gave a yellow or a red he would stop.

    “Thank you Papa.”

    “Welcome baby girl.”

    The hitachi kept massaging baby girl’s clit. Her tits bounced up and down. The butt plug was firm in her ass. She wanted to cum. Hard.

