\section{Naughty Baby Girl Part 24}



    Baby girl moaned. The hitachi was doing its job rubbing against her clit. Her cunt was wet. Very wet. She moaned.

    Papa circled around the chair. In his hand was a flogger which he caressed baby girl’s tits with. Her nipples were hard. Rock hard.

    Reaching into his pocket, Papa took out a set of nipple clamps and put them on baby girl’s nipples. She let out a gasp.

    “Good girl.”

    “Green.”

    “Good.”

    Baby girl wanted to touch herself, but couldn’t due to the handcuffs.

    Papa continued to walk around the chair. His shoes echoed against the wooden floor. Each step made a defining mark.

    Baby girl’s breath quickened.

    Papa turned off the hitachi.

    Baby girl’s clit throbbed.

    Taking out a blindfold, Papa placed it over baby girl’s eyes. She couldn’t see.

    “Do you trust me?”

    Baby girl nodded.

    Papa slapped baby girl’s mouth. “Speak.”

    “Yes Papa.”

    “Words?”

    “Green.”

    “Good.” Papa uncuffed baby girl’s ankles and hands. He then recuffed baby girl’s hands. Taking her over his knee, he spanked her.

    Baby girl moaned.

    Papa spanked again. “Playing with flour.”

    “Yes.”

    Papa spanked again.

    Her moaning continued.

    Taking out some rope, Papa tied baby girl. Her tits had rope around them. The sensation dove into baby girl’s body. She moaned.

    “I have Papa’s cock?”

    Papa closed baby girl’s mouth. “Not yet.” He placed a ball gag in her mouth.

    “Too many sensations?”

    “No Sir.”

    “More?”

    She nodded.

    “Speak.” Papa said, slapping her face. Not hard, just a slight tap.

    “Yes Sir.”

    Papa pulled out a ball gag and placed it in baby’s mouth.

    “If you need to speak, shake your head left and right. Nod if you understand.”

    She nodded.

    Papa placed her back on the chair and turned on the hitachi again.

    Baby girl moaned.

    Papa smiled.

    Removing the rope, Papa stroked baby girl’s tits. He pulled out a pen.

    “Whore.”

    “Slut.”

    “Cum bucket.”

    He spoke as he wrote.

    Baby girl felt the pen against her tits. She loved how it tickled.

    Papa put the pen down and moved the hitachi to the side.

    Baby girl’s cunt was throbbing.

    She wanted to cum. Oh how she wanted to cum.

    “Don’t cum.” Papa said, as if reading her mind.

    She nodded a confirmation.

    Papa thrust a few fingers inside. Now he would manually stimulate her, and stimulate her he did. Baby girl squirmed.

    It was then Papa noticed tears running down baby girl’s cheecks. A look of concern went over his face.

    He removed the ball gag. “Words?”

    She breathed hard. “Green.”

    Papa hesitated. “Are you sure?”

    Baby girl froze.

    Papa took the blindfold off. “Baby?”

    He loosened the restraints. Removed the nipple clamps and the butt plug.

    Holding her in his arms, he held her. Rocked her.

    Baby girl held onto Papa tight.

    Papa grabbed a blanket and carried her to the bathroom. Setting her in a bath, he sat behind her and caressed her. Washed her. Rubbed where the rope marks were.

    Baby girl let go. She came.

    Papa held her. “I’m here baby girl. I’m here.”

    She relaxed and nuzzled into Papa’s arms. “I know Papa.”

    Papa kissed baby girl and continued to hold her.

    “I love you.”

    Baby girl nodded. “Love you too Papa.”

    Papa took care of baby girl. Smiled at her. Nuzzled her.  He kissed her neck and forehead.

    “Good baby girl.”

    “Thank you.”

    “You’re welcome.”

