\section{Naughty Baby Girl Part 25}

     Papa was working in his office. Baby girl walked in with a paddle.

     Handing Papa the paddle, baby girl nodded. 

     Setting the paddle down, Papa smiled. In a second okay baby? He rubbed her hand.

     Baby girl pouted. "Now!"

     She threw herself down on the floor.

     Papa looked down at her. He tilted his head. "If you don't stop that, There will be consequences."

     Baby girl looked at Papa. Standing up, she dropped her panties.

     Papa stood from his desk.

     Baby girl picked up the paddle and swatted Papa with it. Then ran off shedding more clothes as she did so.

     Papa felt his ass. It stung. He took the paddle and followed the trail of clothes.

     Baby girl was in the process of tossing things around the kitchen. Paper. Plates. Silverware.

     Papa stood at the door watching her.

     Baby girl didn't stop.

     Papa pointed down the hallway. "Time out chair young lady."

     Baby girl ran to the next room. "Nope!"

     She refused to listen. Papa followed her. Pillows were being tossed around the living room.

     Papa pulled out a set of handcuffs. Walking up behind baby girl, he cuffed her.

     "Awww"

     Papa walked her down the hallway. Baby girl wanted to play. She would play.

     The room with the chair was lightly lit. Papa sat baby girl down on the chair. She snickered at him. "You won't do it."

     Papa nodded. "You've misbehaved young lady. I will."

     He locked her to the chair. Her feet couldn't move. Her legs wide open. Baby girls cunt was wet as she was trained to be. Her clit throbbed. Wanting attention. Needing attention.

     Her tits were perky. Baby girls nipples needed to be sucked. Pulled on. Licked. Nibbled on.

     Papa put nipple clamps on baby girls tits. She moaned.

     A blindfold later, Papa rubbed baby girls legs. Felt her cunt. Tasted her sweetness. With each lick, baby girl moaned.

     Papa took his clothes off and put his cock in baby girls mouth. She sucked slowly. Papa moved in and out of her mouth. Fucking her face. He slapped her face. He fucked her harder.

     Baby girl moaned. 

     "My good slut." Papa said.

     He grabbed the back of her neck. And fucked her harder. His cock in her throat. Her tits bouncing.

     Papa pulled out of her mouth and came on her tits. He slapped her face again.

     Baby girl frowned. "You didn't come in my mouth."

     Papa shook his head. "Nope. You've been bad."

     Unlocking her, Papa stood her up. Placing a hand around her neck, carefully squeezing the sides he choked her.

     Baby girl moaned. "Yes."

     Papa sat down and faced baby girl away from him. With his hard cock, he fucked her from behind. Placing a dildo in her ass, Papa continued to fuck her. Each thrust shifted the dildo.

     Baby girl moaned and gasped.

     "My cum slut. My cum bucket." Papa said.

     Baby girl moaned.

     "My whore." Papa said. "I will make you cum when I want you to."

     Baby girl nodded. "Yes Papa."

     Papa continued to fuck her. Holding her hips, her tits. Her body was his to use. She was his.

     Sliding out of her, Papa out baby girl on her knees.

     "Suck."

     "Yes Sir." Baby girl said. She took Papas cock in her mouth. Tasting herself and him. She moaned. Papa pulled on her hair as she took his cock in and sucked him.

     As Papa was about to cum, he pulled out and thrust his cock in baby girls cunt. He came hard. "My breeder. Take it all."

     "Yes Sir." Baby girl said. "All yours."

     Papa slid out again. He kissed baby girl. "Good slut."

     Baby girl looked at Papa. "May I cum?"

     Papa shook his head. "No. Naughty baby girls don't get to cum."

     She frowned. "Yes Papa."

     Papa helped baby girl up. He kissed her. Rubbing his hands through her hair, he kissed her more. "Come on" Papa said. "Let's get a shower."

