\section{Naughty Baby Girl Part 26}

    Papa chased baby girl down the hallway. He had whipped cream on his shirt. Taking his shirt off, Papa tossed it in the laundry room on the way.

    Baby girl had the whipped cream can in her hand. She giggled. “Papa silly. He covered in cream.”

    Papa grunted. “Baby girl will be covered in Papa’s cream pretty soon.”

    Baby girl stopped. She hoped he wasn’t fibbing to her. She wanted Papa’s cream.

    Getting on her hands and knees, baby girl crawled towards Papa.

    Papa stopped at the end of the hallway and waited for her to crawl to him.

    “Papa.” Baby girl said as she came near.

    Papa had his hands on his hips.

    Placing a collar on baby girl's neck, Papa smiled. “Come with me.”

    “Yes Papa.”

    Taking her down the hallway, Papa sat baby girl on the bed. He held her chin and she looked up at him.

    Papa slapped baby girl. “That’s for the whipped cream.”

    Baby girl nodded. “Yes Papa.” Saliva came from her mouth. She grinned.

    Papa reached down and fingered her cunt. Baby girl was wet. She was expecting punishment.

    He chuckled. She was a piece of work.

    Papa shook his head. “No…”

    Baby girl laid back on the bed and spread her legs.

    Papa pulled on the chain attached to the collar. “No, you will sit.”

    Baby sat up. “Yes Sir.”

    Papa shoved his cock in baby girl’s mouth. She sucked on it. He fingered her with his free hand. Her clit and cunt were his.

    Baby girl moaned. She wanted to lick his fingers dry, taste herself on his fingers.

    Papa laid baby girl down and spread her legs.

    His hard cock entered her waiting cunt. With each thrust, she could feel herself on the verge of cummning.

    Mustn't cum. Baby girl thought. Mustn't cum.

    Papa continued fucking her.

    Turning her around, he mounted her from behind. Spanking her ass as he fucked her.

    Baby girl moaned loudly.

    Papa smiled. She was taking it well.

    He continued to fuck her.

    “Come.”

    Papa said.

    Baby girl came. Her cunt throbbed around Papa’s cock as she came. Letting out tears, she landed face down on a pillow.

    Papa grabbed her hips and continued to fuck her.

    Baby girl moaned.

    Papa came. Filling his cum bucket with his seed, he came hard.

    Baby girl moaned as Papa came. She wanted to be filled. Needed to be filled.

    Papa stood from the bed and walked around to where baby girl was laying. She smiled at him.

    “Thank you Papa.” She said.

    Papa smiled back. “Welcome angel.” He kissed herforehead. Removing the collar, Papa checked baby girl’s neck. No marks. She was okay. He looked into her eyes. They sparkled back. Not too rough of a session.

    He carried her into the next room and sat on the couch with her in his lap. Papa sang baby girl a song as she fell asleep.

