\section{Naughty Baby Girl Part 27}

    Baby girl and Papa walked out of the movie theater across the parking lot to a restaurant.

    Papa had chosen the restaurant weeks in advance in preparation for their date.

    The waitress seated them.

    “I like it here, Papa.” Baby girl said.

    Papa nodded. “Yes baby, so do I.”

    They looked at the menu and chose what they wanted to eat. The menu had many choices.

    Baby girl looked to Papa and smiled. “I have something for you.” She said.

    Papa looked up from his water glass. “Hmmm?” He asked.

    Sliding a napkin over, baby girl gestured to it. “Open it.”

    Papa looked at the napkin with curiosity. Opening it, he found a pair of panites in them. Light pink panites. He looked at baby girl. She nodded.

    Papa smelled and then pocketed the panties. They smelled of baby’s fresh cunt. He smiled.

    Dinner went by quickly. Soon they were driving home. Papa fingered baby girl’s cunt on the drive home. She was wet. Baby girl squirmed and squirmed. “Papa’s fisky.”

    Papa nodded. “Yes baby girl I am.” Licking his fingers off, Papa placed a hand on baby girl’s tits and gave them a good squeeze. He rolled her nipples in his fingers. She moaned. Papa continued to squeeze baby girl’s nipples.

    Baby girl breathed hard. She licked her lips. She wanted Papa bad. She wanted Papa now.

    Pulling the car over, baby girl jumped in Papa’s lap and pulled his cock out. “Fuck me Papa.”

    Papa grabbed baby girl’s waist. He was horny. He couldn’t wait to get home. Entering her, his hard cock throbbed and pulsed.

    Baby girl rode Papa’s cock up and down. “Oh Papa.” She moaned as she milked Papa’s cock.

    Papa thrust into her. He licked and nibbled on baby girl’s tits in his face.

    Baby girl kept riding Papa not wanting to stop.

    Papa kept thrusting.

    Baby girl came. Her hand on Papa’s shoulder as she did so.

    Papa licked his lips and kissed baby girl. “Good girl.” He said.

    Baby nodded. “Thank you Papa.”

    Papa continued to thrust into her. Squeezing her ass as he did so. Fingering her ass as well.

    Papa came. Filling her tight cunt with his seed. Papa fucked her. “Take it all.”

    “Yes Papa.” Baby girl said. “Gladly.”

    Papa slid out of her. Baby sat back down and looked at Papa.

    “Ready for dessert?” Papa asked?

    Baby girl moaned. “Always.”

