\section{Thu, Nov 1, 2018}

I didn't lose my faith. I lost belief in a corporate entity. I still have a belief in
God and in His Son Jesus Christ. The Holy Ghost is there to prompt things which are
true and false and to testify of the Father and the Son. No problem there at all.

Here's the problem.

The Church of Jesus Christ of Latter-day Saints. That's the problem. They claim sole
authority on everything religious. That is where I draw the line. To indicate that
every other church is false and wrong, to indicate that no matter what if you don't
become Mormon, you don't get to be with God? You can't tell me that's not what they
teach. That is exactly what they teach. How else do people get to the Celestial
Kingdom? The exact wording is:

\begin{displayquote}
Your endowment is, to receive all those ordinances in the House of the
Lord, which are necessary for you, after you have departed this life, to enable you 
to walk back to the presence of the Father, passing the angels who stand as 
sentinels, being enabled to give them the key words, the signs and tokens, 
pertaining to the Holy Priesthood, and gain your eternal exaltation in spite of 
earth and hell.\footnote{Journal of Discourses 2:31}
\end{displayquote}

Exaltation is to be with God. Mormons believe that being with God means to be in the
Celstial Kingdom, the very top level. To be under a Celestial covenant of Eternal
Marriage.\footnote{D\&C 132} The other kingdoms will not have the privlidge of being
with God and are considered hell to that person. Yet when we get to the other side,
and judgement day is upon us. We will go to that kingdom where we belong, that
kingdom which we will feel comfortable in the most. If that is the Telestial Kingdom?
So be it. If it's the Terrestial Kingdom? Yep, that works too. I imagine a very few
portion will be in Outer Darkness, well aside from Satan and those angels which
followed him before the world was. But those who gained a body, those people would
have to deny the Holy Ghost.
