\section{Mon, Nov 5, 2018}

A curious thought crossed my mind the other day. In Alma chapter 40, we read:

\begin{displayquote}
And then shall it come to pass, that the spirits of those who are righteous are 
received into a state of happiness, which is called paradise, a state of rest, a 
state of peace, where they shall rest from all their troubles and from all care, 
and sorrow.

And then shall it come to pass, that the spirits of the wicked, yea, who are evil—for 
behold, they have no part nor portion of the Spirit of the Lord; for behold, they 
chose evil works rather than good; therefore the spirit of the devil did enter into 
them, and take possession of their house—and these shall be cast out into outer 
darkness; there shall be weeping, and wailing, and gnashing of teeth, and this 
because of their own iniquity, being led captive by the will of the devil.

Now this is the state of the souls of the wicked, yea, in darkness, and a state of 
awful, fearful looking for the fiery indignation of the wrath of God upon them; thus 
they remain in this state, as well as the righteous in paradise, until the time of 
their resurrection.\footnote{Alma 40:12-14}
\end{displayquote}

It talks about spirits after the death of the body. The spirits of the good people, 
go to a state of paradise. Other spirits go to outer darkness. These spirits wait 
until the resurrection of the spirit and the body.

Could this be a misspoken concept by the prophet? For we're taught that spirits go 
to either paradise or prison. Outer Darkness is meant for those who deny the Holy 
Ghost and are damned after the resurrection, or reuniting of the body and the spirit.

People make mistakes, I get that. But if they are talking about doctrine of the
church, that is quite a mistake to make. If the words are taken as is, it describes
that whicked spriits go to Outer Darkness before resurrection. Where Outer Darkness
is meant for a final judgment of those who deny the Holy Ghost. That is to say, one
has to see the sun shining and refuse to acknowledge it.

In 1 Peter, we are told of Spirit Prison:

\begin{displayquote}
For Christ also hath once suffered for sins, the just for the unjust, that he might 
bring us to God, being put to death in the flesh, but quickened by the Spirit:

By which also he went and preached unto the spirits in prison;

Which sometime were disobedient, when once the longsuffering of God waited in the 
days of Noah, while the ark was a preparing, wherein few, that is, eight souls were 
saved by water.\footnote{1 Peter 3:18-20}
\end{displayquote}

I'm still looking into this. There are scriptures that speak of what happens to
people after they are resurrected and after the final judgement, but not much about
the spirits in prison. I mean, in D\&C 138 we're taught that people were in Spirit
Prison were taught the gosepl, at which point they are released from prison.

We're taught that those who followed Lucifer will be thrust down to Outer Darkness
after the judgement.

If spirit prison is indeed Outer Darkness, then according to the thougths above, they
can learn the truth and come out from it? Something doesn't quite add up. I can see
Spirit Prison being a different place than Outer Darkness. Spirit Prison, to me,
would be a holding place for those waiting to be resurrected. They can be taught.
Those in Outer Darkness is after rhe resurrection, where they are banished.

Now that banishment isn't a forever banishment and torment isn't endless. As we're
told that Christ's punishment is eternal, as in He is eternal. So it would be an
eternal one, for that is how He is and how the law is. It is eternal. It doesn't mean
that people won't be released from such torment after they have suffered and repented
of their sins.
