\section{Mon, Nov 19, 2018}

Ah another week is upon us. What's there to be said about it? I'm not
sure, well is anyone ever really sure about what's going on? Some 
might argue it's a new week, so what. While others might have you wonder
what there is to be said about it all. Who's to say exactly anything?

There was a time in my life where I figured everything would be simple, just
have to keep my nose clean and follow the brethren. Wouldn't have to worry
about anything if I did those simple things. Wouldn't have to worry or
think about what was right or wrong in my mind, wouldn't have to do any
kind of thinking.

Well, that kind of process can only take you so far. Eventually you have
to decide for yourself if it's right or wrong in your own mind. You have
to study it out and see what possibilities are out there. I'm not saying
I've found something exactly...I'm not certain what it is I have found.
It's a journey to be sure.

Jesus didn't say that people had to do x, y, and z to get into heaven. He simply told
them to follow Him. Sometimes it was to give all they had, but they were to follow
Him. Trusting in Him, the one who would save them from death. Naturally there are two
different deaths in this life, the mortal death and the spiritual death. We are
introduced to these deaths by the fall of Adam.

Yet it is through Jesus and Jesus only that we are able to be saved and come back to
the presence of the father. I wonder if people forget that at times, the concept of
grace. It is by grace we are saved.\footnote{Ephesians 2:8-9}

That scripture talks about it being a gift. Who are we to reject a gift by saying
that we, and we alone, made it to heaven? That would be blasphemy.
