\section{Sun, Jul 22, 2018}

So many confusing aspects of life come about because people don't grasp their own
history. When people do try and attempt to understand that history, they are called
unto repentence because it's showing negative light upon the church. A church which
doesn't want its history to be made and known public doesn't have a leg to stand on.

\st{So many confusing...} There are really things out there which don't make sense.
It would be nice if they actually did make sense for once. But they do not and so we
are left with our own thoughts and processes upon which we are meant to try and
understand that which we cannot. Some would tell you to simply wait until things get
better, until a time when we are able to understand all of it, we are meant to have
faith and act accordingly.

What if I don't want to waste my time?

It never ceases to amaze me, when something bad happens in a person's life they think
it's a sign from God. That there's some reason they're having this difficulty and
it's a blessing that they are going through such an experience.

That's not always the case.

Sometimes bad things just ... happen. Bad things happen to good people, they happen
to bad people. Bad things really just happen. There's no reason to expect it's a sign
from God or that God is putting you through a trial for a specific reason. I wish
people would accept and understand that better. But they don't.

Why would a church hide a lot of its history? It doesn't make much sense to me. I
mean, are we not taught to seek out of the best books and learn as much as we 
can?\footnote{D\&C 88:118} If that's the case, then the church should be producing 
such books on their own history. Leaving nothing out.

The truth is the truth and the truth must be known. It cannot be
hidden simply because of some dark places. Let the people figure it out for
themselves if something is true or false. Do not allow it to remain hidden behind
closed doors.

There comes a time when the truth comes along and it's made known. People need to
make a choice of their own on what should be done with that truth. If it so be they
decide to leave whatever they have behind and go forward without whatever it was they
had, then they can do so. It must be allowed without someone else coming along
telling them what they can and cannot do with their own life. It is their life, it is
their decision on what course of action to take. No one can do that for you. It's
something you have to be able to take a step back and decide for yourself.

The question which comes up after one has prayed about it...once they get a feeling
to simply leave an organized religion. How does one go about doing this? Another
problem to worry about is how would family members react to such a thing? I know how
my own family would react to my leaving a religion I grew up in, but I cannot ignore
the feelings I have had regarding it. I cannot step down, I must gor forward and do
something about these feelings.

Prayers tend to work both ways. You can pray for something to be true, you can spend
all of your time and energy hoping that something will be true. You can pray to see
if something is indeed not true as well. God is not a repsector of persons, He can
and will answer the prayers which you give to Him to answer.

Feeling peace, it's a good feeling. A feeling which I can't deny exists. Finally I am
able to rest. Finally I can not be anxious about church. A church meeting caused me
anxiety of all things. What's that all about? I don't get it. There's no reason for
it to cause anxiety, but there it did its thing. Darn anxiety always getting in the
way. But I don't have to deal with that anymore. One less thing to worry about as far
as anxiety is conerned. I'm grateful for that. I'm grateful for the feeling of peace,
I don't know how long it will last or stay, but I'm grateful for it. Feels good.