\section{Wed, Jul 25, 2018}

\centerline{But what if you're wrong?}

That's a common question to be asked to religious folks isn't it? So many damn
confusing things in life and people still don't grasp the question, what if they're
wrong. What is there to be wrong about? Plenty. The nature of God, who He is, how
things came to be in this life etc. So many possible outcomes to the answer as well.
The most devout will say they aren't wrong, they are in the right no matter what.

Some will tell you, well if I'm wrong then I'll be okay still. What hurts to give
that extra effort? What could hurt if they are wrong? They're still living up to what
they believe is right, so it's good right?

Not all those who profess to know Christ will enter thte kingdom of heaven, it's
stated in the bible that's the case.

\begin{displayquote}
Not every one that saith unto me, Lord, Lord, shall enter into the kingdom of heaven;
but he that doeth the will of my Father which is in heaven.\footnote{Matthew 7:21}
\end{displayquote}

It's right there, black and white.

Another thing to consider, why worry about another person's salvation if you do not
know the status of your own salvation? Should one not be more concerned with their
own outcome before trying to fix another individual? Are we not told to remove the
beam out of our own eye before \st{criticizing someone else} casting the mote out of 
our brother's eye?\footnote{Matthew 7:5}

I dare think some people forget that part of the gospels, they're so caught up in
thinking everyone else is false that they cannot see the beam in their own eye to
even begin to see clearly.