\section{Mon, Aug 20, 2018}\footnote{Day 1}

Oh what a day, today is a day right? It's a brand new day that we can simply attempt
to live at. So allow it to be. If it cannot be what it is, then we are doomed to
repeat that which is impossible...or something like that. Who's to say exactly what
will happen in a life that wishes to destroy us at every moment of every day? My
thoughts exactly.

I'm quite tired today. Went to bed at an awful time, but well that's on me. Tonight I
will sleep good I bet. Just have to wake up at good times and go to bed at good
times. It's a timing issue I believe. There's nothing wrong there at all. Just have
to do it. Perhaps that's the main problem with it all? I do not know. Whatever the
case, \st{here we are doing what we can,} here I am doing what I can do to be better.

Yeah, that sounds better doesn't it. Focus it all on me, as it should be. I mean it's
my life isn't it? So shouldn't I have to deal with it all? Something like that. One
would think this life would get easier, but it doesn't. There's no reason for it to
get easier I don't believe. Life comes and goes and just gets more difficult as we
process it all.

There is a time and a season for everything. Sometimes you need to slow down and
figure out when that time and season is for you. Going too fast at life has the
ablity to mess with your senses and you don't really know what's going on at that
point.\footnote{Ecclesiastes 3}

I have within me a great deal of anxiety and stress, it has been this way for a long
time now. Probably since I was born. People don't understand it. They don't
understand me. It's just not an easy thing to navigate at times. I hate it. I hate
what it does to me most days. That's where everything just comes crashing down on me.
So I have to try even harder for everything to come around and make sense. I have to
be able to understand what is going on in my life and I need to actually be able to
take hold of it and try.