\section{Wed, Jun 6, 2018}

Oh hello brand new day! How are you doing today? There isn't much of a thing to
think about. How nice would that be? Yes, it would be very nice. But it's not.
Life isn't nice that way.

Things should be going good. There is a lot of things that don't go well in
life, life itself shouldn't be one of them. At least to my thinking that's how
none of it should happen. Life needs to be better. It needs to find a way to
become easier? Maybe that's not the right word for it. I don't know what word to
use actually. Easier life...doesn't always make sense.\footnote{Whoever said
this life was easy sure didn't understand what they were getting into.} So we
live a life that's full of confusion and complaint...and whatever else there is
to deal with. This life doesn't always make sense. This life will never make
sense. We have to roll with the punches as it were.\footnote{``Roll with the
punches"??? Where the hell did that phrase even come from? It's not a phrase
that makes much sense! Seriously, who ``rolls" with anything these days? Either
you get with the program or you get smacked down. Isn't it that simple?}

Let's not dwell on the past. The past can only conjure up problems and issues.
To focus soely on the past is to focus on things which will only bring
heartache. A heartache so deep, you don't have a clue where you will end up. It
hurts to be that way. Hurts to not understand anything that's going on. Life
isn't full of wisdom. Life is full of hurt. There is no happiness around this
life, either you walk a certain path, one of your choosing, or you fail.

Failing doesn't always mean certain death. No, not at all. To fail is but a part
of human existence. Everyone fails in their life from time to time. There's
nothing wrong with that. Just remember that when you do fail, to stand back up
and get on with your life again. To fail is not a final resting place, it is but
a temporary marker as it were. You are able to stand from it. There is no shame
in failing.