\section{Fri, Jun 29, 2018}

There are some days which come and go as they wish. Nothing is real anymore,
there are so many obstacles in this life, are we alone in our thinking and
thought process as it were?

Whose to say how any of this life or world will form and shape itself as we grow
beyond our own abilities and programming. Do we not have such an internal
programming? Are we not concerned with everything which comes down our own path?
Out of all the many thoughts and ideas out there, one would guess it's more than
a simple aspect of life which we grasp hold of.

Perhaps this is complete nonsense. Maybe it is something else. Either way we
must not be able to think we cannot do something. It isall within our power and
our grasp. But, how far is our reach exactly?

What sphere of influence do we have to deal with? How exactly does all of that
work, how does that happen?

Perhaps there are days which don't matter and won't make a bit of difference in
the long run. We are all but weird creatures swamped within our own mortal coil
or shell. We cannot be allowed to overthink or underthink the possibilities
which will eventually come along our path. Is it in our own destruction to find
that which we cannot find on our own? How does a person even begin to comprehend
such a thought process? Is it not the right timne to wonder and grasp th at
which we cannot hold onto in our lives? Maybe I am at a loss as to the thoughts
within my own mind. An odd cage as it were. Something of naught upon which
everything is founded.\footnote{Feels like I'm quoting movie quotes or something.}

However to live our lives in harmony and to be true to ourselves we must want to
have such a truth made upon us. We have got to be able to find whatever truth
there is to be had and seek after it. It doesn't matter how many people are
following a specific truth, even if it is a small number, that truth's validity
doesn't diminish. It is still truth. To seek after truth is a good thing, a
godly t hing. Truth is an amazing thing to behold.

Wherever truth may be found, if it is good, we must seek after it. Truth and
fact do not always agree with each other. There is truth and then there is
righteous truth. Know the difference.

So, what of it? Who makes the final decision when it comes down to the
possibility nothing matters in this life?

Who is to say exactly what will happen to my family? Not everything is so cut
and dry. Everything comes at a price. Nothing is free as far as anything is
concerned. Are we not simply sheep huddled together for warmth, hoping our
master will come back someday? If so, where does that leave us?

To feel happy. To be happy, in this life we are to try and acknowledge we have a
say in how this life turns out. It is not destiny, it is not some kind of pre
determined thought process. Nothing of that kind of thinking exists.

If we are wrong, then we are wrong.

There comes a time in a person's thought process which we must strive to be
greater than what we currently are. There is nothing wrong with this. Everything
will continue to break down and give way. Why bother with any of it? Whose to
say people won't be together in the life hereafter? Whose to understand and
grasp fully how this life will end? No one has a full grasp of what is going on.
Not even those in higher up places of management.

Long gone are the days where someone said ``Thus Saith The Lord" for we are now
told they, some, were speaking as men and their words are not to be taken as
doctrine, even though they temselves claimed it to be doctrine.

There are so many different things to consider in this life. Doctrine shouldn't
be confusing at all. Why the need to make things so difficult for this life as
it were? There doesn't need to be anything so stupid or selfish from any of it.

This doesn't quite make sense. Are we here for the right reasons or are we
simply here to be puppets, a lab experiment for some God who enjoys watching His
children suffer and wander in unbelief. Hoping they will find and follow Him.