\section{Fri, Jun 15, 2018}

Stress comes and goes. It seems to come more often than it goes. Because why
not? Is there a reason it's here one day not the next? I doubt it. There are so
many thoughts out there in the world. So many problems and issues that just
don't line up with the logical thinking of anything. Logic.\footnote{Logic:
Reasoning conducted or assessed according to strict principles of validity.} 
Whoever thinks logic is an awesome idea? Shoot, I'd like to shake their hand. 
Unfortunately, we are not logical beings. We have emotions and do not embrace 
logic.

I wonder at times if we could ever fully embrace logic? Is it a thing? Can there
be a thing in life were we don't allow emotions to get in the way of any of it?
I doubt it. I think emotions are there for a purpose. Not always a good purpose,
but a purpose for sure.

Then again, logic isn't always it's cracked up to be. With simple slight of
hand, anyone can be tricked into believing 2+2 = 5.

\lstinputlisting[language=Java]{2018/WrongMath.java}

In case you don't quite grasp what the program is doing. It is indeed
calcualting 2+2 but sending that answer to an array to get the answer of 5. Java
is zero based, that is it doesn't start counting at 1. The value for 2+2 which
is 4, but the value which is returned from the array is 5. Make sense? Clear as
mud? Good!

Another part of this life which becomes tiresome is just being tired all of the
time. There's no reason we should be tired. But here we are, tired as all get
out. Talk about fun! No, not really. It's not fun to be constantly tired no
matter what you end up doing. Tired is annoying. Tired is dumb. tired is stupid.
But here we are, some people are tied and there's nothing they can do about it.
Others don't have the slightest feeling of being tired. It's an odd universe in
which we live.

So, where do we go from here exactly? Is there a process, a place we can end up
without going crazy? I doubt it. I highly don't think or believe there is
anything we can do in this life that will make us not go crazy. But that is only
my belief. This life is full of nonsense. Full of annoying thoughts and
processes which cause us to be destroyed long before anything else occurs. We
all will die. There is nothing wrong with that thought. It is inevitable.

\lstinputlisting[language=SQL]{2018/clue.sql}

It's a simple thought process right? We want all of the users which actually
have a clue as to what is going on in life. Those who don't? We don't really
care about them and they can be tossed aside from being processed. I hope that
makes sense to some degree. I know there are times when nothing in this life
makes perfect sense. That's okay though. Not everything is meant to make sense.
It is but a life in which we live. A tangled web we weave. Someone said that
right? I'm not just making up quotes? I should find out who said that.

Ah, the actual quote is:

\begin{displayquote}
Oh! What A Tangled Web We Weave 

When First We Practice To Deceive\footnote{Marmion, Sir Walter Scott}
\end{displayquote}

I am not one to decieve people...but life is still an tangled up mess of a web
which we do not fully recover from.

It is but a life which we do not understand or grasp everything that happens to
us. We live it as best we can. There is no reason for us not to attempt to live
this life to the best of our ability. Yet, here we are trying to do our best and
here we still are falling and failing all over the place as we attempt it.