\section{Tue, Jun 26, 2018}

Another day has come to our fair city... or world... or whatever you wish to
call it. Yeah let's just call it whatever the heck we want to call it. Why not?
There's not much going on in the world that can be depended upon these days...is
there? I'm not sure. Perhaps life would come around as it wanted to and we would
all be better because of it. Maybe not. Who's to say exactly what will happen in
this life? No one can know for sure.

\st{
There are times in this life where I just feel like screaming and/or ripping my
hair out! Yeah we usually don't talk about such things. It would be rather
annoying to constantly remind ourselves that we don't enjoy the simple things in
life. That this life is but a terrible dream which we want to wake up from. A
nightmare as it were. Nothing in this life will be wonderful ever. That's not
how any of it works. There are times where life will get in your way, it will
try and make you go down to whatever level it wants you to. There's no way
around it. There's no way through it. Life will eventually come for you... or
the other guy will get you. Either way, someone will get you. That's what this
life is all about. Trying to get the upperhand on someone else? Shame on you!
Shame on me! Shame on the whole world! There doesn't need to be a reason for any
of the contention in this life to be what it is. It is life. It can be wonderful
if we let it. It needs to be wonderful, why can't people see this?

I'll tell you why. They don't want to see it. That's the problem with this life.
They don't want to see all that is wrong with life. They don't want to actually
see what is going on and happening. They don't want to have an understanding or
grasp that which they cannot grasp. They want to remain in a blissful state. A
happy state. A state where nothing can go wrong. Life doesn't work that way
unfortunately. Life is miserable. Life isn't wonderful. Life is crazy at times.
It is terrible!

But who am I to say exactly what this life is or what it will mean to anyone. I
am but a person who lives day to day in the hopes that something good will come
from any of it. All of it. Hopeful? Perhaps. Stupid? Sure why not. Let's call it
that. There needs to be a way for this life to come about better than it ever
was before. Life cannot be taken for granted. It is but a most terrible thought
process upon which we stand. That's right, this life is a terrible thought
process.

Think about that for a moment. How is it a thought process you ask? Well, we are
not currently here. We wish we were here...but we are not. We can't possibly be
here. There's no reason for us to actually realize or think for a moment that we
exist beyond that which we cann't be.

Now that might not make any sense. That could be a most terrible thought process
to be handled upon. We cannot believe that which we cannot focus on. We cannot
understand that which we do not wish to understand.

A person an only declare ignorance for so long until they reach a point in this
life where they are not taken seriously anymore. People have short temper spans
these days. They have a fuse. When that fuse gets lit, they go off immediately.
That's just how the world works.
}

If we knew what was actually going to happen in this life, I doubt we would be
standing around worrying about the things we worry about.\footnote{
Worry is but a construct of the mind. It can be a chemical influence on the
brain much like anxiety. We always tend to worry about that which we have no
control over. Why should we have control over a thing? We shouldn't. Control is
never handeled properly. Why have control over something if you cannot properly
deligate it to the needed places. No one can tell you they will have a complete
understanding of what's going on. There needs to be something which can actually
take control and give order to chaos. Chaos is quite a motivator at times.
}

Well, some might continue to worry. That's human nature isn't it? Yeah, something 
like that. To worry about something that doesn't matter isn't logical. But the 
human race was never logical. I doubt there has even been a 100\% logical 
thinker in this world. If there was? I wouldn't mind meeting them and learning 
from them.

Truth is another interesting concept.\footnote{"When you eliminate the impossible, 
whatever remains, however improbable, must be the truth." Star Trek VI} Where
can we find truth in a world that constantly spews forth hate and lies? Are
there any reasons to believe in such lies? Lies come and go, there are no
reasons to not believe in such things, yet here we are living and thinking about
everything that could go wrong in a lifetime. Here we sit. Hoping someday for
everything to make sense, for everything to come to an end and we will be
sitting there thinking how well we did. Well, I don't think that will ever
happen. This life will come about to an end and we might be sitting there doing
exactly what we are doing now. Waiting for something better to come along.