\section{Mon, Aug 6, 2018}

There seems to be something in the air as of late. I'm not certain what it is or how
it got here. All I know is it's here. There should be something exciting to this
life, but there isn't. It's becoming rather bland. Perhaps I'm just getting
comfortable to it all? I'm not sure. There should be an explaination for it all, but
there isn't. There hardly ever is anymore. Any kind of explaination would be of
benefit, and yet here we are. Sitting, thinking, wondering about things that probably
shouldn't be wondered about.

Have you ever waited for baloons to die? It can be an annoying thought process, and
annoying thing to watch and something obviously annoying to just have happen. They
were full of life once, now they just hang around waiting to have nothing within
them. It's a lot like life if you think about it. People come about and are full of
all this energy, then they evenaully fizzle and fade away without anything else to
sustain them. No matter how into something they were at some point in life, it all
fades away.

I suppose if life didn't ever fizzle, we wouldn't have a problem. There wouldn't be
some kind of issue as it were.\footnote{I guess it all comes down to hopeful
thinking, that's really all it is.}

There is a phrase, which seems to have become a motto as it were. Which is sad, the
phrase:

\begin{displayquote}
My shoes are too tight. But it doesn't matter, because I have forgotten how to 
dance.\footnote{Londo, ``War Prayer", Babylon 5}
\end{displayquote}

The analysis is simple, a person puts constraints on themselves, the shoes, during a
lifetime, and they cannot enjoy life anymore, thus forgetting how to dance. \st{To 
live a life and then to realize it was all for nothing is not an easy thing to
process at times.} There is in this life, a time for everything.\footnote{
Ecclesiastes 3:1-8} Each moment has a purpose, each moment has a time upon which it 
is able to breathe and explore this life which is around us.

If we didn't have the ability to search out and explore such a life, where would we
end up exactly? To be constricted in ones own beliefs, cannot be a safe place to end
up, can it? Everyone needs a safe place in which they are able to be calm. The need
to be able to be safe and have a place to relax is what is needed most.

Memory recollection can be a tricky topic at times. Some people can have the ability
to remember things in perfect detail, while others have issues recalling that which
should be memerable to them. I wonder if it is by design of the human brain that this
is the cause. Is it possible we are not meant to recall things clearly like it
happened yesterday? At which point in our lives does our memory completely falter and
we cannot have the ability to figure out the truth from it all?

Do you ever have a memory come up and you can't shake it? It's one of those things
where you just don't know where it's coming from. It lingers for a bit, not willing
to leave and you just deal with it.