\section{Fri, Sep 14, 2018}

Friday has come upon us. This is amazing. I love a good Friday actually. There's not
reason not to enjoy a Friday. It's just the last hurrah before the weekend comes
along. Three day weekend here for me due to personal issues and problems. That's okay
though.

Ever sit back and think and wonder to yourself, what on Earth am I doing here? In the
circumstances I was placed into? The people I live with. All of those things which
come and go into the thoughts of people? Yeah something like that. It comes and goes
and here we all are, just trying to live life to the best of our ability I suppose. I
mean, come on though. There has got to be someting better. Something out there which
doesn't seem to matter about anything but happiness that we are to be experiencing.

But then you read the newspaper and learn about all of the evil things out there in
the world. You just have to wonder. What the heck is going on in the minds of some of
these people? They can't be for real, can they? I'm just not sure.

Who is to say exactly how this life is meant to unfold? I do not think there is any
kind of reason for any of it. We are here. We go through this life. We die. Is that
not enough of an explaination?

If there is a being out there who knows all things and how everything will unfold. If
there is a being who has unconditional love, except for when there is conditions
based on how you follow Him. One would think this life has no point to it.

According to religion, we were living with God before we came to an earth and forgot
everything. Adam and Eve introduced sin into the world by eating of the apple. Thus
their eyes were opened and they knew good from evil.

We do not have a rememberence of things past, we have to learn them gain line upon
line and precept upon precept. There is no other way upon which we are able to
remember those things which have been forgotten, or put on hold, due to the veil
being placed over our minds.

A person must prove themselves in this earth life to see if they will be worthy to
return to God and live with Him again after all is said and done. At times it doesn't
seem or feel fair, if God knows all we cannot have any kind of chance to overcome any
and all of the sins that happen. Yet we are expected to turn away from sin, even
though Jesus covered those sins that are unique to each of us when He suffered in the
garden and on the cross.

It is, at times, confusing. We are left to wonder how exactly any of this works and
are left to have faith. Without faith, we cannot understand or grasp any of which is
to happen when this earth life is over. We do not know all of the answers at this
time, no that is preserved for a different time and place after we die.