\section{Fri, Jun 8, 2018}

40 Years ago today. The Priesthood and Temple Ban on the Negro race was lifted.

There is in this life truths which cannot be denied. There are times when men
speak for God without asking God if they should say such things. It can be
rather embarrassing later on down the road when they have to change their speak,
claiming it to be from God or that God never instructed them to say such things.

As a body, we are expected to listen to their explaination of it all and simply
accept it. Moving forward as though none of it ever happened. This is not how
life works though. It is not in human nature to simply forget something happened
when in fact it did. There is no denying what was taught.

Yes we can move forward from such an act. But we cannot forget what happened in
order to not repeat the past. I hope that makes some kind of sense. It is better
to move forward into the future without repeating past mistakes than it is to
create those mistakes all oever again.

Naturally it is better to have not made such foolish statements to begin with,
but I fear that is human nature. I would say more on this topic, but I fear I
might get too heated. I do not wish that.\footnote{I of course am speaking about
blacks finally receiving the blessings of the priesthood and the temple after
so many years of prophets and aposltes having anti feelings towards them as a 
race. In my opinion, it should never have happened. They should have always
had the blessings allowed them, because God is not that author of confusion,
and God is not a respector of men.}

It is a good thing to be able to enjoy a coming up weekend. There is not much to
be said about it, aside from that which can be said. Work is a necessity of
life. There is no other thing possible than the need to do work. That is okay
for work brings in money, money brings about the ability to survive and live.

It is a wonder, do we become a slave to money? I do not know. There could be
times when it is a needed thing, but to become a slave to it? As though it were
your god? I would hope that is not the case. God is not made out of money, for
He is not an idol.\footnote{Acts 17}

There are so many confused people in this life. Some belong to a religion,
others do not admit to doing such. Either way, people will live their lives
according to their own dictates. However, there are some who are brainwashed in
such thinking. There is nothing wrong with belonging to a religion, that is fine
and well. It becomes an issue when that religion dictates everything you do.
Laws regarding your life should not be up to a religion, they need to be up to
God and His Son Jesus Christ.