\section{Tue, Oct 2, 2018}

Life can be tricky at times. There are so many advancments in a life that a person can
see out there, yet not understand or grasp. That's okay though. At least we know from
experience that it can and does get better as life moves on. If we are but to
understand and think for ourselves, would it not be beneficial to actually do some
thinking at times? There doesn't appear to be any reason not to enjoy a thought here
and there. There's no reason not to try to understand something as simple as that.
But what is simple exactly? Is there anything which can or cannot be proven because
it is simply there? Because it exists? What does any of that mean anymore? If a
person really does have agency, if agency is a thing and not something a person
created for the benefit of their own welfare, then we should be allowed to choose
which religion to believe in. We should be allowed to decide what happens in our life
and continue on that path as we see fit.

That thinking crosses over into quite a rabbit hole. It is said that Jesus died for
our sins, that he knows us personally. That He knew which sins we would commit or
possibly commit and He suffered for those sins. So, let's say as an example a person
has the ability to steal something. Jesus suffered for that sin for that speciifc
person. What happens if that person decides never to steal something ever in their
life? Does that mean Jesus suffered for nothing?

If that is the case, that Jesus suffered for nothing, then that would mean the
atonment is for naught. It covered sins that didn't exist for a person. However, if a
person does commit the sin of stealing doesn't that mean Jesus and God know exactly
what course our lives will take? Thus we don't have agency in the matter? We are
doomed to make that mistake no matter which road we took, simply because Jesus saw
the sin and atoned for it. It's an interesting thought process for sure. I just wish
I had an answer for it.
