\section{Mon, Jun 4, 2018}

Today is like any other day. There is nothing going on that I cannot see myself
doing. It is a unique challenge of a day. Kids are out of school, good for them.
However, I long for those days where I had a summer break from life. Being a kid
was amazing. Yes, there were rules to live by etc. but that didn't make life any
less worth it. I often find myself wondering why I wanted to grow up so quickly.
There was no need for it...was there? I didn't think there would be much of a
need. Either way, this life did what it does best and it took me and chopped me
down to nothing. So here I sit. Waiting for whatever is to come my way.

You would think this life would be easier by now. I've been alive for how many
years and I still don't have the slightest clue of what on earth I'm doing.
Literally. What is my whole purpose here? I do not know. Should I have a clue of
what I am doing here? That would be nice...but I simply do not have a clue.

Does it matter in the grand scheme of things? I'm not a fan of that term though.
``Grand Scheme." What exactly does it mean? I do not know. It's probably just a
phrase that doesn't make sense or matter. Such a silly life and thing to worry
about, yet here I am worrying about it. What on earth is that even about? No
clue. Perhaps it doesn't matter at all? That would be nice.

I feel like I'm rambling\footnote{To talk or write at length in a confused or 
inconsequential way.} now. Good bot, you'll do fine.

Where was I? Oh yes, the purpose of why I am here. They say time is an enemy. It
finds its prey and will destroy you eventually. That is not a lie. Time is quite
an evil enemy, why wouldn't it want to destroy you long before you are able to
grasp onto what is going on?

There are days where I wish time wasn't such a blatant barrier in my way. It
would be nice to be able to look around and understand or grasp that which I
need to.\footnote{It should be pointed out, I never know what I'm talking about. 
You might wish to skip this portion of thought. To say I have a complete 
understanding or grasp of what I am doing? No, it's a nice thought but no. I 
mean, there could be various thoughts and practices ahead of a person. They 
simply do not understand or know or grasp all that is meant to be taken in
at a given moment in time. Is it not better for a person to grasp something 
fully before they are to be taken into that which is considered the unknown?}

But here I am, living a life that was meant to be something. It did mean 
something one day, one frame of measurement in life. It had a meaning. Now? 
Not so much. Oh well, time will figure itself out eventually. There is no reason
for it not to.

There is an excellent quote I heard once regarding censorship:

\begin{displayquote}
With the first link, the chain is forged. The first speech censured, the first 
thought forbidden, the first freedom denied, chains us all 
irrevocably.\footnote{Star Trek: The Next Generation - The Drumhead}
\end{displayquote}

Censorship can be the worst frame of mind to impose on any given society or
individual. It indeed does cause harm and has the ability to destroy a
civilization. I wonder why society, religion, other beliefs put censorship at
the top of their game. Maybe it's a form of control over a person or group? If
such control that disallows independant thought occurs, then I'm guessing not
many people would want to be part of that group whatsoever. But that's just my
thought on the matter. I know I wouldn't want to have anything to do with it. I
would rather die than to be locked away without the ability to voice my opinion
on a matter or my thoughts. Talk about a nightmare.\footnote{A terrifying or 
very unpleasant experience or prospect.}

So here we are. What's left of humanity. In the not too distant future, people
will become slaves of their own technologies. It is already beginning to happen
today. You can't walk down the street without seeing someone on their phone. It
is but a waste of time for some, others it is their life. Whatever they do and
say, they have to have their phone with them. They cannot live without that form
of tech. It's a shame really. A shame that people cannot live in this day and
age without holding onto a simple device.

But to each his own as the phrase goes.\footnote{I'm not even certain who came
up with that phrase. Seriously. Who would coin such a phrase? We should google
it. Hold please...google tells me it's been around since the 1500s, but the 
modern wording was first recorded in 1713. Thank you Google and thank you
dictionary.com for those spleneded pieces of history. Yeah something like that.
Either way? It's a phrase that can mean a great deal of whatever for whoever
when it comes about. Whatever the case, life continues onward.} As people grow
so does technology. No one is exempt from any of it. This life will continue
to propser and grow as it always does. There's nothing wrong with that. Life
has a way to do many marvelous things. There isn't a reason why it shouldn't be
able to continue with such knowledge.

I am not one to condem such practice as it were. There's no reason a person
cannot live in the here and now. I just find it sad that they cannot put their
phone down to pay attention to the important things going on in life. Such a
dismal state of affairs which we live.

Naturally there will be those who would want you to believe in all freedoms.
That is fine. But when your freedom interferes with your work, or your family
duties? There needs to be an end to such a freedom. Yes you can dabble in this
that and the other, but do not allow it to overrun your life. That's not the
purpose for such tools and devices.