\section{Tue, July 17, 2018}

There comes a time in life... many times in a life where one simply does not
know where to go or what to do. They do not understand pretty much anything
which is tossed about around them. The person, themselves, can feel quite lost
during these times. There's nothing wrong with such feelings. Teachings of the
past flood their mind, they do not understand or know what is going on. Being
confused about it all hurts. It's one thing to have a belief system, but when
that belief system comes crashing down around you where does that leave you?

To go back to the days where you believed so innocently. There are times when
that would be nice. But they aren't always possible. So many thoughts come and
go in and out of the mind at times. It can be overwhelming, and even then that's
just being nice.

So, what does one do about it? Do they keep marching on as if nothing has taken
place? Do they confront the issue at hand? What are they to do about any of it?
So many questions with so many uncertainties and unanswered everything. Talk
about a rollercoaster. I wish at times I had never embarked on this journey, but
now I know what I know. There's no turning back.

Where is the truth? Where is the lie? Where is the falsehood? So many questions
and so many different opinions on matters. It is but a differing of opinions at
times. Sometimes it is better other times it is worse. Either way, unless you
come up with some kind of equation to figure out what is truth and what is
false, you will fail eventually.


\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
a     & b     & a (AND) b      & a (OR) b    \\ \hline
false & false & false          & false       \\ \hline
false & true  & false          & true        \\ \hline
true  & false & false          & true        \\ \hline
true  & true  & true           & true        \\ \hline
\end{tabular}
\caption{TRUE/FALSE Examination}
\label{table:1}
\end{table}

Math and Science are fact. They cannot be destroyed. They can however be proven
wrong but another truth will fill its place, using either Math or Science. There
are truths in this world that cannot be altered. They are concrete, no matter
how much you try you cannot change certain things. They are laws which must be
lived by and abided by in the universe there is no contradicting them.

People have tried to contradict certain truths but have found it difficult to do
so. They eventually have to come to the truth themselves and realize there is
nothing but truth in the thing they have been seeking. They must accept that as
fact and cannot turn from it.