\section{Wed, Jun 27, 2018}

Headaches. What are you going to do with them? They come, they go, they stick
around and they are evil! Evil I say! What exactly are you supposed to do with a
headache that doesn't leave? It moves around but doesn't leave. Grrr I say, Grrr
to them all!

Whatever the case, there is nothing wrong with thinking. Overthinking can be a
problem, but thinking in general can be good. To think about something is to try
and grasp and understand what is being taught. There's nothing wrong with that.
One has to be able to research and try to understand that which they are
learning. If they do not? There is no purpose in learning and no purpose in
understanding. To think for your own self without relying on other people's
thoughts and wishes is to own your beliefs.

Feelings are something else which can betray you. Feelings can often be
misinterpreted and misrepresented. There are those who would base their faith on
their feelings, but those feelings cannot always be valid. Any kind of feeling
can cause your demise. There is nothing you can do about it. Faith cannot be
based on a fallacy such as feelings. It is not logical.\footnote{
Ah there's that word again, logical. What is logic though? I know I've 
\st{talked} wrote about it before. But that was just a quote now wasn't it?
Yeah, something like that. If someone understands logic, then they are far
better off than I am.
}

To feel okay with yourself is a must. There are days where no one ever fully
feels okay with themselves. They don't grasp the concept of self worth or self
love. It is a sad thought that people have such feelings and thoughts. It occurs
to more people than you would think.

Self acceptance can come. It will come. Yes it might take patience and a lot of
ressaurance, but people are able to come to accepting themselves as they are.
People who press down on them, and try to dictate what is right and wrong in
their lives are not those who should be around you.