\section{Mon, Jul 16, 2018}

Another weekend is over. A week is just beginning. It is what it is mostly a day
where things happen. Nothing happens because it wants to of course. There is
always a cause and a reaction to an event. This is what life is made for. This
is what life is about. At least I believe that's what it is all about. Who is to
know exactly what life is meant to be?

There are days in this life where we all just want to simply sleep away. There's
nothing wrong with that thinking. However, it must needs be to have some sort of
accurate representation upon the world as a whole. Or upon ones self as a whole.
To be accepted in the world and not of yourself doesn't hold much merrit. Sure
you have the world to thank for your achievements, but if you do not accept
yourself, what have you then? A blank slate. A person who doesn't wish to be
here. That is all there is in life at that point. It  doesn't matter much beyond
anything else.

So here we are. Simply trying to live a life that is worth living. Seeing out
there the things which are meant to be seen. Enjoying everything there is to be
enjoyed without causing harm to ourselves.

It is an adventure at least. Perhaps a misadventure. Either way, we are here and
that's all which matters.

\st{Mistakes happen in life. They really do. But what are you supposed to do
about mistakes then? Do you take them as they are? Do you allow them to run free
in the wild? What of mistakes?}\footnote{\st{What of mistakes indeed. There are so
many thigns in this life which do not make sense. We are here for a purpose
so we are told, yet we do not know all there is to know about any of it. So here
we are simply living life to the best way we can.}}

Perhaps a person can try to understand the reason why they are here. Maybe they
can't. Is there ever a full reason why or why not something happens in life? I
doubt it. Only that we are meant to try and understand to the best of our
ability what we are doing here. If we can understand that, at least that much,
then we are better off then we were when we began.

Reason is hardly ever reasonable. It is but an annoying fly which is in your
house to the point where you do not wish it to be buzzing around you anymore. Or
is it bees that buzz? Oh that's even worse! A buzzing bee flying around your
house bugging you. Yeah, that's the ticket! Such a life upon which we stand, and
still don't have a full understanding of anything of it. We are alive, is that
enough? Perhaps.

Speaking of mistakes. Who's to say who makes the mistakes exactly? Who's to say
what those mistakes are? What makes up a mistake? Is not one person's mistake
another person's treasure?