\section{Tue, Sep 4, 2018}

A thought came to me as I was reading another book. I can't recall who said it, but
they are correct. The Book of Mormon doesn't teach of three heavens like the Bible
does, and even then the Bible didn't have much to say about it. Just that there were
three heavens like the Sun, Moon, and the Stars. Each have a glory. Here's Paul's
words on the matter:

\begin{displayquote}
There are also celestial bodies, and bodies terrestrial: but the glory of the 
celestial is one, and the glory of the terrestrial is another.

There is one glory of the sun, and another glory of the moon, and another glory of 
the stars: for one star differeth from another star in glory.\footnote{1 Cor 15:40}
\end{displayquote}

Then, at another time he talks about a man being caught up in the 3rd
heaven.\footnote{2 Cor 12:2}

But nowhere in the Book of Mormon do we have any such teachings. Later on, Joseph
Smith had a revelation, it's known as ``The Vision" or Section 76 of the D\&C that
talks about the three heavens, as well as outer darkness. All in all I find it
interesting for a book that brings back truths lost from the Bible, the Book of
Mormon doesn't even touch on the fact that there are three degress of glory.

I suppose there could be reasons for it? But I don't want excuses. I can come up with
my own excuses of why they aren't in there. Anyone can come up with an excuse as to
why something isn't in there. It's not difficult. But one would think, if you're
going to tell people they're going to a heaven or hell, it should be specified to
those people should it not? Yes the book was written ``for our day", but the people
were still taught were they not?

Yet the book has no problem talking about Outer Darkness:

\begin{displayquote}
And then shall it come to pass, that the spirits of the wicked, yea, who are 
evil-for behold, they have no part nor portion of the Spirit of the Lord; for 
behold, they chose evil works rather than good; therefore the spirit of the devil 
did enter into them, and take possession of their house—and these shall be cast out 
into outer darkness; there shall be weeping, and wailing, and gnashing of teeth, 
and this because of their own iniquity, being led captive by the will of the 
devil.\footnote{Alma 40:13}
\end{displayquote}

So, they can talk about Hell as it were, but not discuss the three kingdoms which
people should be striving for? Intimidating people that they'll go to a hell place 
is not teaching love to those people. Did not Christ teach to love the Lord your God
and your neighbor? Those around you?