\section{Fri, Jul 20, 2018}

Happy day, it's Friday! I mean honestly, what's better than a Friday? Perhaps a
Saturday, fine I'll give you that. But today is Friday and that's good enough
for me. I enjoy a good Friday. Not to be confused with Good Friday, that's an
actual day. But just a Friday that's the end of the week signaling the weekend.
Yeah something like that. Yes indeedy!

I remember being in a class once, where the teacher had us write down our
thoughts and feelings about certain topics. Near the end of th quarter, he said
if we aren't personalizing it to ourselves, we aren't putting enough time and
effort into the writing. At that point, I hadn't done much of anything so I
started writing sentences with more I's in them. Making it more about me than
general thoughts. It was a good experience. I find myself slipping in and out of
such writing these days, sometimes I write more about me other times I write
more genrally. It's a toss up. But I need to get more into the habit of
personalizing things more. That would be a good thing.

There was another time I was sitting in class, the teacher had quoted from a
paper he handed out to everyone. It talked about being restricted, held captive,
if you couldn't move and were bound were you really bound? Everyone in the class
agreed that you were. But then the teacher asked if anyone thought opposite of
what it said. My hand went up. Apparently I was the only one in the class that
was thinking that morning? I'm not sure.

I argued the point that even though they might bind a person, physically
restricting their movements etc, they will still have the ability to think for
themselves. They cannot take that freedom away from them for they cannot know
their thoughts. Mind control is a thing, it can happen, but I suppose it all
depends on a person's willpower. If they have the ability to deny thoughts
thrown at them and can have the ability to be strong through it they cannot be
bound and cannot be broken.

It's an interesting thought to this day actually. There are so many types of
oppression\footnote{
oppression

\textit{noun}

1. Prolonged cruel or unjust treatment or control.

2. The state of being subject to unjust treatment or control.

3. Mental pressure or distress.
} in the world. A person can be dragged through the mental gymnastics of a cult,
or religion\footnote{Is there a differenced between the two?} and can be torn
left and right beyond anything which they are able to \st{feel} withstand it 
would seem. It's a cruel thing to force someone to go through.

I wish I had that exact quote I mentioned above, it would be a nice addition to
today's thought process. But I cannot find it. Maybe I'll find something simliar
to it? I don't know. Onward I search.