\section{Thu, Jul 19, 2018}

Life can be frustrating at times. There's no way around it. You will have
difficulties in this life. That's all there is to it. That's the most simple
fact of it all. You can't escape it, you can't run from it. It's not that you'll
be doomed or anything, just that life will make its twist and turns and there's
nothing you are able to do about it. That's fine though. it's life. Eventually
things get figured out right? One would hope so.

Watched a movie last night. It was about a guy who could time travel, and time
travel he did. By the end of the movie, he decided that life wasn't about time
traveling but the ability to realize that each day is precious and to live like
you have gone into the past to make changes. It was an inspiring film, quite a
moment to be had for sure.

I oft wonder at times what it would be like to change something in my own life.
There are some things I wish I could change, but the more I look at them I don't
think I would change them. Those moments are what made me the person I am today.
Changing them would in effect change me. I suppose if I were to be able to
change something, I wouldn't want to have a knowledge of both the former me and
the new me. I suspsect that would become confusing.

Think about it for a moment. You have this knowledge of a former you, things and
events didn't happen in this new timeline of events since you changed them. What
would that do to a person's psychie? Since timetravel isn't possible, I don't
think we would have such an answer. But it is something interesting to think
about.

Feelings that come along in this life alone are confusing. They tend to cause so
much inner struggle. Feelings, emotions, whatever you want to call them. They
serve a purpose I suppose, but somedays I wonder if it would be better if
\st{we} I didn't even experience such things. But \st{we} I must deal with these 
thoughts and feelings, some come from damaged pasts, depression, anxiety and 
whatnot. Either way, here \st{we} I am \st{are} doing the best \st{we} I can do 
without looking back. Never look back. It will destroy you.