\section{Thu, Jun 28, 2018}

Changes come all along the places we will end up. There's nothing left of
anything else long ago the world did end. No one wanted anything else, it would
come crashing down. It is not my fault or determined fate which has the life
upon me. My world will live and continue on if it should only find life. So cast
about your jealous woes of life which easily glide. Nothing else will matter now
a life is but a colliding star.

To grasp and to understand two different things cannot measure within ourselves
a mask is but shrouded long ago into the deepest dark of night. We all be
destroyed long before this life will end. It is but an option yet here we come.
Lost in a moment long ago gone. Oh how gone it all can be long into the darkest
of days and the brightest of nights. We suffer.

Not every aspect of life will make perfect sense. There is nothing more to it
than that which will come to destroy us. Perhaps it comes today, maybe it will
find a way to do its bidding tomorrow. No one has a full clue, no one knows or
understands, grasping all there is at the end of th eday. We are but a simple
vessel seeking and living through this life in the darkest mirror possible. Oh
what a mirror upon which we weep. Lasting but a fleeting moment to bring us down
tot he depths of a great monster. A beast from which there can be no full
escape. To do so would invite that spark, an element of surprise. Maybe not all
at once, but for now it might be a good thing. Something simply wait for you.
That something will find what it wants and needs. Nothing else will come from
it. We are but alone in our thinking.

Now there are days upon more days when none of this will come to any good thing.
It will eventually be our own undoing. Thought this med was supposed to slow my
mind. Maybe it has worn off by now? Who is to say what is going on in this life
at this exact moment. To feel this way, we are but a pain destroyed, reborn and
waiting to come alive all over again.

What a nightmare all of this has become. We are but a person trapped within the
simple brain dynamic. Nothing can ever come good from any of it. This life will
need to come away and be destroyed. So I shall quietly sit here and sip on my
water. It knows what my body needs and that which can be placed aside. Such
nonsense to be held and yet here we are simply waiting for summer to come.

It is cold.

Not like everything else is happening all at tonce, or maybe it actually is.
Such a life barely exists beyond the happy feelings which come from any of it.
We are but a consequence of our own actions. Actions come and go, they tend to
destroy. They tend to create fear and feed upon those things which are right or
wrong. Fear has a tendency to destroy a person deep from within. Not everything
has the ability to survive such an attafck. Oh attacks come and go, they don't
matter why th ey are attacking, only that they are attacking. Nothing has to
wonder at that point. The enevitable will come crashing down someday. Where will
you be when it does come around?