\section{Fri, Jul 13, 2018}

Ah Friday the 13th. It's a day. It's a thing. One of those dreaded days of the
year which we come across every so often. I wonder if someone has made a
calculated approximation of how often this day actually comes around. That would
be interesting to see actually. I'll have to do some looking into that.

But all I have is this awesome way of checking if a value exists in an array:

\lstinputlisting[language=Java]{2018/CheckArray.java}

Not too shabby if I do say so myself! Now I can't recall where I picked up this
wee little bit of knowledge...somewhere from the great internets I'm sure. I
just don't know where exactly. Oh well. What happens happens and we all have
nothing to worry about if that's the case. I have the code, and that's really
all which matters yes? Maybe. Well as long as it's simply an example piece and
not an actual full blown application...'cause that would be wrong.

But the internet is littered with example java code all over the place. Who's to
say who wrote the original one after it's been passed around for so long?
There's an interesting piece of thought. Who wrote the original piece of code
that we see in examples all over the place?\footnote{
I actually wouldn't mind figuring that bit of history out. I mean...if it's even
possible! I don't think it is. It's like a story that's been told year after
year, decade after decade...passed down from generation to generation. Who's to
say what is \st{real and what is fake anymore} the original real story from the 
beginning.
}
