\section{Mon, Jul 16, 2018}

Another weekend is over. A week is just beginning. It is what it is mostly a day
where things happen. Nothing happens because it wants to of course. There is
always a cause and a reaction to an event. This is what life is made for. This
is what life is about. At least I believe that's what it is all about. Who is to
know exactly what life is meant to be?

There are days in this life where we all just want to simply sleep away. There's
nothing wrong with that thinking. However, it must needs be to have some sort of
accurate representation upon the world as a whole. Or upon ones self as a whole.
To be accepted in the world and not of yourself doesn't hold much merrit. Sure
you have the world to thank for your achievements, but if you do not accept
yourself, what have you then? A blank slate. A person who doesn't wish to be
here. That is all there is in life at that point. It  doesn't matter much beyond
anything else.

So here we are. Simply trying to live a life that is worth living. Seeing out
there the things which are meant to be seen. Enjoying everything there is to be
enjoyed without causing harm to ourselves.

It is an adventure at least. Perhaps a misadventure. Either way, we are here and
that's all which matters.

\st{Mistakes happen in life. They really do. But what are you supposed to do
about mistakes then? Do you take them as they are? Do you allow them to run free
in the wild? What of mistakes?}\footnote{\st{What of mistakes indeed. There are so
many thigns in this life which do not make sense. We are here for a purpose
so we are told, yet we do not know all there is to know about any of it. So here
we are simply living life to the best way we can.}}

Perhaps a person can try to understand the reason why they are here. Maybe they
can't. Is there ever a full reason why or why not something happens in life? I
doubt it. Only that we are meant to try and understand to the best of our
ability what we are doing here. If we can understand that, at least that much,
then we are better off then we were when we began.

Reason is hardly ever reasonable. It is but an annoying fly which is in your
house to the point where you do not wish it to be buzzing around you anymore. Or
is it bees that buzz? Oh that's even worse! A buzzing bee flying around your
house bugging you. Yeah, that's the ticket! Such a life upon which we stand, and
still don't have a full understanding of anything of it. We are alive, is that
enough? Perhaps.

Speaking of mistakes. Who's to say who makes the mistakes exactly? Who's to say
what those mistakes are? What makes up a mistake? Is not one person's mistake
another person's treasure?\footnote{What is determined to be a \textit{treasure?} 
There can be so many things classified as treasures these days can't there. Life 
comes along and there are things to be seen and heard. Life has many choices in 
it, it isn't a simple thing to undertake. It is what it is.}

Let us not forget that which is most important a dear to us. There is a time in
life which cannot be shattered upon broken dreams and realities. Life comes at
us once, we have the opportunity to take unto ourselves this life and to see
what is happening an what goes on in our own lives, as well as the lives of
others. It is up to us to determine the best course of action for ourselves.
Were it not so, we wouldn't have the ability to be here. We would be someplace
else. A far off distant shore perhaps, or a place beyond that which we consider
home. Someplace beyond the nebulas of this realm. It is but a dream to some, a
pipe dream to others...this is what life is.

\st{As a youth, I was often fond of playing in the front yard. A man drove by
one day, stopped and asked a question. I answered the man, he had his family in
the car so it was alright to answer such a question right? I do not recall what
the exact question was...just that he asked it and went on his way. My father
saw the exchange and reminded me the importance of not talking to strangers. It
is true I didn't know who the man was, where he was going, where he was coming 
from...I did not know the man at all. An important lesson indeed to be found
among the various memories I have from my years in this life. Years later, I
still don't enjoy talking to people I don't know. Call it being an introvert,
or consider it being something else...whatever the case, it is something I don't
really think about or consider. I try to avoid people as best as possible. Not
the best way to make friends or to gravitate towards people...but it works for 
me, there's no reason to get to know people I don't know or will never wish to
know. But that is just me. There are people out there who can talk to anyone, 
they are able to strike up a conversation without problem. I am not that person.
Not in the slightest, and I am okay with that thought.}

There are things in this life which don't always make sense. I have touched on
this a lot in the past. Perhaps a little bit too much? I do not know, nor can
I say with a full thought process of it all. I do know for a fact that this life
can be a maze if you allow it to be. There is nothing wrong with that, it is
what it is and will be what it will always be. If we are here as a test, under
some kind of sky being then so be it. There is nothing wrong with that. We must
be able to grasp and consider everything which is possible. If we are to take it
upon ourselves to govern ourselves, then we must govern ourselves with accuracy
and be able to understand and grasp that which has been placed in our laps at
the time we are able to do so. \st{It is not above the god given law of self.}
It is not above that which we are capable of. We must govern outselves in times
of need and times of whatever comes our way. We are not immune to the effect of
such matters.

I do not wish to dwell on the negative aspects of life, but it tends to happen
from time to time. It comes and goes as it pleases. There is nothing wrong with
thinking negatively about such matters, but here we are living to the point
where nothing else can take form. We are here. We must accept that fact and we
must move on.

What we remember or don't remember from a past life, or another life as it were
doesn't matter. Why should it matter to us? We are but people living in a huge
gigantic universe. A spec of dust compared to everything else in the world. This
is what life is about. Our nothingness. To understand and grasp that we are
nothing is but the first step in life. There is nothing wrong with that thought.
