\section{Tue, July 17, 2018}

There comes a time in life... many times in a life where one simply does not
know where to go or what to do. They do not understand pretty much anything
which is tossed about around them. The person, themselves, can feel quite lost
during these times. There's nothing wrong with such feelings. Teachings of the
past flood their mind, they do not understand or know what is going on. Being
confused about it all hurts. It's one thing to have a belief system, but when
that belief system comes crashing down around you where does that leave you?

To go back to the days where you believed so innocently. There are times when
that would be nice. But they aren't always possible. So many thoughts come and
go in and out of the mind at times. It can be overwhelming, and even then that's
just being nice.

So, what does one do about it? Do they keep marching on as if nothing has taken
place? Do they confront the issue at hand? What are they to do about any of it?
So many questions with so many uncertainties and unanswered everything. Talk
about a rollercoaster. I wish at times I had never embarked on this journey, but
now I know what I know. There's no turning back.

Where is the truth? Where is the lie? Where is the falsehood? So many questions
and so many different opinions on matters. It is but a differing of opinions at
times. Sometimes it is better other times it is worse. Either way, unless you
come up with some kind of equation to figure out what is truth and what is
false, you will fail eventually.

The following table \ref{table:1} demonstrates this concept.

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
a     & b     & a (AND) b      & a (OR) b    \\ \hline
false & false & false          & false       \\ \hline
false & true  & false          & true        \\ \hline
true  & false & false          & true        \\ \hline
true  & true  & true           & true        \\ \hline
\end{tabular}
\caption{TRUE/FALSE Examination}
\label{table:1}
\end{table}

Math and Science are fact. They cannot be destroyed. They can however be proven
wrong but another truth will fill its place, using either Math or Science. There
are truths in this world that cannot be altered. They are concrete, no matter
how much you try you cannot change certain things. They are laws which must be
lived by and abided by in the universe there is no contradicting them.

People have tried to contradict certain truths but have found it difficult to do
so. They eventually have to come to the truth themselves and realize there is
nothing but truth in the thing they have been seeking. They must accept that as
fact and cannot turn from it.

It amazes me that people try to use faith in the place of logic. They cannot
succeed. They will never be able to dictate that faith alone will be better than
the truth. Because a person feels something to be true, does not mean it is
true. Truth is truth, feelings can be fallible.\footnote{
fallible (\textit{adjective}) - capable of making mistakes or being erroneous.
}

So once we realize and understand that the truth cannot be shaken and feelings
can be faked, what do we do with this knowledge? Is there anything which can be
done? One can move away from such feelings, realizing that cold hard facts are
the only way to process this life. It's not an easy thought process, it's not an
easy way to actually go forth and live a life. But it is possible. Anything is
possible in this life if you have the will and the deesire to attempt it.

Not many people are comfortable with thinking outside of the box as it were.
They see their religion as a comfort zone and they don't want to leave that
space where they feel at peace, even if the truth is staring them in the face,
they do not want to see any other truth than what they feel.

\st{It's rather messed up if you think about it. Year after year people are 
brainwashed into thinking something is true while it cannot hold water. It is a
complete mess of a life to be living! But people continue onward like nothing
ever matters. They believe what they're told and they don't care anymore. That's
what this life happens to some people. They simply do not care what is going on
and don't want to hear what is true. They are okay with the blinders on. They 
are okay with the thought that their religion won't lead them astray. They don't
care about the history of anything. They only care about the here and now. But
if the history got them to a point, wouldn't they care about it then? Nothing in
this life comes without a price. Nothing in this life comes without a backstory.
If you care so much about the history to keep saying certain things from it, yet
you do not wish to delve deeper...are you not confusing yourself? Are you not
putting yourself under condemnation for not wanting to know the whole truth?}

Sometimes the feelings just get so overwhelemed. See there it is again,
feelings. They come and they go and they cannot ever be depended upon. That's
life. That's fact. If feelings could be depended upon, then God would only allow
such good feelings to come to his one true church. Members of other faiths
wouldn't be having the experiences they are having. Yet they are. They have
uplifting experiences which tells them their choice in religion is true. Why
would they want to move away from that if it's true? Exactly.

Gah. So much noise in the world. So much noise and there's nothing that can be
done from any of it. If there's one thing you can count on in the world alone is
the noise level that comes with it. There's so much noise around a person cannot
simply think and enjoy the life they are living. It comes in the form of so many
different things. Distractions abound in the millions and here we are just
trying to wade through all of it.

\begin{displayquote}
\centering
Say something, I'm giving up on you.\footnote{Say Something - A Great Big World}
\end{displayquote}

It feels at times...like all I want to do is just hold onto something so tight
and never let go. But everything I've come to know as truth has been taking
dents left and right. There's not much to hold onto anymore. Family is great and
all, but they aren't around forever either. Family leaves. Friends leave as
well. There's nothing which really sticks around and allows us to continue
growing. We either have to find peace and joy by ourselves or we are doomed to
simply live an existence where there is no joy or peace to be found. Is that the
bottom line? I think it is. God intends us to find and make our own joy and
peace. No one can give that joy and peace to us.

I've said it in the past, threatening someone that they will ``drag you kicking
and screaming into heaven" is not following the pattern Christ set when he was
on the Earth during his mortal ministry. It is a shame that some people would go
to such lengths to scare others into behaving and conforming to the belief
system they believe in.\footnote{Ah a continued theme in my life, a thought that
will never leave me. It has been said to me so many times I cannot hide from it.
Such a sad state of affairs we live in when such a thought is meant to help a
person, such as myself, into doing that which is expected of them by an outside
force.}

\st{It makes me angry at times. There is nothing I can do about it except to 
stay far away from such influences in my life. Yet those same influences wish to 
inflict such ``obedience" upon my own family and children. I do not know where
it begins and where it ends. This life is but a process. A long process which I
cannot seem to bear or hold to for long. It is something of a struggle, to be 
honest with you, yet I continue onward hoping something will be better. Hoping
someday will just be brighter than the last years that it has been dark. Yeah,
I doubt that will ever really happen in this life. I don't know for sure. It is
but a dream right? Isn't that what this life is all about? A dream sequence upon
which we have no clue what is going on? Yes, something like that. I wish there
was something I could do about it. Aside from the things I am attempting to do
already. There needs to be something better in this life than there currently
is. Something which can break me from the deep which I am drowning in.}

Oh life, where have you gone off to? What are you exploring today and where
are you headed to in the future? One would hope and think this life would
eventually make sense. To be able to understand and grasp it all would mean so
much to me. Yet here I sit and I don't grasp any of it. Memories flood in where
I see the past, my past. It comes in waves. So many different things in this
life and here we are simply wondering when the next phase of it will be complete
and what will we do with it then? Will it not simply continue to be carried down
the river as it were? Life will wash away eventually. Where will that leave us?

To say you have the full truth, and yet to be so blind against certain other
truths in the world. How can you claim you have the truth at all? To know one
side of the truth only is to harm yourself in the long run. You have to know
both sides of the truth in order to make an informed opinion about the matter at
hand.
