\section{Mon, Jul 23, 2018}

Cars on the freeway. That's what life feels like at times. Just a bunch of cars on a
freeway. There's nothing wrong with cars on a freeway mind you. Until they end up
getting into an accident, or backing up the freeway so you cannot move forward.
Obviously you can't go backwards either. But you sure as hell can't move forward.
That's what this life is about. Always  moving forward, sometimes you are stuck in a
section for a while. That would be where the freeway is stopped. But other times you
are inching forward towards whatever goal you have. It's not always a fast
progression either. When the freeway is moving fast, that's a good sign.

Times change and so do people. People have the ability to make changes in their
lives. There's nothing wrong with that. Change can and will come at the decision of
the person needing the change. I don't doubt God works in this way. If we are to have
joy in this life and something isn't right, we need to make a change. That change can
come within, we do not have to wait on revelation from God for that change to take
place. Goes back to not being commanded in all things.\footnote{D\&C 58:26 For behold, 
it is not meet that I should command in all things; for he that is compelled in all 
things, the same is a slothful and not a wise servant; wherefore he receiveth no 
reward.}

So, if we are to think for ourselves and not expect God to fix everything in our
lives. Then we are able to do that which we must do to make our lives better. Why
don't people tend to see this? They have the charge to do it. It's up to them to make
their life better instead of complain that God hasn't come down and changed things
for them. God won't interfere like that. It's not in the program for Him to
interfere. Why don't people grasp that? It's a most basic principle.

I've often wondered what it would be like to write a letter to my parents regarding
my current religious beliefs. It wouldn't be an easy letter to write. I suppose these
things are never easy to write, are they. Well that's the delima I find myself in. Do
I tell my parents my beliefs? Do I shatter their world? What would that letter even
look like?

My wife has told me to wait till they die. Which can be harsh, I'm not gonna lie. But
if it prevents heartbreak in this life, why not. They don't need to know my beliefs I
guess, I mean they already have thoughts I don't believe anymore. But we don't really
talk about it, and why should we? It only causes contention and strife.

Being told that contention is of the devil\footnote{
3 Nephi 11:29 For verily, verily I say unto you, he that hath the spirit of 
contention is not of me, but is of the devil, who is the father of contention, 
and he stirreth up the hearts of men to contend with anger, one with another.
} for so many years, I tend to avoid contention. I hate it, it's not producitve no 
matter who's behind any of it.

My parents did tell me to write my own book regarding the church, but I'm not sure if
they understand the kind of book I want to write. The truth of things is what is most
important. Be it spiritual truth, religious truth, or personal truth. The truth must
hold strong and will always be dear to my heart.

I've been told so many times to stop looking for truth and to simply believe what
I've been taught growing up because that's the truth. Or have faith, to rely on my
faith. Faith and belief \st{isn't} aren't facts though. Believing in something is 
okay, but once you have facts and can prove something? Wouldn't that be better?

Why can the Bible be proven to be true, yet there is no evidence for the Book of
Mormon? God wants His children back right? He wants them to find the right path back?
I mean that's what I was taught growing up. Why wouldn't He provide proof of the Book
of Mormon in that way? Are we really just meant to go off faith only?
